Applied Calculus Ch. 1 ยง5 Prob. 14
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("AC-01-5-14-SD")
```

just a change

#### Graph $y = 100 e^{-0.4 x}$.  Describe what you see.

```{r include=FALSE}
f= newMC(totalPts=1)
```
The graph...     

`r I(f(FALSE))` Falls at a constant slope     
`r I(f(FALSE))` Falls rapidly for small $x$ then suddenly levels out.           
`r I(f(TRUE))` Falls rapidly for small $x$, smoothly decreasing in slope as $x$ gets bigger.          

```{r results="hide", include=FALSE}
I(f(finish=TRUE))
```

`r I(closeProblem())`

#### Approximate the answers to these questions by reading from your graph. 

```{r include=FALSE}
approximate = selectSet(name="atwhatvalue", totalPts=1, "1"=FALSE, "2"=FALSE, "4"=TRUE, "8"=FALSE, "16"=FALSE)
```

At what value of $x$ does the function reach a value of $y=20$? `r I(approximate)`

`r I(closeProblem())`

```{r include=FALSE}
yvalue = selectNumber(choices=c(0,50,100,150), correct=c(100), name="valueofy", totalPts=1)
```

When $x=0$ the function has a value $y$ of what? `r I(yvalue)`

`r I(closeProblem())`

```{r include=FALSE}
halfofvalue=selectNumber(choices=c(1, 1.75, 2.5, 3.25, 3.75), correct=c(1.75), name="halfvalue", totalPts=1)
```
At what value of $x$ does the value of $y$ fall to half what it was at $x=0$? `r I(halfofvalue)`

`r I(closeProblem())`
