Applied Calculus Ch.1 ยง2 Prob.16
========================================================
```{r include=FALSE}
require(WriteScoreR)
require(mosaic)
newScorerSet("AC-1-02-16-SD")
```

```{r include=FALSE}
f = newMC(totalPts=1)
```

What is the meaning of the number 3.5 in Okun's law?     

`r I(f(FALSE))` The yearly percentage increase in production when unemployment is zero.     
`r I(f(TRUE))` The yearly percentage increase in production when unemployment does not change from the previous year.     
`r I(f(FALSE))` The unemployment rate when production does not grow.     
`r I(f(FALSE))` The typical unemployment rate.

```{r results="hide", include=FALSE}
I(f(finish=TRUE))
```

`r I(closeProblem())`

```{r include=FALSE}
g = newMC(totalPts=1)
```
What is the effect on national production of a year when
  unemployment rises from 5% to 8%?

National production will ...     
`r I(g(FALSE))` Go up by 3.5 percent     
`r I(g(FALSE))` Go down by 3.5 percent     
`r I(g(FALSE))` Go up by 2.5 percent     
`r I(g(TRUE))` Go down by 2.5 percent     

```{r results="hide", include=FALSE}
I(g(finish=TRUE))
```

`r I(closeProblem())`

```{r include=FALSE}
h = selectSet(name="unemployment", totalPts=1, "Up by 1.75"=TRUE, "Down by 1.75"=FALSE, "Up by 3.5"=FALSE, "Down by 3.5"=FALSE)
```

What change in unemployment rate corresponds to a year when
  production is the same as the year before?
`r I(h)`  

```{r results="hide", include=FALSE}
```
`r I(closeProblem())`

```{r eval=FALSE, include=FALSE}
I(textItem(name="okunslaw",rows=3,totalPts=2))`
```
What is the meaning of the coefficient $-2$ in Okun's law?     
`r I(textItem(name="okunslaw",rows=3, totalPts=2))`

`r I(closeProblem())`
