Intro to Statistical Modeling Ch. 14 Prob. 10
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-14-10-SD")
```

The t- and F-distributions are closely related.  That is, you can calculate the p-value on a t-statistic by using the F distribution, if you do it right. 

Generate a large random sample from a t-distribution with 10 degrees of freedom.  Then generate another random sample from the F-distribution with 1 and 10 degrees of freedom.  

Graphically compare the distributions of the F and t values.  What do you see?

```{r include=FALSE}
prob1=selectSet(name="TorF", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* They are the same. `r I(prob1)`
```{r include=FALSE}
prob2=selectSet(name="TorF2", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* The F distribution is much more skew to the right. `r I(prob2)`
```{r include=FALSE}
prob3=selectSet(name="TorF3", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* The t distribution is symmetrical around zero. `r I(prob3)`

Now compare the distributions of the F values and the **square** of the t values.  What do you see?

```{r include=FALSE}
prob4=selectSet(name="TorF4", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* They are the same. `r I(prob4)`

`r I(closeProblem())`