Intro to Statistical Modeling Ch. 14 Prob. 27
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-14-27-SD")
```
Here is the report of a simple model of the foot-length data:
```{r}
kids = fetchData("KidsFeet");
summary( lm( length ~ 1, data=kids ) )
```
**SHOULD MATCH**    
Coefficients:
          Estimate   Std. Err.  t value Pr(>|t|)    
(Intercept) 24.723       0.211    117.2   <2e-16 


The summary report includes a p-value (written as $\verb+Pr(>|t|)+$).
```{r include=FALSE}
feet=selectSet(name="null", totalPts=1, "The mean cannot be calculated."=FALSE, "The sample mean is zero."=FALSE, "The population mean is zero."=TRUE, "The sample mean is greater than zero."=FALSE, "The sample mean is less than zero."=FALSE, "The population mean is greater than zero."=FALSE, "The population mean is less than zero."=FALSE)
```
What is the Null Hypothesis corresponding to this p-value: `r I(feet)`

<aside>
ANSWER:    
Null hypotheses **always** refer to the population, not the sample. (It's the p-value that is about your sample, referring what you found in the sample to what you would find from a random sample drawn from a population satisfying the null hypothesis.)

If the null were true, the coefficients in models would be zero (on average).  For this simple model, *A* ~ 1, the coefficient refers to the mean, so the null hypothesis underlying the p-value in this regressin report is that the population mean is zero.
</aside>

`r I(endProblem())`