Intro to Statistical Modeling Ch. 14 Prob. 22
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-14-22-SD")
```

```{r include=FALSE}
kids=fetchData("KidsFeet")
```
The special program <code>rand()</code> generates random vectors for use in modeling.   It's special because it works only within the <code>lm</code> command.  For example, suppose we want to create three random model vectors along with an intercept term to model the kids' foot width data:
```{r}
lm( width ~ rand(3), data=kids)
```
 
```{r}
lm( width ~ rand(3), data=kids)
```
 

The coefficients are different in the two models because the
"explanatory" vectors are random.

We're going to study the $R^2$ due to such collections of random vectors.  This can be calculated with the <code>r.squared</code> program: 
```{r}
r.squared(lm( width ~ rand(3), data=kids))
```

```{r}
r.squared(lm( width ~ rand(3), data=kids))
```

Note that the $R^2$ values vary from trial to trial, because the vectors are random.

According to the principle of equipartition, **on average**, each random vector should contribute $1/(n-1)$ to the $R^2$ and the effect of multiple vectors is additive. So, for example, with $n=39$ cases, the three random vectors in the above example should result in an $R^2$ that is near $3/(39-1) = 0.08$.


Repeat the above calculation of $R^2$ many times for $p=3$ random vectors and find the mean of the resulting $R^2$.  You can do the repetitions 100 times with a statement like this:
```{r eval=FALSE}
samps=do(100)*r.squared(lm(width~rand(3),data=kids))
```

Now do the same thing for $p=1,3,10,20,37$ and $38$.  Are the results consistent with the theory that, on average, $R^2$ should be $p/(n-1)$?


Copy the table onto a piece of paper and enter your results in the empty second and third columns to hand in to your professor.  


| $p$ &nbsp; | &nbsp; $p/(n-1)$ &nbsp; | &nbsp; Mean $R^2$ |
|:---|:---:|:---:|
| 1 | | |
| 3 | | | 
| 10 | | | 
| 20 | | |
| 37 | | |
| 38 | | | 


Note that for $p=38$ all of the trials produced the same $R^2$ value. Explain why.    
`r I(textItem(name="p=38", totalPts=2, rows=3))`


<aside>
ANSWER:    
Here are the mean $R^2$  for different values of $p$, and the value of $p/(n-1)$. (For the kids data, $n=39$.)
```{r}
mean(do(1000)*r.squared(lm( width ~ rand(1), data=kids)))
```
**SHOULD MATCH**
[1] 0.02744934
```{r}
1/(39-1)
```

```{r}
mean(do(1000)*r.squared(lm( width ~ rand(3), data=kids)))
```
**SHOULD MATCH**
[1] 0.07814845
```{r}
3/(39-1)
```

```{r}
mean(do(1000)*r.squared(lm( width ~ rand(10), data=kids)))
```
**SHOULD MATCH**
[1] 0.2652253
```{r}
10/(39-1)
```

```{r}
mean(do(1000)*r.squared(lm( width ~ rand(20), data=kids)))
```
**SHOULD MATCH**
[1] 0.5277672
```{r}
20/(39-1)
```

```{r}
mean(do(1000)*r.squared(lm( width ~ rand(37), data=kids)))
```
**SHOULD MATCH**
[1] 0.973848
```{r}
37/(39-1)
```

```{r}
mean(do(1000)*r.squared(lm( width ~ rand(38), data=kids)))
```
**SHOULD MATCH**
[1] 1
```{r}
38/(39-1)  # obviously !!
```
</aside>

`r I(endProblem())`