Intro to Statistical Modeling Ch. 14 Prob. 2
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-14-2-SD")
```

```{r include=FALSE}
kids=fetchData("KidsFeet")
```
You can test the null hypothesis that the population mean of a variable $x$ is zero by constructing a model *x~1* and interpreting the coefficient on
the intercept term <code>1</code>. 

Often, the null hypothesis that the population mean is zero is irrelevant.  For example, in the kid's feet data, the mean foot width is $8.99$ cm.  There is no physical way for the population mean to be zero.

But, suppose you want to test the null hypothesis that the population mean (for the population of school-aged children from whom the sample was drawn) is $8.8$ cm.  To do this, create a new variable that would be zero if the population mean were 8.8 cm.  This is simple: make the new variable by subtracting $8.8$ cm from the original variable.  The new variable can then be tested to see if its mean is different from zero.

Using the kids-feet data: 

```{r include=FALSE}
prob1=selectNumber(choices=c(0.000,0.024,0.026,0.058,0.094,0.162,0.257), correct=c(0.024), totalPts=1, name="8.8Pvalue")
```
* Find the p-value on the null-hypothesis that the population mean of the foot *width* is $8.8$ cm. `r I(prob1)`


<aside>
ANSWER:    
The p-value in the regression report on the model *width* ~ *1* refers to the null hypothesis that the population mean is zero.  In general, the p-value on the model *A*  ~ *1* is that the population mean of quantity *A* is zero.  


The question here refers to a null hypothesis that the population mean of the *width* variable is 8.8 cm.  To fit this into the framework of the model *A* ~  *1*, you need to create a variable that reflects *width* but which would have a value of 0 if the null were true.  Easy enough: just subtract 8.8 from the variable *width*. This can be done directly in the model statement.
```{r}
summary(lm( width - 8.8 ~ 1, data=kids))
```

The p-value is 0.0237.
</aside>

```{r include=FALSE}
prob2=selectNumber(choices=c(0.00,0.23,0.27,0.31,0.48,0.95), correct=c(0.27), totalPts=1, name="8.9Pvalue")
```
* Find the p-value on the null-hypothesis that the population mean of the foot *width* is $8.9$ cm.

<aside>
ANSWER:    
Same sort of thing:, but subtract 8.9 from *width*:
```{r}
summary(lm( width - 8.9 ~ 1, data=kids))
```

WARNING: It's not a usual practice to look at a succession of null hypotheses.  The point of doing so in this problem is just to show that to use the model *A* ~ *1* format to conduct the hypothesis test, you can subtract the hypothesized mean from the variable in question.
</aside>

`r I(closeProblem())`
