Intro to Statistical Modeling Ch. 14 Prob. 11
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-14-11-SD")
```
You know that you can compute the sample mean $m$ and variance $s^2$ of a variable with simple calculations     
$$ m = \frac{1}{N}\sum_{i=1}^N x_i \ \ \mbox{or} 
\ \ s^2 = \frac{1}{N-1} \sum_{i=1}^N (x_i - m)^2 $$     
Such calculations are implemented with simple computer commands, e.g. 
```{r}
feet = fetchData("KidsFeet")
mean( feet$length )
```

```{r}
var( feet$length )
```

This is a fine way to calculate these quantities.  But, just to show the link of these quantities to modeling, I ask you to do the following with the kidsfeet data: `KidsFeet` :

* Fit a model where one of the coefficients will be the mean of the *length*.  Enter the model report below.

`r I(textItem(name="mean", totalPts=2, rows=2))`

* Perform ANOVA on the same model. One of the numbers in the ANOVA report will be the variance.  Which one is it?  

`r I(textItem(name="variance", totalPts=2, rows=2))`

* Based on the above, explain why the calculation of the sample variance involves dividing by $N-1$ rather than $N$.

`r I(textItem(name="Nminus1", totalPts=2, rows=2))`

`r I(endProblem())`