Intro to Statistical Modeling Ch. 11 Prob. 35
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-11-35-SD")
```
In commenting on the "achievement gap" between different groups in the public school, the Saint Paul Public School Board released the following information:

> Saint Paul Public Schools (SPPS) serve more than 42,000 students. Thirty percent are African American, 30% Asian, and 13% Hispanic. The stark reality is that reading scores for two-thirds of our district's African American students fall below the national average, while reading scores for 90% of their white counterparts surpass it. 

The point of this exercise is to translate this information into the point-score increase needed to bring African American students' scores into alignment with the white students.

Imagine that the test scores for white students form a normal distribution with a mean of 100 and a standard deviation of 25. Suppose also that African American students have test scores that form a normal distribution with a standard deviation of 25.  What would have to be the mean of the African American students' test scores in order to match the information given by the School Board?

```{r include=FALSE}
f=newMC(totalPts=1, name="score.threshold")
```
* What is the score threshold for passing the test if 90% of white students pass?  One of the following R commands will calculate it. Which one?    
`r I(f(FALSE))` <code>pnorm(0.1,mean=100,sd=25)</code>   
`r I(f(FALSE))` <code>pnorm(0.9,mean=100,sd=25)</code>     
`r I(f(FALSE))` <code>qnorm(25,mean=100,sd=0.9)</code>    
`r I(f(TRUE))` <code>qnorm(0.1,mean=100,sd=25)</code>    
`r I(f(FALSE))` <code>qnorm(0.9,mean=100,sd=25)</code>    
`r I(f(FALSE))` <code>qnorm(25,mean=100,sd=0.1)</code>    
`r I(f(FALSE))` <code>rnorm(25,mean=100,sd=0.9)</code>
```{r include=FALSE,results='hide'}
I(f(finish=TRUE))
```

* Using that threshold, what would be the mean score for African Americans such that two-thirds (66.7\%) are below the threshold? Hint: If you knew the answer, then it would produce this result.    

<code>
\> pnorm(67.96,mean=YourAnswer,sd=25)    
[1] 0.667    
</code>

```{r include=FALSE}
target=selectNumber(choices=c(47,57,63,71,81), correct=c(57), totalPts=1, name="proposal")
```
Start by proposing an answer; a guess will do. Look at the resulting response and use that to guide  refining your proposal until you hit the target response: 0.667. When you are at the target, your proposal will be close to one of these: `r I(target)`

```{r include=FALSE}
target2=selectNumber(choices=c(21,35,44,53,67,74), correct=c(44), totalPts=1, name="failureRate")
```
* Suppose scores for the African American students were to increase by 15 points on average.  What would be the failure rate (in percent)? `r I(target2)`

```{r include=FALSE}
target3=selectNumber(choices=c(0.32,0.64,1.18,1.72,2.66,5.02), correct=c(1.72), totalPts=1, name="comparison")
```
* A common way to report the difference between two groups is the number of standard deviations that separate the means.  How big is this for African American students in the Saint Paul Public Schools compared to whites (under the assumptions made for this problem)? `r I(target3)`


It would be more informative if school districts gave the actual distribution
of scores rather than the passing rate.

`r I(endProblem())`