Intro to Statistical Modeling Ch. 11 Prob. 36
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-11-36-SD")
```
A manufacturer of electrical fiber optic cables produces spools that are 50,000 feet long.  In the production process, flaws are introduced randomly.  A study of the flaws indicates that, on average, there is 1 flaw per 10000 feet.

```{r include=FALSE}
cable=selectSet(name="distribution", totalPts=1, "normal"=FALSE, "uniform"=FALSE, "binomial"=FALSE, "exponential"=FALSE, "poisson"=TRUE)
```
* Which probability distribution describes the situation of how many flaws there will be in a spool of cable. `r I(cable)`

```{r include=FALSE, eval=FALSE}
I(textItem(name="enterNumber", totalPts=2, rows=1))
```
* What's the probability that a 50,000 foot-long cable has 3 or fewer flaws?  (Enter your answer to 3 decimal places, e.g., 0.456.)     
`r I(textItem(name="enterNumber", totalPts=2, rows=1))`

<aside>
ANSWER:    
0.265 &plusmn; 0.001     
NOTE: The margin of error should be much smaller.

```{r}
ppois(3.3, 5)
```
</aside>

`r I(closeProblem())`

