Intro to Statistical Modeling Ch. 11 Prob. 45
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-11-45-SD")
```
Government data indicates that the average hourly wage for manufacturing workers in the United States is $14. (Statistics Abstract of the United States, 2002) Suppose the distribution of the manufacturing wage rate nationwide can be approximated by a normal distribution. If a worker did a nationwide job search and found that 15% of the jobs paid more than $15.30 per hour.  In order to find the standard deviation of the hourly wage for manufacturing workers, what process should we try?
```{r include=FALSE}
f=newMC(totalPts=1, name="process")
```
`r I(f(FALSE))` <code>qnorm(0.15, mean=14, sd=15.3)</code>     
`r I(f(TRUE))` Look for $x$ such that <code>pnorm(15.3, mean=14,sd=x)</code> gives 0.85    
`r I(f(FALSE))` Calculate a z-score using 1.3 as the standard deviation    
`r I(f(FALSE))` Not enough information is being given.    
`r I(f(finish=TRUE))`

`r I(endProblem())`