Intro to Statistical Modeling Ch. 11 Prob. 21
========================================================
```{r include=FALSE}
require(WriteScoreR)
require(mosaic)
newScorerSet("SM-11-21-SD")
```
Ralph's bowling scores in a single game are normally distributed with a mean of 120 and a standard deviation of 10.

```{r include=FALSE}
bowl=selectNumber(choices=c(10,120,240,360,600,710), correct=c(600), totalPts=1, name="TotalScoreMean")
```
* He plays 5 games.  What is the mean and standard deviation of his
   total score? 
  * Mean `r I(bowl)`
```{r include=FALSE}
bowl2=selectNumber(choices=c(20.14,21.69,22.36,24.31,24.71), correct=c(22.36), totalPts=1, name="TotalScoreStdDev")
```
  * Standard Deviation `r I(bowl2)`


* What is the mean and standard deviation of his average score for the 5 games?
```{r include=FALSE}
bowl3=selectNumber(choices=c(10,60,90,120,150,180), correct=c(120), totalPts=1, name="AverageScoreMean")
```
  * Mean: `r I(bowl3)`
```{r include=FALSE}
bowl4=selectNumber(choices=c(4.47,4.93,5.10,5.62,6.18), correct=c(4.47), totalPts=1, name="AverageScoreStdDev")
```
  * Standard deviation: `r I(bowl4)`



Lucky Lolly bowls games that, when the scores randomly distributed, have a mean of 100 and standard deviation of 15.

```{r include=FALSE}
bowl5=selectNumber(choices=c(1.00,2.00,2.33,3.00,3.33,7.66,120,150), correct=c(3.33), totalPts=1, name="z-scoreLolly")
```
* What is the z-score of 150 for Lolly? `r I(bowl5)`

```{r include=FALSE}
bowl6=selectNumber(choices=c(1.00,2.00,2.33,3.00,3.33,7.66,120,150), correct=c(3.00), totalPts=1, name="z-scoreRalph")
```

* What is the z-score of 150 for Ralph? `r I(bowl6)`

```{r include=FALSE}
bowl7=selectSet(name="over150", totalPts=1, "Lolly"=FALSE, "Ralph"=TRUE, "Equally likely"=FALSE, "Can't tell from the information given."=FALSE)
```
* Is Lolly or Ralph more likely to score over 150? `r I(bowl7)`

```{r include=FALSE}
bowl8=selectNumber(choices=c(1.00,2.00,2.33,3.00,3.33,7.66,120,150), correct=c(2.00), totalPts=1, name="z-scoreLolly2")
```
* What is the z-score of 130 for Lolly? `r I(bowl8)` 

```{r include=FALSE}
bowl9=selectNumber(choices=c(1.00,2.00,2.33,3.00,3.33,7.66,120,150), correct=c(1.00), totalPts=1, name="z-scoreRalph2")
```
* What is the z-score of 130 for Ralph? `r I(bowl9)`

```{r include=FALSE}
bowl10=selectSet(name="over130", totalPts=1, "Lolly"=FALSE, "Ralph"=TRUE, "Equally likely"=FALSE, "Can't tell from the information given."=FALSE)
```
* Is Lolly or Ralph more likely to score over 130? `r I(bowl10)`

`r I(closeProblem())`


