Intro to Statistical Modeling Ch. 11 Prob. 40
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-11-40-SD")
```

As part of a test of the security inspection system in an airport, a government supervisor adds 5 suitcases with illegal materials to an otherwise shipping load, bringing the total to 150 suitcases.

In order to determine whether the shipment should be accepted, security officers randomly select 15 of the suitcases and X-rays them.  If one or more of the suitcases is found to contain the materials, the entire shipment will be searched.

```{r include=FALSE}
xray=selectSet(name="ProbabilityModel", totalPts=1, "Normal"=FALSE, "Uniform"=FALSE, "Binomial"=TRUE, "Poisson"=FALSE, "Exponential"=FALSE)
```

* What probability model best applies here in describing the probability that one or more of the five added suitcases will be X-rayed? `r I(xray)`

```{r include=FALSE}
xray2=selectSet(name="Probability", totalPts=1, "1-pnorm(5,mean=150,sd=15)"=FALSE, "1-pnorm(15,mean=150,sd=5)"=FALSE, "1-punif(5,min=0, max=150)"=FALSE, "1-punif(15,min=0, max=150)"=FALSE, "1-pbinom(0,size=15,prob=5/150)"=TRUE, "1-ppois(0,45/150)"=FALSE, "1-ppois(0,5/150)"=FALSE, "Not enough information to tell."=FALSE)
```
* What is the probability that one or more of the five added suitcases
will be X-rayed? `r I(xray2)`

\begin{MultipleChoice}
\wrongc{1-pnorm(5,mean=150,sd=15)}
\wrongc{1-pnorm(15,mean=150,sd=5)}
\wrongc{1-punif(5,min=0, max=150)}
\wrongc{1-punif(15,min=0, max=150)}
\correctc{1-pbinom(0,size=15,prob=5/150)}
\wrongc{1-ppois(0,45/150)}
\wrongc{1-ppois(0,5/150)}
\wrong{Not enough information to tell.}
\end{MultipleChoice}

`r I(closeProblem())`


