Intro to Statistical Modeling Ch. 11 Prob. 41
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-11-41-SD")
```
Do the best job you can answering this question.  The information provided is not complete, but that's the way things often are.

Linda is 31 years old, single, outspoken, and very bright.  She majored in philosophy.  As a student, she was deeply concerned with issues of discrimination and social justice, and also participated in antinuclear rallies.  

* Rank the following possibilities from most likely to least likely, for instance "A B C D E":

**A.** Linda is a teacher.     
**B.** Linda works in a bookstore and takes yoga classes.    
**C.** Linda is a bank teller.    
**D.** Linda sells insurance.    
**E.** Linda is a bank teller and is active in the feminist movement.    
```{r include=FALSE,eval=FALSE}
I(textItem(name="possibilities", totalPts=2, rows=1))
```
`r I(textItem(name="possibilities", totalPts=2, rows=1))`


* Is there any relationship between the probabilities of the above items that you can be absolutely sure is true?
```{r include=FALSE, eval=FALSE}
I(textItem(name="true", totalPts=2, rows=3))
```
`r I(textItem(name="true", totalPts=2, rows=3))`


<aside>
ANSWER:     
E cannot be more likely than C, because E is a sub-case of C.
</aside>

From 'Judgments of and by representativeness,' 
in "Judgment under uncertainty : heuristics and biases"  
edited by Daniel Kahneman, Paul Slovic, Amos Tversky.
Pub info   Cambridge ; New York : Cambridge University Press, c1982.

`r I(closeProblem())`

