Intro to Statistical Modeling Ch. 11 Prob. 43
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-11-43-SD")
```
You have decided to become a shoe-maker.  Contrary to popular belief, this is a highly competitive field and you had to take the Shoe-Maker Apprenticeship Trial (SAT) as part of your apprenticeship application.  

* The Shoe-maker's union has told you that among all the people taking the SAT, the mean score is 700 and the standard deviation is 35.

```{r include=FALSE}
shoe=selectSet(name="YourPercentile", totalPts=1, "1-pnorm(750, mean=700, sd=35)"=FALSE, "pnorm(750, mean=700, sd=35)"=TRUE, "qnorm(750, mean=700, sd=35)"=FALSE, "1-qnorm(750, mean=700, sd=35)"=FALSE, "Not enough information to answer."=FALSE)
```
According to this information, what is the percentile corresponding to your SAT score of 750? `r I(shoe)`

```{r include=FALSE}
shoe2=selectSet(name="95thPercentile", totalPts=1, "pnorm(.95, mean=700, sd=35)"=FALSE, "pnorm(.95, mean=750, sd=35)"=FALSE, "qnorm(.95, mean=700, sd=35)"=TRUE, "qnorm(.95, mean=750, sd=35)"=FALSE, "Not enough information to answer."=FALSE)
```
* Your friend just told you that she scored at the 95th percentile, but
she can't remember her numerical score.  Using the information from
the Shoe-maker's union, what was her score? `r I(shoe2)`


`r I(closeProblem())`


