Intro to Statistical Modeling Ch. 9 Prob.12
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-09-12-SD")
```
Consider the following models where a response variable A is modeled by explanatory variables B, C, and D.

1. *A* ~ *B*
2. *A* ~  *B + C + B:C*
3. *A* ~ *B + C*
4. *A* ~ *B $\star$ C*
5. *A* ~ *B + D*
6. *A* ~ *B $\star$ C $\star$ D*


```{r include=FALSE}
true=selectSet(name="TF", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
Answer the following:     
* 1 is nested in model 2. `r I(true)`
```{r include=FALSE}
true2=selectSet(name="TF2", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* Model 5 is nested in model 3. `r I(true2)`
```{r include=FALSE}
true3=selectSet(name="TF3", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* Model 1 is nested in model 3. `r I(true3)`
```{r include=FALSE}
true4=selectSet(name="TF4", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* Model 5 is nested in model 1. `r I(true4)` 
```{r include=FALSE}
true5=selectSet(name="TF5", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* Model 2 is nested in model 3. `r I(true5)`
```{r include=FALSE}
true6=selectSet(name="TF6", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* Model 3 is nested in model 4. `r I(true6)`
```{r include=FALSE}
true7=selectSet(name="TF7", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* All the other models are nested in model 6. `r I(true7)`

`r I(endProblem())`
