Intro to Statistical Modeling Ch. 9 Prob. 13
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-9-13-SD")
```
Consider two models, Model 1 and Model 2, with the same response variable.   

```{r include=FALSE}
true1=selectSet(name="match", totalPts=1, "variables"=FALSE, "model terms"=TRUE)
```
* Model 1 is nested in Model 2 if the `r I(true1)`
of Model 1 are a subset of those of Model 2.

```{r include=FALSE}
true=selectSet(name="TF", totalPts=1, "True"=TRUE, "False"=FALSE)
```
  * If Model 1 is nested in Model 2, then model 1 cannot have a higher $R^2$ than model 2. `r I(true)`     

* Which of the following are nested in *A* ~ *B $\star$ C + D*?

```{r include=FALSE}
true2=selectSet(name="TF2", totalPts=1, "True"=TRUE, "False"=FALSE)
```
  * *A* ~ *B* `r I(true2)`

```{r include=FALSE}
true3=selectSet(name="TF3", totalPts=1, "True"=TRUE, "False"=FALSE)
```
  * *A* ~ *B + D* `r I(true3)`

```{r include=FALSE}
true4=selectSet(name="TF4", totalPts=1, "True"=FALSE, "False"=TRUE)
```
 * *B* ~ *C* `r I(true4)`
 
```{r include=FALSE}
true5=selectSet(name="TF5", totalPts=1, "True"=TRUE, "False"=FALSE)
```
  * *A* ~ *B + C + D* `r I(true5)`

```{r include=FALSE}
true6=selectSet(name="TF6", totalPts=1, "True"=FALSE, "False"=TRUE)
```
  * *A* ~ *B $\star$ D + C* `r I(true6)`

```{r include=FALSE}
true7=selectSet(name="TF7", totalPts=1, "True"=TRUE, "False"=FALSE)
```
  * *A* ~ *D* `r I(true7)`
  
`r I(endProblem())`
