Intro to Statistical Modeling Ch. 9 Prob. 11
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-9-11-SD")
```

Consider models with a form like this
<code>
lm( response ~ 1, data=whatever)
</code>     

The $R^2$ of such a model will always be 0. Explain why.     
`r I(textItem(name="R2", totalPts=2, rows=3))`

<aside>
ANSWER:     
This model has only an intercept term.  That means that  the model values will be the same for all the cases: the model value will be a constant.  As such, it has no case-to-case variability.  Thus, the model values account for **none** of the variability and $R^2$ will be exactly zero.  To illustrate:

```{r}
kids = fetchData("KidsFeet")
m = lm( width ~ 1, data=kids)
var( fitted(m))
```

Note that the calculated variance is zero --- it appears as $7 \times 10^{-31}$ due to computer round-off error.

Since the variance is zero, the $R^2$  is as well:
```{r}
r.squared(m)
```
</aside>

`r I(endProblem())`