Intro to Statistical Modeling Ch. 9 Prob. 10
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-9-10-SD")
```
Which of the following statements is true about $R^2$?

```{r include=FALSE}
true=selectSet(name="TF", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* $R^2$ will never go down when you add an additional explanatory term to a model. `r I(true)`


```{r include=FALSE}
f=newMC(totalPts=1, name="perfect")
```
* For a perfectly fitting model,          
`r I(f(FALSE))` $R^2$ is exactly zero     
`r I(f(TRUE))` $R^2$ is exactly one     
`r I(f(FALSE))` Neither of the above    
`r I(f(finish=TRUE))`

```{r include=FALSE}
true2=selectSet(name="var", totalPts=1, "Variance of the residuals divided by the variance of the fitted."=FALSE, "Variance of the response divided by the variance of the residuals."=FALSE, "Variance of the fitted divided by the variance of the residuals."=FALSE, "Variance of the fitted divided by the variance of the response."=TRUE, "Variance of the response divided by the variance of the fitted."=FALSE)
```
* In terms of the variances of the fitted model points, the residual, and the response variable, $R^2$ is the: `r I(true2)`

`r I(endProblem())`