Intro to Statistical Modeling Ch. 9 Reading Questions
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-9-RQ-SD")
```

* How does $R^2$ summarize the extent to which a model has captured variability?
```{r include=FALSE, eval=FALSE}
I(textItem(name="variability", totalPts=2, rows=3))
```
 `r I(textItem(name="variability", totalPts=2, rows=3))`

<aside>
ANSWER:    
$R^2$ tells what fraction of the variance in the response variable is contained in the variance of the fitted model values.  
</aside>

* What does it mean for one model to be nested in another?
```{r include=FALSE, eval=FALSE}
I(textItem(name="nesting", totalPts=2, rows=3))
```
 `r I(textItem(name="nesting", totalPts=2, rows=3))`
  
<aside>
ANSWER:    
Consider two models of the same response variable fitted to the same data, Model1 and Model2.   Model1 is nested in Model2 when Model2 has all the same explanatory terms as Model1, plus more.  In other words, Model2 contains all the explanatory terms that appear in Model1.
</aside>

* How does the correlation coefficient differ from $R^2$? 
```{r include=FALSE,eval=FALSE}
I(textItem(name="correlation", totalPts=2, rows=3))
```
 `r I(textItem(name="correlation", totalPts=2, rows=3))`

<aside>
ANSWER:    
The correlation coefficient $r$ is $\sqrt{R^2}$ from the very simple model *A* ~ *B* where both A and B are quantitative variables.  Or, put another way, $R^2$ is a generalization of the correlation coefficient to allow there to be
more than one explanatory term and to allow categorical variables to be used as explanatory variables. The sign information that would appear in $r$ is given in the sign of the coefficients, rather than in $R^2$, which is always positive.
</aside>

`r I(closeProblem())`
