Intro to Statistical Modeling Ch. 9 Prob. 1
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-9-1-SD")
```

The $R^2$ statistic is the ratio of the variance of the fitted values to the variance of the response variable.  

Using the `KidsFeet` data:

```{r include=FALSE}
feet=selectNumber(choices=c(0.053,0.119,0.183,0.260,0.346), correct=c(0.260), totalPts=1, name="var1")
```
* Find the variance of the response variable in the model *width* ~ *sex + length + sex:length* . `r I(feet)`

<aside>
ANSWER:     
```{r}
kids = fetchData("KidsFeet")
var( kids$width)
```
</aside>

```{r include=FALSE}
feet2=selectNumber(choices=c(0.053,0.119,0.183,0.260,0.346), correct=c(0.119), totalPts=1, name="var2")
```
* Find the variance of the fitted values from the model `r I(feet2)`

<aside>
ANSWER:     
```{r}
mod = lm( width ~ sex*length, data=kids)
var( fitted(mod))
```
</aside>

```{r include=FALSE}
feet3=selectNumber(choices=c(0.20,0.29,0.46,0.53,0.75), correct=c(0.46), totalPts=1, name="R2")
```
* Compute the $R^2$ as the ratio of these two variances. `r I(feet3)`

<aside>
ANSWER:     
```{r}
0.1194/0.2597
```
or, more precisely
```{r}
var( fitted(mod)) / var(kids$width)
```
</aside>

```{r include=FALSE}
feet4=selectSet(name="YN", totalPts=1, "Yes"=TRUE, "No"=FALSE)
```
* Is this the same as the "Multiple $R^2$" given in the <code>summary(mod)</code> report? `r I(feet4)`


`r I(closeProblem())`

