Intro to Statistical Modeling Ch. 9 Prob. 21
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-9-21-SD")
```
Here is a set of models:

Model A:  *wage* ~ *1*

Model B:  *wage* ~ *age + sex*

Model C:  *wage* ~ *1 + age $\star$ sex*

Model D:  *wage* ~ *educ*

Model E:  *wage* ~ *educ* + *age* - 1

Model F:  *wage* ~ *educ:age*

Model G:  *wage* ~ *educ $\star$ age $\star$ sex*

You may want to try fitting each of the models to the Current Population Survey data `CPS85` to make sure you understand how the * shorthand for interaction and main effects expands to a complete set of terms.  That way you can see exactly which coefficients are calculated for any of the models.

Answer the following:
```{r include=FALSE}
true=selectSet(name="BinA", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* B is nested in A. `r I(true)`
<aside>
ANSWER:     
False, A is nested in B.  The intercept term 1 is implicitly included in B.
</aside>

```{r include=FALSE}
true2=selectSet(name="DinE", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* D is nested in E. `r I(true2)` 

<aside>
ANSWER:      
False.  D includes the intercept term, but E does not.
</aside>

```{r include=FALSE}
true3=selectSet(name="BinC", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* B is nested in C. `r I(true3)`

<aside>
ANSWER:     
True.  C includes all the terms in B plus the interaction term *age*:*sex*.
</aside>

```{r include=FALSE}
true4=selectSet(name="AllinG", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* All of the models A-F are nested in G. `r I(true4)`

<aside>
ANSWER:     
True. The notation *educ* $\star$ *age* $\star$ *sex* includes all the main terms, all the two-variable interaction terms, a three-variable interaction term.  The intercept is also included, by default.
</aside>

```{r include=FALSE}
true5=selectSet(name="DinF", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* D is nested in F. `r I(true5)` 

<aside>
ANSWER:     
False.  F includes an intercept and an interaction term *educ*:*age*, but not the main term *educ*.
</aside>

\item At least one of the models
A-G is nested in \model{\VN{educ}}{\VN{age}}. \TrueOrFalse[itemname=wrongresponse]{F} 

\begin{AnswerText}
False.  The model \model{\VN{educ}}{\VN{age}} has a different response variable than any of the models A-G.
\end{AnswerText}


\end{enumerate}
