Intro to Statistical Modeling Ch. 9 Prob. 4
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-9-5-SD")
```
For each of the following pairs of models, mark the statement that is most correct.

#### Part 1 

* **Model 1.** *A* ~ *B + C*
* **Model 2.** *A* ~ *B $\star$ C*

```{r include=FALSE}
f=newMC(totalPts=1, name="statement1")
```
`r I(f(FALSE))` Model 1 can have a higher $R^2$ than Model 2     
`r I(f(TRUE))` Model 2 can have a higher $R^2$ than Model 1     
`r I(f(FALSE))` The $R^2$ values will be the same.     
`r I(f(FALSE))` None of the above are necessarily true.     
`r I(f(finish=TRUE))`

<aside>
ANSWER:    
Model 1 is nested within Model 2, so Model 2 can have a higher $R^2$ than Model 1.
</asid>

 
#### Part 2

* **Model 1.** *A* ~ *B + C*     
* **Model 2.** *B* ~ *A $\star$ C*

```{r include=FALSE}
g=newMC(totalPts=1, name="statement2")
```
`r I(g(FALSE))` Model 1 can have a higher $R^2$ than Model 2     
`r I(g(FALSE))` Model 2 can have a higher $R^2$ than Model 1     
`r I(g(FALSE))` The $R^2$ values will be the same.     
`r I(g(TRUE))` None of the above are necessarily true.    
`r I(g(finish=TRUE))`

<aside>
ANSWER:     
At first glance it might seem that Model 1 is nested in Model 2, but notice that the two models have different explanatory variables.  This means that no definite statement can be made about the relationship between the $R^2$ for the two models.  (However, if there is only a single explanatory variable --- not the situation here --- then there's more to be said.  See the "Going Further" item at the end of this problem.
</aside>

#### Part 3

* **Model 1.** *A* ~ *B + C + B:C*
* **Model 2.** *A* ~ *B $\star$ C*

```{r include=FALSE}
h=newMC(totalPts=1, name="statement3")
```
`r I(h(FALSE))` Model 1 can have a higher $R^2$ than Model 2     
`r I(h(FALSE))` Model 2 can have a higher $R^2$ than Model 1     
`r I(h(TRUE))` The $R^2$ values will be the same.     
`r I(h(FALSE))` None of the above are necessarily true.      
`r I(h(finish=TRUE))`

#### Going further 

In answering this question, you might want to try out a few examples using real data: just pick two quantitative variables to stand in for A and B.

What will be the relationship between $R^2$ for the following two models?

* **Model 1.** *A* ~ *B*     
* **Model 2.** *B* ~ *A*

```{r include=FALSE}
j=newMC(totalPts=1, name="statement4")
```
`r I(j(FALSE))` Model 1 can have a higher $R^2$ than Model 2     
`r I(j(FALSE))` Model 2 can have a higher $R^2$ than Model 1     
`r I(j(TRUE))` The $R^2$ values will be the same.     
`r I(j(FALSE))` None of the above are necessarily true.    
`r I(j(finish=TRUE))`

<aside>
ANSWER:     
Not an entirely fair question.

It's reasonable to look at the two models, note that neither is nested within the other, and conclude that none of statements A, B, or C are necessarily true.  

As it happens, however, each of Model 1 and Model 2 describe the relationship between A and B using the simple model involved in the correlation coefficient.  The correlation coefficient describes the alignment of A and B, which is the same as the alignment of B and A.  

To illustrate, consider the following example:
```{r}
kids = fetchData("KidsFeet")
m1 = lm( width ~ length, data=kids)
m2 = lm( length ~ width, data=kids)
r.squared(m1)
```

```{r}
r.squared(m2)
```

However, this simple relationship won't hold true in general if there is more than one explanatory variable.
</aside>

`r I(endProblem())`