Intro to Statistical Modeling Ch. 9 Prob. 2
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-9-2-SD")
```

The variance of a response variable A is 145 and the variance of the residuals from the model *A* ~ *1 + B* is 45.

```{r include=FALSE}
model=selectSet(name="varFit", totalPts=1, "45"=FALSE, "100"=TRUE, "145"=FALSE, "190"=FALSE, "Cannot tell"=FALSE)
```
* What is the variance of the fitted model values? `r I(model)`

<aside>
ANSWER:     
Remember that the variance of the response can be split into two parts: the variance of the fitted model values and the variance of the residuals.  So, $145 = 45 + \mbox{var of fitted model values}$.  So the variance of the fitted model values is 100.
</aside>

```{r include=FALSE}
model2=selectSet(name="r2", totalPts=1, "0"=FALSE, "45/145"=FALSE, "100/145"=TRUE, "100/190"=FALSE, "145/190"=FALSE, "Cannot tell"=FALSE)
```
* What is the $R^2$ for this model? `r I(model2)`

<aside>
ANSWER:      
$R^2$ compares the variance of the fitted model values to the variance of the response, so $100/145$.
</aside>

`r I(endProblem())`