Intro to Statistical Modeling Ch. 5 Prob. 12
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-5-12-SD")
opts_chunk$set(dev="svg",fig.width=3,fig.height=3,fig.show="hide")
```

```{r include=FALSE}
set.seed(53)
A = runif(10,min=5,max=15)+ rnorm(10,0,2)
B = rnorm(40,mean=15,sd=sd(A))
heights =c(mean(A),mean(B)) 
draw.them = function(lowA,highA,lowB,highB) {
barplot( heights, names.arg=c('Wild-type','Mutant'),
   width=.6,cex.axis=1,cex.names=1,ylim=c(0,25),space=1,xlim=c(0,2.5))
positions = c(0.9, 2.15)
arrows(positions, c(lowA,lowB), positions, c(highA,highB),angle=90,code=3,
   length=.1,lwd=2 )
points( rep(positions[1]-.45,length(A)), A, pch=20)
points( rep(positions[2]-.45,length(B)), B, pch='x')
}
```

Scientific papers very often contain graphics with "error bars."
Unfortunately, there is little standardization of what such error bars
mean so it is important for the reader to pay careful attention in 
interpreting the graphs.  

The following four graphs --- A through D ---
each show a distribution of data along with error bars.  The meaning
of the bars varies from graph to graph according to different
conventions used in different areas of the scientific literature.
In each graph, the height of the filled bar is the mean of the data.
Your job is to associate each error bar with its meaning.  You can do
this by comparing the actual data (shown as dots) with the error bar.

Graph A | Graph B | Graph C | Graph D|     
|:-----:|:-----:|:-----:|:-----:|
<img src="figure/C5-12-sderror.svg" width="100%"> | <img src="figure/C5-12-sd.svg" width="100%"> | <img src="figure/C5-12-range.svg" width="100%"> | <img src="figure/C5-12-confinterval.svg" width="100%">



```{r C5-12-sderror,echo=FALSE}
# sd error
draw.them( mean(A)-sd(A)/sqrt(10),mean(A)+sd(A)/sqrt(10), mean(B)-sd(B)/sqrt(30),mean(B)+sd(B)/sqrt(30))
```


```{r C5-12-sd,echo=FALSE}
# sd
draw.them( mean(A)-sd(A),mean(A)+sd(A),mean(B)-sd(B),mean(B)+sd(B))
```

```{r C5-12-range,echo=FALSE}
# range
draw.them( min(A),max(A),min(B),max(B))
```

```{r C5-12-confinterval,echo=FALSE}
# conf. interval
draw.them( mean(A)-2*sd(A)/sqrt(10),mean(A)+2*sd(A)/sqrt(10),
   mean(B)-2*sd(B)/sqrt(30),mean(B)+2*sd(B)/sqrt(30))
```


```{r include=FALSE}
scientific=selectSet(name="range", totalPts=1, "Graph A"=FALSE, "Graph B"=FALSE, "Graph C"=TRUE, "Graph D"=FALSE)
```
* Range of the data `r I(scientific)`

```{r include=FALSE}
scientific2=selectSet(name="stddev", totalPts=1, "Graph A"=FALSE, "Graph B"=TRUE, "Graph C"=FALSE, "Graph D"=FALSE)
```
* Standard deviation of the data `r I(scientific2)`

```{r include=FALSE}
scientific3=selectSet(name="stdError", totalPts=1, "Graph A"=TRUE, "Graph B"=FALSE, "Graph C"=FALSE, "Graph D"=FALSE)
```
* Standard error of the mean `r I(scientific3)`

```{r include=FALSE}
scientific4=selectSet(name="confidence", totalPts=1, "Graph A"=FALSE, "Graph B"=FALSE, "Graph C"=FALSE, "Graph D"=TRUE)
```
* 95% confidence interval on the mean `r I(scientific4)`


This problem is based on
G. Cumming, F. Fidler, and DL Vaux (2007), "Error bars in
  experimental biology", *J. Cell Biology* **177**(1):7-11

<aside>
ANSWER:
The easiest one to spot is the range, where the error bars for both
groups extend to the extreme range of the data. Graph C. 

The standard error of the mean will be the standard deviation divided
by $\sqrt{n}$.  The standard error is always smaller than the standard deviation. Also, typically about 2/3 of the data falls within $\pm$
one standard deviation.  The bars in Graph B cover about 2/3 of the
data and are bigger than the bars in Graphs A and D, so the standard
deviation is shown in Graph B.

By elimination, the graphs A and D must be the standard error and the
95% confidence interval.  The 95% confidence interval is $2 \times$
the standard error, so Graph D must be the confidence interval.
</aside>

`r I(endProblem())`
