Intro to Statistical Modeling Ch.5 Prob. 17
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-05-30-SD")
```

Standard errors and confidence interval apply not just to model
coefficients, but to any numerical description of a variable.
Consider, for instance, the median or IQR or standard deviation, and
so on.

A quick and effective way to find a standard error is a method called
**bootstrapping**, which involves repeatedly resampling the
variable and calculating the description on each resample.  This gives the
sampling distribution of the description.  From the sampling
distribution, the standard error --- which is just the standard
deviation of the sampling distribution --- can be computed.

Here's an example, based on the inter-quartile range
of the kids' foot length measurements.

First, compute the desired sample statistic on the actual data

```{r}
IQR(kids$length)
```

Next, modify the statement to incorporate resampling of the data:

```{r}
IQR(resample(kids$length))
```


Finally, run this statement many times to generate the sampling
distribution and find the standard error of this distribution:

```{r}
samps = do(1000) * IQR(resample(kids$length))
sd(samps)
```

Use the bootstrapping method  to find an estimate of the standard error of each of these
sample statistics on the kids' foot length data:

```{r include=FALSE}
boot=selectNumber(choices=c(0.01,0.07,0.14,0.24,0.34,0.71,1.29,1.32,24.6), correct=c(0.24), totalPts=1, name="median")
```
* The sample median.  (Pick the closest answer.) `r I(boot)`

```{r include=FALSE}
boot2=selectNumber(choices=c(0.01,0.07,0.14,0.24,0.34,0.71,1.29,1.32,24.6), correct=c(0.14), totalPts=1, name="stdev")
```
* The sample standard deviation. (Pick the closest answer.) `r I(boot2)`

```{r include=FALSE}
boot3=selectNumber(choices=c(0.01,0.07,0.14,0.24,0.34,0.71,1.29,1.32,24.6), correct=c(0.34), name="75perc", totalPts=1)
```
* The sample 75th percentile. `r I(boot3)`

Bootstrapping works well in a broad set of circumstances, but if you
have a very small sample, say less than a dozen cases, you should be
skeptical of the result.

`r I(endProblem())`
