Intro to Statistical Modeling Ch. 5 Prob. 40
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-05-40-SD")
```

In this activity, you are going to look at the sampling distribution
and how it depends on the size of the sample.  This will be done by
simulating a sample drawn from a population with known properties.  In
particular you'll be looking at a variable that is more or less like
the distribution of human adult heights --- normally distributed with a mean
of 68 inches and a standard deviation of 3 inches. 

Here's one random sample of size $n=10$ from this simulated
population:
```{r}
rnorm(10, mean=68, sd=3)
```

These are the heights of a random sample of $n=10$.  The sampling
distribution refers to some numerical description of such data, for
example, the  *sample mean*.    Consider this sample mean the
output of a single trial.
```{r}
mean( rnorm(10, mean=68, sd=3) )
```

If you gave exactly this statement, it's very likely that your result
was different. That's because you have a different random sample ---
<code>rnorm</code> generates random numbers.  And if you repeat the
statement, you'll likely get a different value again, for instance:
```{r}
mean( rnorm(10, mean=68, sd=3) )
```

Note that both of the sample means above differ somewhat from the population
mean of 68.  

The point of examining a sampling distribution is to be able to see
the reliability of a random sample.  Do to this, you generate many
trials --- say, 1000 --- and look at the distribution of the trials.  

For example, here's how to look at the sampling distribution for the
mean of 10 random cases from the population:
```{r results='hide'}
s = do(1000)*mean( rnorm(10, mean=68, sd=3) )
```
By examining the distribution of the values stored in <code>s</code>, you
can see what the sampling distribution looks like.

Generate your own sample

1. What is the mean of this distribution? `r I(textItem(name="mean", totalPts=2, rows=1))`

2. What is the standard deviation of this distribution? `r I(textItem(name="stddev", totalPts=2, rows=1))`

3. What is the shape of this distribution? `r I(textItem(name="shape", totalPts=2, rows=1))`


Now modify your simulation to look at the sampling distribution for $n=1000$.

4. What is the mean of this distribution? `r I(textItem(name="mean2", totalPts=2, rows=1))`

5. What is the standard deviation of this distribution? `r I(textItem(name="stddev2", totalPts=2, rows=1))`

6. What is the shape of this distribution? `r I(textItem(name="shape2", totalPts=2, rows=1))`
 

Which of these two sample sizes, $n=10$ or $n=1000$, gave a sampling
distribution that was more reliable?  How might you measure the
reliability?

The idea of a sampling distribution applies not just to means, but to
any numerical description of a variable, to the coefficients on
models, etc.

Now modify your computer statements to examine the **sampling
distribution of the standard deviation** rather than the mean.  Use a
sample size of $n=10$.    (Note: Read the previous
sentence again.  The statistic you are asked to calculate is the
**sample standard deviation**, not the sample mean.)

7. What is the mean of this distribution? `r I(textItem(name="mean3", totalPts=2, rows=1))`

8. What is the standard deviation of this distribution? `r I(textItem(name="stddev3", totalPts=2, rows=1))`
 
9. What is the shape of this distribution? `r I(textItem(name="shape3", totalPts=2, rows=1))`

Repeat the above calculation of the distribution of the sample standard deviation with $n=1000$.

10. What is the mean of this distribution? `r I(textItem(name="mean4", totalPts=2, rows=1))`

11. What is the standard deviation of this distribution? `r I(textItem(name="stddev4", totalPts=2, rows=1))`

12. What is the shape of this distribution? `r I(textItem(name="shape4", totalPts=2, rows=1))`


For this simulation of heights, the population standard deviation was set to 3.  You expect the result from a random sample to be close to the
population parameter.   Which of the two sample sizes, $n=10$ or $n=1000$ gives results that are closer to the population value?     
`r I(textItem(name="closerToValue", totalPts=2, rows=1))`

`r I(endProblem())`