Intro to Statistical Modeling Ch. 10 Prob. 5
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-10-5-SD")
```

Consider two models that you are to fit to a single data set involving three variables: A, B, and C.

* **[Model 1]** *A* ~ *B*     

* **[Model 2]** *A* ~ *B* + *C*

```{r include=FALSE}
f=newMC(totalPts=1)
```
When should you say that Simpson's Paradox is occuring?      
`r I(f(FALSE))` When Model 2 has a lower $R^2$ than Model 1.     
`r I(f(FALSE))` When Model 1 has a lower $R^2$ than Model 2.     
`r I(f(TRUE))` When the coef. on B in Model 2 has the opposite sign to the coef. on B in Model 1.     
`r I(f(FALSE))` When the coef. on C in Model 2 has the opposite sign to the coef. on B in Model 1.     
```{r include=FALSE, results='hide'}
I(f(finish=TRUE))
```

```{r include=FALSE}
true=selectSet(name="TorF", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
True or False: If B is uncorrelated with A, then the coefficient on B in the model *A* ~ *B* must be zero. `r I(true)`

```{r include=FALSE}
true2=selectSet(name="TorF2", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
True or False: If B is uncorrelated with A, then the coefficient   on B in a model *A* ~ *B* + *C* must be zero. `r I(true2)`

```{r include=FALSE}
true3=selectSet(name="TorF3", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
True or False: Simpson's Paradox can occur if B is uncorrelated with C. `r I(true3)`

`r I(closeProblem())`


###### Based on a suggestion by student Atang Gilika.

