Intro to Statistical Modeling Ch. 10 Prob. 11
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-10-11-SD")
```
A study on drug D indicates that patients who were given the drug were **less** likely to recover from their condition C.  Here is a table showing the overall results:

Drug | # Recovered | # Died | Recovery Rate
|:----:|:----:|:----:|:----:|
Given | 1600 | 2400 | 40%
Not given | 2000 | 2000 | 50%


Strangely, when investigators looked at the situation separately for males and females, they found that the drug *improves* recovery for each group:

**Females** 

Drug | # Recovered | # Died | Recovery Rate
:---:|:---:|:---:|:---:|
Given | 900 | 2100 | 30%
Not given | 200 | 800 | 20%

**Males**  

Drug | # Recovered | # Died | Recovery Rate
:---:|:---:|:---:|:---:|
Given | 700 | 300 | 70%
Not given | 1800 | 1200 | 60%


```{r include=FALSE,eval=FALSE}
I(textItem(name="simpsons-and-drug", totalPts=2, rows=3))
```
Which is right?  Does the drug improve recovery or hinder recovery? What advice would you give to a physician about whether or not to prescribe the drug to her patients?  Give enough of an explanation that the physician can judge whether your advice is reasonable.     
`r I(textItem(name="simpsons-and-drug", totalPts=2, rows=3))`


###### Based on an example from Judea Pearl (2000) *Causality: Models, Reasoning, and Inference*, Cambridge Univ. Press, p. 175

`r I(closeProblem())`

