Intro to Statistical Modeling Ch. 10 Prob. 10
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-10-10-SD")
```

Standard & Poor's is a RATING AGENCY that provides information about various financial instruments such as stocks and bonds.  The S&P 500 Stock Index, for instance, provides a summary of the value of stocks. 

Bonds issued by governments, corporations, and other entities are rated using letters.  As described on the Standard & Poor's website, the ratings levels are 
AAA, AA+, AA, AA-, A+, A, A-, BBB+, BBB, BBB-, BB+, BB, BB-, B+, B, B-, CCC+, CCC, CCC-, CC, C, and D. The AAA rating is the best. ("The obligor's capacity to meet its financial commitment on the obligation is extremely strong.")  D is the worst. ("The `D' rating category is used when payments on an obligation are not made on the date due ....")  

```{r include=FALSE}
SandP=selectSet(name="TorF", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* The bond ratings are a categorical variable. `r I(SandP)`
```{r include=FALSE}
SandP2=selectSet(name="TorF2", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* The bond ratings are an ordinal variable. `r I(SandP2)`


Bonds are a kind of debt; they pay interest and the principal is paid back at the end of a maturity period. The people and institutions who invest in bonds
are willing to accept somewhat lower interest payments in exchange for greater security.  Thus, AAA-rated bonds tend to pay the lowest interest rates and worse-rated bonds pay more.  A report on interest rates on bonds (www.fmsbonds.com, for 8/21/2008) listed interest rates on municipal bonds:

Issue | Maturity | Rate
|:----:|:----:|:----:|
| | AAA Rated | |
National | 10 Year | 3.75
National | 20 Year | 4.60
National | 30 Year | 4.75
Florida | 30 Year | 4.70
| | AA Rated | |
National | 10 Year | 3.90
National | 20 Year | 4.70
National | 30 Year | 4.85
Florida | 30 Year | 4.80
| | A Rated | |
National | 10 Year | 4.20
National | 20 Year | 5.05
National | 30 Year | 5.20
Florida | 30 Year | 5.15



```{r include=FALSE}
SandP3=selectSet(name="ExplanVariables", totalPts=1, "Two: Issue and Maturity"=FALSE, "Three: Issue, Maturity, and S & P rating"=TRUE, "Four: Issue, Maturity, S & P Rating, and Interest Rate"=FALSE)
```
How many explanatory variables are given in this table to account for the interest rate: `r I(SandP3)`

```{r include=FALSE}
SandP4=selectNumber(choices=c(0.05,0.15,0.25,0.30,0.40), correct=c(0.15), totalPts=1, name="ChangeInRate")
```
Judging from the table, and holding all other explanatory variables constant, what is the change in interest rate associated with a change from AAA to AA rating? `r I(SandP4)`

```{r include=FALSE}
SandP5=selectNumber(choices=c(0.15, 0.50, 0.85, 1.20, 1.45), correct=c(0.85), totalPts=1, name="ChangeinRate2")
```
Again, holding all other explanatory variables constant, what is the change in interest rate for a 10-year compared to a 20-year maturity bond?  (Pick the closest answer.)`r I(SandP5)`


Sometimes it is unclear when a variable should be considered quantitative and when it should be taken as categorical.  For example, the *maturity* variable looks on the surface to be quantitative (10-year, 20-year, 30-year, etc.).  What is it about these data that suggests that it would be unrealistic to treat *maturity* as a quantitative variable in a model of *interest rate*?
```{r include=FALSE, eval=FALSE}
I(textItem(name="maturity", totalPts=2, rows=3))
```
`r I(textItem(name="maturity", totalPts=2, rows=3))`


<aside>
ANSWER:    
If *maturity* were treated as a quantitative variable, the difference in interest rate between 10-year and 20-year maturity would be modeled as the same as the difference between 20-year and 30-year maturity.  Yet this is far from the case in the data.
</aside>

`r I(endProblem())`


