Intro to Statistical Modeling Ch. 1 Prob. 1.01
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-01-1.01-SD")
```

Many fields of natural and social science have principles that are identified by name.  Sometimes these are called "laws", sometimes "principles", "theories", etc.  Some examples include:

Kepler's Law      
Newton's Laws of Motion      
Ohm's Law      
Grimm's Law      
Nernst Equation     
Raoult's Law      
Nash Equilibrium      
Boyle's Law     
Zipf's Law      
Law of Diminishing Marginal Utility      
Pareto Principle           
Snell's Law      
Hooke's Law      
Fitt's Law     
Laws of Supply and Demand      
Ideal Gas Law      
Newton's Law of Cooling          
Le Chatelier's Principle      
Poiseuille's Law      

These laws and principles can be thought of as models.  Each is a
description of a relationship.  For instance, Hooke's law relates the extension and stiffness of a spring to the force exerted by the spring.  The laws of supply and demand relate the quantity of a good to the price and postulates that the market price is established at the equilibrium of supply and demand.

Pick a law or principle from an area of interest to you --- chemistry, linguistics, sociology, physics, ... whatever.  Describe the law, what quantities or qualities it relates to one another, and the ways in which the law is a model, that is, a representation that is suitable for some purposes or situations and not others.

```{r eval=FALSE, include=FALSE}
I(textItem(name="laworprinciple", rows=4, totalPts=2))
```

Enter your answer here:      
`r I(textItem(name="laworprinciple", rows=4, totalPts=2))`

An example is given below:

>EXAMPLE: As described in the text, Hooke's Law, $f = -k x$, relates the force ($f$), the stiffness ($k$) and the extension past resting length ($x$) for a spring.  It is a useful and accurate approximation for small extensions.  For large extensions, however, springs are permanently distorted or break.  Springs involve friction, which is not included in the law.  Some springs, such as passive muscle, are really composites and show a different pattern, e.g., $f = -  k \ {x^3} / {|x|}$ for moderate sized extensions.

`r I(endProblem())`
