Intro to Statistical Modeling Ch. 1 Prob. 1.02
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-01-1-01-SD")
```

NOTE: Remember to load the <code>mosaic</code> package before starting:

<code>library(mosaic)</code>

Each of the following statements has a syntax mistake.  Write the
statements properly and give a sentence saying what was wrong. (Cut and paste the correct statement from R, along with any output that R gives and your sentence saying what was wrong in the original.)

Here's an example:      

>QUESTION: What's wrong with this statement?     
><code>a = fetchData(myfile.csv)</code>     
     


>ANSWER: It should be <code>a = fetchData("myfile.csv")</code>  The file name is a character string and therefore should be in quotes.  Otherwise it's treated as an object name and there is no object called myfile.csv.     
     



Now for the real thing.  Say what's wrong with each of these
statements for the purpose given:

```{r include=FALSE}
f = newMC(totalPts=1,name="seqsemi")
```
* <code>seq(5;8)</code> to give <code>[1] 5 6 7 8</code>
  
`r I(f(FALSE))` Nothing is wrong.     
`r I(f(TRUE))` Use a comma instead of a semi-colon to separate arguments:  <code>seq(5,8)</code>.     
`r I(f(FALSE))` It should be <code>seq(5 to 8)</code>.  
`r I(f(finish=TRUE))`

<aside>
ANSWER: The semicolon is not a valid separator between arguments.  The statement should be <code>seq(5,8)</code>.
</aside>

* <code>cos 1.5</code> to calculate the cosine of 1.5 radians
 
```{r include=FALSE, eval=FALSE}
I(textItem(name="cosine", rows=4, totalPts=2))
```

`r I(textItem(name="cosine", rows=4, totalPts=2))`

<aside>
ANSWER:The parentheses have been left out.  It should be <code>cos(1.5)</code>.
</aside>

* <code>3 + 5 = x</code> to make x take the value 3 + 5
 
```{r include=FALSE, eval=FALSE}
I(textItem(name="xvalue", rows=4, totalPts=2))
```

`r I(textItem(name="xvalue", rows=4, totalPts=2))`

<aside>
ANSWER: Assignment statements should have the object name on the left: <code>x = 3 + 5</code>
</aside>

* <code>sqrt[4*98]</code> to find the square root of 392
 
```{r include=FALSE, eval=FALSE}
I(textItem(name="squareroot", rows=4, totalPts=2))
```

`r I(textItem(name="squareroot", rows=4, totalPts=2))`

<aside>
ANSWER: Use parentheses, not square brackets, to invoke an operator: <code>sqrt(4*98)</code>.
</aside>

* <code>10,000 + 4,000</code> adding two numbers to get 14,000
 
```{r include=FALSE, eval=FALSE}
I(textItem(name="addition", rows=4, totalPts=2))
```

`r I(textItem(name="addition", rows=4, totalPts=2))`

<aside>
ANSWER: Don't punctuate numbers with commas, just the digits: <code>10000 + 4000</code>.
</aside>

* <code>sqrt(c(4,15,25,36)) = 4</code> intended to give
 <code>[1] FALSE TRUE FALSE FALSE</code>
 
```{r include=FALSE, eval=FALSE}
I(textItem(name="squareroot2", rows=4, totalPts=2))
```

`r I(textItem(name="squareroot2", rows=4, totalPts=2))`

<aside>
ANSWER: Only a single <code>=</code> was used, the assignment operator rather than equality.  It should be <code>sqrt(c(4,16,25,36)) == 4</code>
</aside>

* <code>fruit = c(apple, berry, cherry)</code> to create a collection of names
 <code>[1] "apple" "berry" "cherry"</code>
 
```{r include=FALSE, eval=FALSE}
I(textItem(name="collectionofnames", rows=4, totalPts=2))
```

`r I(textItem(name="collectionofnames", rows=4, totalPts=2))`

<aside>
ANSWER: The character strings have to be quoted to distinguish them from object names.  It should be <code>fruit = c( "apple", "berry", "cherry")</code>.
</aside>

* <code>x = 4(3+2)</code> where x is intended to be assigned the value 20

```{r include=FALSE, eval=FALSE}
I(textItem(name="valueassign", rows=4, totalPts=2))
```

`r I(textItem(name="valueassign", rows=4, totalPts=2))`

<aside>
ANSWER: The multiplication operator needs to be specified explicitly and not implicitly as in algebraic notation.  The statement should be <code>x = 4*(3+2)</code>.
</aside>

* <code>x/4 = 3+2</code> where x is intended to be assigned the value 20

```{r include=FALSE, eval=FALSE}
I(textItem(name="valueassign2", rows=4, totalPts=2))
```

`r I(textItem(name="valueassign2", rows=4, totalPts=2))`

<aside>
ANSWER: Only an object name can be on the left side of the assignment operator.  It should be <code>x = 4*(3+2)</code>
</aside>

`r I(endProblem())`
