Intro to Statistical Modeling Ch.1 Prob. 1.05
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-01-P1-05-SD")
```

According to legend, when the famous mathematician Johann Carl Friedrich Gauss
(1777-1855) was a child, one of his
teachers tried to distract him with busy work: 
add up the numbers 1 to 100.   Gauss did this easily and
immediately without a computer.  But using the computer, which of the
following commands will do the job?
```{r include=FALSE}
f = newMC(totalPts=1)
```

`r I(f(FALSE))` sum(1,100)     
`r I(f(FALSE))` seq(1,100)     
`r I(f(FALSE))` sum of seq(1,100)     
`r I(f(TRUE))` sum(seq(1,100))     
`r I(f(FALSE))` seq(sum(1,100))     
`r I(f(FALSE))` sum(1,seq(100))     

```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```

<aside>
Answer:
A just sums two numbers: $1$ and $100$; B only gives the sequence from $1$ to $100$ without summing them; C was written in human language, not computer ( R ) language; for E, the inside summation is performed first (giving a value of $101$), and so the entire command produces a sequence from $1$ to $101$; for F, a sequence from $1$ to $100$ is produced first, then it sums every element of this sequence AND $1$, with $1$ being redundant. Therefore, only D produces the correct output.
</aside>

`r I(closeProblem())`
