Intro to Statistical Modeling Ch. 7 Prob. 4 
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-7-4-SD")
```
For some simple models, the coefficients can be interpreted as grand means, group-wise means, or differences between group-wise means. In each of the following, *A*, *B*, and *C* are quantitative variables and *color* is a categorical variable with levels "red," "blue," and "green."

The model *A* ~ *color* gave these coefficients:

Term | Coefficient
|:----|:----:|
Intercept | 10
*color* Blue | 5
*color* Green | 12

```{r include=FALSE}
coef=selectSet(name="blue", totalPts=1, "5"=FALSE, "10"=FALSE, "12"=FALSE, "15"=TRUE, "17"=FALSE, "22"=FALSE, "27"=FALSE, "unknown"=FALSE)
```
* What is the mean of *A* for those cases that are Blue: `r I(coef)`

```{r include=FALSE}
coef2=selectSet(name="green", totalPts=1, "5"=FALSE, "10"=FALSE, "12"=FALSE, "15"=FALSE, "17"=TRUE, "22"=FALSE, "27"=FALSE, "unknown"=FALSE)
```
* What is the mean of *A* for those cases that are Green: `r I(coef2)`

```{r include=FALSE}
coef3=selectSet(name="red", totalPts=1, "5"=FALSE, "10"=TRUE, "12"=FALSE, "15"=FALSE, "17"=FALSE, "22"=FALSE, "27"=FALSE, "unknown"=FALSE)
```
* What is the mean of *A* for those cases that are Red: `r I(coef3)`

```{r include=FALSE}
coef4=selectSet(name="grandmean", totalPts=1, "5"=FALSE, "10"=TRUE, "12"=FALSE, "15"=FALSE, "17"=FALSE, "22"=FALSE, "27"=FALSE, "unknown"=FALSE)
```
* What is the grand mean of *A* for all cases: `r I(coef4)`     


The model *B* ~ color - 1 gave these coefficients:

Term | Coefficient
|:----|:----:|
*color* Red | 100
*color* Blue | -40
*color* Green | 35

```{r include=FALSE}
coef5=selectSet(name="Blue2", totalPts=1, "-40"=TRUE, "-5"=FALSE, "0"=FALSE, "35"=FALSE, "60"=FALSE, "65"=FALSE, "100"=FALSE, "135"=FALSE, "unknown"=FALSE)
```
* What is the group mean of *B* for those cases that are Blue: `r I(coef5)`

```{r include=FALSE}
coef6=selectSet(name="Red2", totalPts=1, "-40"=FALSE, "-5"=FALSE, "0"=FALSE, "35"=FALSE, "60"=FALSE, "65"=FALSE, "100"=TRUE, "135"=FALSE, "unknown"=FALSE)
```
* What is the group mean of *B* for those cases that are Red: `r I(coef6)` 

```{r include=FALSE}
coef7=selectSet(name="Green2", totalPts=1, "-40"=FALSE, "-5"=FALSE, "0"=FALSE, "35"=TRUE, "60"=FALSE, "65"=FALSE, "100"=FALSE, "135"=FALSE, "unknown"=FALSE)
```
* What is the group mean of *B* for those cases that are Green: `r I(coef7)`

```{r include=FALSE}
coef8=selectSet(name="GrandMean2",totalPts=1, "-40"=FALSE, "-5"=FALSE, "0"=FALSE, "35"=FALSE, "60"=FALSE, "65"=FALSE, "100"=FALSE, "135"=FALSE, "unknown"=TRUE)
```
* What is the grand mean of *B* for all cases: `r I(coef8)`


The model *C* ~ 1 gave this coefficient:**

Term | Coefficient
|:----|:----:|
Intercept | 4.7


```{r include=FALSE}
coef9=selectSet(name="Blue3", totalPts=1, "0.0"=FALSE, "4.7"=FALSE, "unknown"=TRUE)
```
* What is the group mean of *C* for those cases that are Blue: `r I(coef9)`

```{r include=FALSE}
coef10=selectSet(name="GrandMean3", totalPts=1, "0.0"=FALSE, "4.7"=TRUE, "unknown"=FALSE)
```
* What is the grand mean of *C* for all cases: `r I(coef10)`

`r I(endProblem())`