Intro to Statistical Modeling Ch. 7 Prob. 5
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-7-5-SD")
```

Using the appropriate data set and correct modeling statements, compute each of these quantities and give the model statement you used (eg., *age* ~ *sex*)

```{r include=FALSE}
CPS=selectNumber(choices=c(28,31,32,35,39), correct=c(32), totalPts=1, name="single")
```
From the `CPS85` data, what is the mean age of single people? (Pick the closest answer.) `r I(CPS)` years.

```{r include=FALSE, eval=FALSE}
I(textItem(name="model", totalPts=2, rows=3))
```
What was your model expression?     
`r I(textItem(name="model", totalPts=2, rows=3))`

<aside>
ANSWER:
The model *age* ~ *married* gives an intercept which is the mean age of married people and a *marriedSingle* coefficient which tells the difference in mean ages between the married and single people:

```{r}
cps = fetchData("CPS85")
lm( age ~ married, data=cps)
```


Adding these two coefficients gives the mean age of single people, about 32 years.
</aside>

```{r include=FALSE}
CPS2=selectSet(name="difference", totalPts=1, "Single people are, on average, 5 years younger."=FALSE, "Single people are, on average, 5 years older."=FALSE, "Single people are, on average, 7 years younger."=TRUE, "Single people are, on average, 7 years older."=FALSE)
```
* From the `CPS85` data, what is the difference between the mean ages of married and single people? (Pick the closest answer.) `r I(CPS2)`

```{r include=FALSE, eval=FALSE}
I(textItem(name="model2", totalPts=2, rows=3))
```
What was your model expression?      
`r I(textItem(name="model2", totalPts=2, rows=3))`

<aside>
ANSWER:     
The answer can be read off from the same model used to answer part 1.
The coefficient $-6.877$ on *marriedSingle* says that single people
are, on average, about 7 years younger than married people in these data.
</aside>

```{r include=FALSE}
swim=selectNumber(choices=c(55,60,65,70,75,80), correct=c(65), totalPts=1, name="meanswim")
```
* From the `SwimRecords` data, what is the mean swimming time for women? (Pick the closest.) `r I(swim)` seconds.

```{r include=FALSE, eval=FALSE}
I(textItem(name="model3", totalPts=2, rows=3))
```
What is your model expression?     
`r I(textItem(name="model3", totalPts=2, rows=3))`


<aside>
ANSWER:      
```{r}
swim = fetchData("SwimRecords")
lm( time ~ sex, data=swim)
```

Since the reference group is females, the mean swimming time for women
is given by the intercept.
</aside>

```{r include=FALSE}
util=selectNumber(choices=c(-150,-93,42,150,192), correct=c(42), totalPts=1, name="meanCCF")
```
* From the `Utilities` data, what is the mean CCF for November? (Pick the closest.)  (Hint: use <code>as.factor(month)</code> to convert the month number to a categorical variable.) `r I(util)`

```{r include=FALSE, eval=FALSE}
I(textItem(name="utils", totalPts=2, rows=3))
```
What is your model expression? 
`r I(textItem(name="utils", totalPts=2, rows=3))`

# Generated answer does not match previously recorded answer:

<aside>
ANSWER:     
```{r}
u = fetchData("Utilities")
lm( ccf ~ as.factor(month), data=u)
```
SHOULD MATCH >
Coefficients:
       (Intercept)   as.factor(month)2   as.factor(month)3  
           192.000               2.375             -62.250  
 as.factor(month)4   as.factor(month)5   as.factor(month)6  
          -113.625            -141.625            -178.111  
 as.factor(month)7   as.factor(month)8   as.factor(month)9  
          -182.667            -180.333            -176.556  
as.factor(month)10  as.factor(month)11  as.factor(month)12  
          -149.875             -88.778              -0.875  

November is month 10, so the mean value of *ccf* for November is
the sum of the intercept and the month 10 coefficient: $192 - 149.9\approx 42$.
</aside>


`r I(closeProblem())`

