Intro to Statistical Modeling Ch. 7 Prob. 1
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-7-1-SD")
```

There is a correspondence between the model formula and the coefficients found when fitting a model.  

For each of the following model formulas, tell what the coefficient is:

$3 - 7 x + 4 y + 17 z$

```{r include=FALSE}
model=selectNumber(choices=c(-7,3,4,17), correct=c(3), totalPts=1, name="intercept")
```
* Intercept: `r I(model)` 
```{r include=FALSE}
model2=selectNumber(choices=c(-7,3,4,17), correct=c(17), totalPts=1, name="zCoef")
```
* $z$ coef: `r I(model2)`  
```{r include=FALSE}
model3=selectNumber(choices=c(-7,3,4,17), correct=c(4), totalPts=1, name="yCoef")
```
* $y$ coef: `r I(model3)` 
```{r include=FALSE}
model4=selectNumber(choices=c(-7,3,4,17), correct=c(-7), totalPts=1, name="xCoef")
```
* $x$ coef: `r I(model4)`  

$1.22 + 0.12 *age* + 0.27 *educ* - 0.04 *age*:*educ*$

```{r include=FALSE}
model5=selectNumber(choices=c(-0.04,0.12, 0.27,1.22), correct=c(1.22), totalPts=1, name="intercept2")
```
* Intercept: `r I(model5)`
```{r include=FALSE}
model6=selectNumber(choices=c(-0.04,0.12, 0.27,1.22), correct=c(0.12), totalPts=1, name="educCoef")
```
* *educ* coef: `r I(model6)` 
```{r include=FALSE}
model7=selectNumber(choices=c(-0.04,0.12, 0.27,1.22), correct=c(0.27), totalPts=1, name="ageCoef")
```
* *age* coef: `r I(model7)` 
```{r include=FALSE}
model8=selectNumber(choices=c(-0.04,0.12, 0.27,1.22), correct=c(-0.04), totalPts=1, name="age:educCoef")
```
* *age*:*educ* coef: `r I(model8)`  

$8 + 3 *color*Red -4 *color*Blue$

```{r include=FALSE}
model8=selectNumber(choices=c(-4,3,8), correct=c(8), totalPts=1, name="intercept3")
```
* Intercept: `r I(model8)`
```{r include=FALSE}
model9=selectNumber(choices=c(-4,3,8), correct=c(3), totalPts=1, name="colorRed")
```
* *color*Red coef: `r I(model9)`  
```{r include=FALSE}
model10=selectNumber(choices=c(-4,3,8), correct=c(-4), totalPts=1, name="colorBlue")
```
* *color*Blue coef: `r I(model10)`

`r I(closeProblem())`
