Intro to Statistical Modeling Ch. 7 Reading Questions
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-7-RQ-SD")
```

* What is the role of the response variable in a model formula?
```{r include=FALSE, eval=FALSE}
I(textItem(name="response", totalPts=2, rows=3))
```
 `r I(textItem(name="response", totalPts=2, rows=3))`


<aside>
ANSWER:    
The response variable is the quantity whose variability you seek to account for in constructing a model.  
</aside>

* What is the purpose of constructing indicator variables from categorical variables?
```{r include=FALSE, eval=FALSE}
I(textItem(name="indicator", totalPts=2, rows=3))
```
  `r I(textItem(name="indicator", totalPts=2, rows=3))`

<aside>
ANSWER:    
The indicator variables constructed from a categorical variable are a quantitative representation of which level of the categorical variable each case falls in to.  But making this quantitative representation, you can include categorical
variables in a model formula, which is by necessity numerical in nature.
</aside>

* How can model coefficients be used describe relationships? What are the relationships between? 
```{r include=FALSE, eval=FALSE}
I(textItem(name="relationships", totalPts=2, rows=3))
```
 `r I(textItem(name= "relationships", totalPts=2, rows=3))`

<aside>
ANSWER:   
The model coefficients tell how the response variable will change when the explanatory variable changes value.  
</aside>

* What is Simpson's paradox? 
```{r include=FALSE, eval=FALSE}
I(textItem(name="simpson", totalPts=2, rows=3))
```
 `r I(textItem(name="simpson", totalPts=2, rows=3))`

<aside>
ANSWER:    
In general, when you extend a previous model by constructing a new model with an additional explanatory variable, the coefficients on the new model will be different than on the previous model.  Simpson's paradox is an extreme case when not only does a coefficient change its value, but its sign changes too, going from positive to negative or vice versa.
</aside>


* Given an example of how the meaning of a coefficient of a particular term can depend on what other model terms are included in the model? 
```{r include=FALSE, eval=FALSE}
I(textItem(name="context", totalPts=2, rows=3))
```
 `r I(textItem(name="context", totalPts=2, rows=3))`


<aside>
ANSWER:    
Suppose you model the wage data in the current population survey *time* ~ *sex*.  The meaning of *sex* is how the two sexes differ from one another without worrying about what other variables might account for the difference.  For example, the sexes might be unevenly distributed across the various sectors of the economy, but this model doesn't take that into account.

When you add *sector* as an explanatory variable, the meaning of *sex* becomes subtly different: it's the difference between the two sectors *taking into consideration* any differences that might be accounted for by the sector.
</aside>

`r I(endProblem())`

