Intro to Statistical Modeling Ch. 7 Prob. 14
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-7-14-SD")
```

The graph shows schematically a hypothesized relationship between how fast a person runs and the person's age and sex.

```{r 7-14-fig, engine = "tikz", echo=FALSE,fig.ext = 'png', cache=TRUE}
\begin{tikzpicture}[scale=2]
\draw[->] (0,0) -- node[below] {Age} (5,0);
\draw[->] (0,0) -- node[above,sloped] {Speed} (0,5);
\draw[ultra thick,blue] (.7,5) -- node[above,sloped,pos=.2] {Men} (3.5,.5);
\draw[ultra thick,black] (.5,3) -- node[above,sloped,pos=.8] {Women} (4.5,2);
\end{tikzpicture}
```


Consider the model *speed* ~ *age* $\star$ *sex*. 

```{r include=FALSE}
run=selectSet(name="age", totalPts=1, "Negative"=TRUE, "Zero"=FALSE, "Positive"=FALSE, "No way to tell, even roughly, from the information given"=FALSE)
```
* What will be the sign of the coefficient on *age*? `r I(run)`

```{r include=FALSE}
run2=selectSet(name="age2", totalPts=1, "Negative"=TRUE, "Zero"=FALSE, "Positive"=FALSE)
```
* What will be the sign of the coefficient on *sex*?  (Assume that the *sex* variable is an indicator for women.) `r I(run2)`

```{r include=FALSE}
run3=selectSet(name="age3", totalPts=1, "Negative"=FALSE, "Zero"=FALSE, "Positive"=TRUE, "There is no interaction coefficient"=FALSE, "No way to tell, even roughly, from the information given"=FALSE)
```
* What will be the sign of the interaction coefficient? (Again, assume that the *sex* variable is an indicator for women.) `r I(run3)`


`r I(endProblem())`