Intro to Statistical Modeling Ch. 7 Prob. 12
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-07-12-SD")
```

In the SAT data `SAT`, the variables have these units: 

* *sat* has units of "points." 
* *expend* has units of "dollars."
* *ratio* has units of "students."
* *frac* has units of "percentage points."


Consider the model formula 


*sat* = 994 + 12.29 *expend* - 2.85 *frac*

```{r include=FALSE}
SAT=selectSet(name="units994", totalPts=1, "points"=TRUE, "dollars"=FALSE, "students"=FALSE, "percentage points"=FALSE, "points per dollar"=FALSE, "students per point"=FALSE, "points per student"=FALSE, "points per percentage points"=FALSE)
```
* What are the units of the coefficient 994? `r I(SAT)`

```{r include=FALSE}
SAT2=selectSet(name="units12.29", totalPts=1, "points"=FALSE, "dollars"=FALSE, "students"=FALSE, "dollars per student"=FALSE, "points per dollar"=TRUE, "students per point"=FALSE, "points per student"=FALSE)
```
* What are the units of the coefficient 12.29? `r I(SAT2)`

```{r include=FALSE}
SAT3=selectSet(name="units2.85", totalPts=1, "points"=FALSE, "dollars"=FALSE, "percentage points"=FALSE, "points per dollar"=FALSE, "students per point"=FALSE, "points per student"=FALSE, "points per percentage points"=TRUE)
```
* What are the units of the coefficient 2.85? `r I(SAT3)`

`r I(endProblem())`