Intro to Statistical Modeling Ch. 12 Prob. 12
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-12-12-SD")
```

In 1882, Charles Darwin wrote about earthworms and their importance in producing soil.

> *Hensen, who has published so full and interesting an account of the habits of worms, calculates, from the number which he found in a measured space, that there must exist 133,000 living worms in a hectare of land, or 53,767 in an acre.* --- p. 161,  "The Formation of Vegetable Mould, through the Action of Worms with Observations on their Habits"


While 133,000 seems sensibly rounded, 53,767 is not. <aside> 
In *A Short History of Almost Everything*, writer Bill Bryson made fun of absurd statements of precision: "Darwin loved an exact number.... [H]e announced that the number of worms to be found in an average acre of English country soil was 53,767."  </aside> This problem investigates some of the things you can find out about the precision of such numbers and how to report them using modern notation, which wasn't available to Darwin or his contemporaries.


Background: A hectare is a metric unit of area, 10,000 square meters.  An acre is a traditional unit of measure, with one acre equivalent to 0.4046863 hectares.  That is, an acre is a little less than half a hectare.

The implicit precision in Hensen's figure is $133,000 \pm 500$, since it is rounded to the thousands place.  Correctly translate the Hensen figure to be in worms per acre. 

```{r include=FALSE}
worms=selectNumber(choices=c(53760,53767,53770,53823,53830), correct=c(53823), totalPts=1, name="WormsPerAcre")
```
* Literally translating 133,000 worms per hectare to worms per acre gives what value? `r I(worms)`

<aside>
ANSWER:    
Just multiply 133,000 by $0.4046863$ to get $53823$.  Darwin was either using a slightly different conversion factor or made a calculation mistake.
</aside>

```{r include=FALSE}
worms2=selectNumber(choices=c(197,200,202,205,207), correct=c(202), totalPts=1, name="500wormsPerAcre")
```
* Literally translating $\pm 500$ worms per hectare to worms per acre gives what value? `r I(worms2)`

<aside>
ANSWER:    
Similar to the above, just multiply 500 by $0.4046863$ to get $202$.  More precision isn't warranted on the margin of error.
</aside>

* Which one of these reports gives a proper account for the number of worms per acre?
```{r include=FALSE}
f=newMC(totalPts=1)
```
`r I(f(FALSE))` $53767 \pm 202$    
`r I(f(FALSE))` $53823 \pm 200$    
`r I(f(TRUE))` $53820 \pm 200$    
`r I(f(FALSE))` $53830 \pm 200$    
```{r include=FALSE, results='hide'}
I(f(finish=TRUE))
```

<aside>
ANSWER:    
It's worth reporting at most two digits on the margin of error, so $202$ can be reported as $200$. (The second digit happens to be zero, but the precision is to two digits.) Then report the point estimate to the digit that corresponds to the second digit in the margin of error: so $53823$ becomes $53820$.
</aside>


Of course, it's just an assumption that Hensen's precision is $\pm 500$. Imagine that the way Hensen made his estimate was to dig up 10 different patches of ground, each of size one square meter.  In each patch, Hensen counted the worms found then added these together to get the total number of worms in 10 square meters.  Since Hensen reported 133,000 worms per hectare, he would have found a total of 133 worms in the ten square meters he actually dug up. 

Of course, if Hensen had picked a different set of 10 patches of soil in the same field, he would likely not have found exactly 133 worms. There is some sampling variability to the number of worms found.

Using an appropriate probability model for the number of worms to be found in 10 square meters of soil, estimate the standard deviation of the number found, assuming that on average the number is 133 per 10 square meters.

```{r include=FALSE}
worms3=selectSet(name="model", totalPts=1, "guassian"=FALSE, "uniform"=FALSE, "exponential"=FALSE, "poisson"=TRUE, "binomial"=FALSE)
```
* What is an appropriate probability model? `r I(worms3)`

<aside>
ANSWER:    
The poisson is the standard model for a count that is random, where the average rate is the parameter.  A binomial is also a model for counts, but it assumes there is a fixed number of trials, each of which yields either 0 or 1.
</aside>

```{r include=FALSE}
worms4=selectNumber(choices=c(2.1,7.9,11.5,15.9,58.2,102), correct=c(11.5), totalPts=1, name="StdDev")
```
* Using the appropriate probability model, what standard deviation corresponds to a mean of 133 per 10 square meters?  (Hint: You can use a random number generator to make a large sample of draws and then find the standard deviation of this sample.) `r I(worms4)`

<aside>
ANSWER:    
Here is how to generate 10000 trials sampling from a population where the average count in a trial is 133.
```{r}
foo = rpois(10000,133)
sd(foo)
```

As it happens, for a poisson distribution, the standard deviation will be the square root of the population average. $\sqrt{133} = 11.53$.
</aside>

* Using your standard deviation, and recalling that the number of worms in one hectare will be 1000 times that found in 10 square meters, give an appropriate 95% confidence interval to use today in reporting Hensen's result.
```{r include=FALSE}
g=newMC(totalPts=1)
```
`r I(g(TRUE))` $133,000 \pm 23000$    
`r I(g(FALSE))` $133,000 \pm 2100$    
`r I(g(FALSE))` $133,000 \pm 16000$    
`r I(g(FALSE))` $133,000 \pm 20000$    
`r I(g(FALSE))` $130,000 \pm 120000$
```{r include=FALSE, results='hide'}
I(g(finish=TRUE))
```

<aside>
ANSWER:    
You need to multiply the standard deviation you found by 2 in order to translate it to a 95% confidence interval.  Then scale that up by 1000 to move from 10 square meters to a hectare. The result is $11.53\times2\times1000 = 23000$.
</aside>

```{r include=FALSE}
worms5=selectNumber(choices=c(730,2100,16000,58000,190000), correct=c(730), totalPts=1, name="MarginOfError")
```
* Now imagine, almost certainly contrary to fact, that Hensen had actually dug up an entire hectare and found 133,201 worms, and rounded this to 133,000 just for the sake of not seeming silly.  Of course, this would have been a heroic effort just to gain precision on the count.  It would also be futile, since the number in a "hectare of soil" presumably differs widely depending on the soil conditions.  But if Hensen had calculated a 95% confidence interval using an appropriate probability model on the count of 133,201 worms, rather than just rounding to what seems reasonable, what would have been his margin of error? `r I(worms5)`

<aside>
ANSWER:    
This is similar to the previous problem, but now the rate to use in the poisson distribution is 133000 rather than 133.  The 133000 parameter produces a larger standard deviation, $\sqrt{133000} = 365$, but the larger count is much more precise on a relative basis.  Multiply the standard deviation by 2 to give the 95% margin of error.
</aside>

`r I(closeProblem())`

