Intro to Statistical Modeling Ch. 12 Prob. 2
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-12-2-SD")
```

```{r include=FALSE}
kids=fetchData("KidsFeet")
```


Look at this report from a model of the kids' feet data, 
```{r}
summary(lm(width~length+sex,data=kids))
```

* Based on the output of the report, which of these statements is a correct confidence interval on the <code>sexG</code> coefficient?     
```{r include=FALSE}
f=newMC(totalPts=1, name="statement")
```
  `r I(f(FALSE))` $-.23 \pm 0.13$ with 95 percent confidence     
  `r I(f(FALSE))` $-.23 \pm 0.13$ with 50 percent confidence    
  `r I(f(TRUE))` $-.23 \pm 0.13$ with 68 percent confidence    
  `r I(f(FALSE))` $-.23 \pm 0.0805$ with 95 percent confidence    
  `r I(f(FALSE))` $-.23 \pm 0.23$ with 68 percent confidence    
  `r I(f(FALSE))` None of the above    
`r I(f(finish=TRUE))`

* Based on the output of the report, which of these statements is a correct confidence interval on the <code>length</code> coefficient?
```{r include=FALSE}
g=newMC(totalPts=1, name="statement2")
```
  `r I(g(FALSE))` $0.22 \pm 0.050$ with 95 percent confidence     
  `r I(g(TRUE))` $0.22 \pm 0.050$ with 68 percent confidence    
  `r I(g(FALSE))` $0.22 \pm 0.100$ with 50 percent confidence    
  `r I(g(FALSE))` $0.22 \pm 0.070$ with 50 percent confidence     
  `r I(g(FALSE))` None of the above
`r I(g(finish=TRUE))`

`r I(endProblem())`