Intro to Statistical Modeling Ch. 12 Prob. 5
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-12-5-SD")
```
A statistics professor sends her students out to collect data by interviewing other students about various quantities, e.g., their SAT scores, GPAs and other
data for which the college registrar retains official records.  Each student is
assigned one quantity and one target population, for example, the verbal SAT scores of all female students, or the cumulative grade point average for sophomore males.

Each student interviews some students --- how many depends on the student's initiative and energy.  The student then reports the results in the form of a confidence interval, $P \pm M$ with 95% confidence.

```{r include=FALSE}
stats=selectSet(name="fraction", totalPts=1, "95%"=TRUE, "50%"=FALSE, "5%"=FALSE, "Can't tell, it depends on how much data each student collected."=FALSE, "Can't tell, the students each looked at different quantities, not all of them at the same quantity."=FALSE)
```
After the students hand in their reports, the professor contacts the registrar to find the population parameters for each group that the students surveyed.  **Assuming** that the interviewed students provided accurate information, what fraction of the students' confidence intervals will contain the corresponding population parameter? `r I(stats)`

`r I(endProblem())`