Intro to Statistical Modeling Ch. 6 Prob. 2
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-6-2-SD")
```

In studies of employment discrimination, several attributes of
employees are often relevant:
>age, sex, race, years of experience, salary, whether promoted, whether laid off 


For each of the following questions, indicate
which is the response variable and which is the explanatory variable.

* Are men paid more than women? 

```{r include=FALSE}
employment=selectSet(name="responsevar", totalPts=1, "age"=FALSE, "sex"=FALSE, "race"=FALSE, "years experience"=FALSE, "salary"=TRUE, "promoted"=FALSE, "laid off"=FALSE)
```
  * Response Variable: `r I(employment)`

```{r include=FALSE}
employment2=selectSet(name="explanatoryvar", totalPts=1, "age"=FALSE, "sex"=TRUE, "race"=FALSE, "years experience"=FALSE, "salary"=FALSE, "promoted"=FALSE, "laid off"=FALSE)
```
  * Explanatory Variable: `r I(employment2)`

<aside>
ANSWER:
For many people, it can be confusing at first to decide what is the
response variable and what is the explanatory variable.  In this
question, there are two variables: salary and sex.  There are two
kinds of questions you might ask with these variables: "Can I tell
something about how much a person is paid given their sex?" and "Can
I tell what sex a person is, given how much they are paid?"  Those
questions are different.  

In examining possible employment discrimination, the issue is whether
a person's sex influences how much they are paid.  So sex is the
explanatory variable and pay is the response variable.
</aside>

* On average, how much extra salary is a year of experience worth? 

```{r include=FALSE}
employment3=selectSet(name="responsevar2", totalPts=1, "age"=FALSE, "sex"=FALSE, "race"=FALSE, "years experience"=FALSE, "salary"=TRUE, "promoted"=FALSE, "laid off"=FALSE)
```
  * Response Variable: `r I(employment3)`

```{r include=FALSE}
employment4=selectSet(name="explanatoryvar2", totalPts=1, "age"=FALSE, "sex"=FALSE, "race"=FALSE, "years experience"=TRUE, "salary"=FALSE, "promoted"=FALSE, "laid off"=FALSE)
```
  * Explanatory Variable: `r I(employment4)` 


<aside>
ANSWER:
The response variable is the person's salary.  The explanatory
variable is how much experience they have.
</aside>

* Are whites more likely than blacks to be promoted? 

```{r include=FALSE}
employment5=selectSet(name="responsevar3", totalPts=1, "age"=FALSE, "sex"=FALSE, "race"=FALSE, "years experience"=FALSE, "salary"=FALSE, "promoted"=TRUE, "laid off"=FALSE)
```
  * Response Variable: `r I(employment5)`

```{r include=FALSE}
employment6=selectSet(name="explanatoryvar3", totalPts=1, "age"=FALSE, "sex"=FALSE, "race"=TRUE, "years experience"=FALSE, "salary"=FALSE, "promoted"=FALSE, "laid off"=FALSE)
```
  * Explanatory Variable: `r I(employment6)`

<aside>
ANSWER:
The response variable is whether the person was promoted or not.
</aside>

* Are older employees more likely to be laid off than younger ones?  

```{r include=FALSE}
employment7=selectSet(name="responsevar4", totalPts=1, "age"=FALSE, "sex"=FALSE, "race"=FALSE, "years experience"=FALSE, "salary"=FALSE, "promoted"=FALSE, "laid off"=TRUE)
````
  * Response Variable: `r I(employment7)`

```{r include=FALSE}
employment8=selectSet(name="explanatoryvar4", totalPts=1, "age"=TRUE, "sex"=FALSE, "race"=FALSE, "years experience"=FALSE, "salary"=FALSE, "promoted"=FALSE, "laid off"=FALSE)
```
  * Explanatory Variable: `r I(employment8)` 

<aside>
ANSWER:
In these exercises, there is just one explanatory variable in each setting.  However, in real situations you will often be interested in examining **multiple** explanatory variables at the same time.  
</aside>

`r I(endProblem())`