Intro to Statistical Modeling Ch. 6 Prob. 23
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-6-23-SD")
```

Given data and a model design, the computer will find the model function and model values for you.  As an example, consider the Current Population 
Survey  data `CPS85`.  Suppose you want to build a model with *wage* as a response variable and *age* and *sex* as explanatory variables incorporated as main terms.  Also include the intercept term, as usual.

Using the model design language, this model is *wage*~ 1 + *age* + *sex*.

You first need to read in the data frame.  

```{r results="hide"}
w = fetchData("cps.csv")
```


Next, use the <code>lm</code> operator to find the model function:

```{r results='hide'}
mod1 = lm( wage ~ 1 + age + sex, data=w)
```


The two arguments are:
* **the model design** *wage* ~ 1 + *age* + *sex*. 
* **the data to be used** This always looks like <code>data=w</code> where the name of the data frame is used.


The <code>mod1 = </code> ... part of the command simply gives the model a
name so that you can use it later on.  If you construct more than one
model, it makes sense to give them different names.  But don't re-use
the name of the data frame; a name can be used for only one thing at a
time.

In making a graph of the function, the model values will always be
plotted on the vertical axis.  But you have a choice of what to put on
the horizontal axis.  Here are the commands which use the
<code>xyplot</code> operator:

#### Model values versus *age*.
  
```{r}
xyplot( fitted(mod1) ~ age, data=w )
```
  
   
#### Model values versus *sex*.

```{r}
print(xyplot( fitted(mod1) ~ sex, data=w ))
```


The fitted model values can be accessed with <code>fitted(mod1)</code>.
The choice of which explanatory variable to plot on the horizontal
axis is specified by the name following the *~* sign in the
plotting command.  Remember to include the name of the data frame in
the last argument: <code>data=w</code>.


Some elaborations are possible.

#### Show the response variable in addition to the model values.
  
This involves putting the response variable name to the left of the *~* sign:

```{r}
print(xyplot( wage + fitted(mod1) ~ age, data=w ))
```   

The <code>+</code> sign means "plot both," not addition.

#### Break up the display according to one or more categorical
  variables.

```{r}
xyplot( wage + fitted(mod1) ~ age | sex, data=w )
```   

This uses a vertical bar followed by the name of the categorical
variable.  Each of the levels of the variable to the right of the vertical bar
*+|+* will have a separate plot, so in the graphics it's females in
one plot and males in the other.


A different way to break up the display makes it easier to compare the
model values for the different groups:

```{r}
xyplot(wage+fitted(mod1) ~ age,groups=sex,data=w)
``` 


`r I(closeProblem())`