Intro to Statistical Modeling Ch. 6 Prob. 27
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-6-27-SD")
```

Sometimes when making a graphic, you want to change some aspect of it or add new elements to it.  The lattice graphics system provides ways to do this.  To illustrate, make a simple density plot in the ordinary way.  

```{r}
galton = fetchData("Galton")
densityplot( galton$height )
```

In looking at the plot, you realize that you want a better label for the horizontal axis.  One option is to redo the plot from scratch:

```{r}
densityplot( galton$height, xlab="Children")
```

Another option is to instruct the graphics system just to change the specific parameters you want, for example, to change the x-label and to delete the points plotted at the bottom:

```{r}
trellis.last.object( xlab="Height (inches)", plot.points=FALSE)
```

Now suppose you decide to superimpose density plots of the mothers' and fathers' heights.  To do this, you need to tell the lattice system that you want to {\em add on} to the plot.  This is done with the <code>trellis.focus</code> command:

```{r}
trellis.focus()
```

You'll notice that the original graphic is surrounded by a red line. Once this is done, you can add on to the plot.  

To start, use <code>density</code> to compute the density curve for the mothers and the fathers.  This will not plot out those curves, yet.

```{r}
mother = density(galton$mother)
father = density(galton$father)
```

Now you can add those curves to the plot, using the <code>llines</code> command.  This takes a series of x- and y- points, but those are already contained in the output of the <code>density</code> program:

```{r}
llines(mother, col='red', lwd=2)
llines(father, col='black', lwd=2)
```

Finally, tell the lattice system that you are done adding to the original plot:

```{r}
trellis.unfocus()
```

```{r include=FALSE, eval=FALSE}
I(textItem(name="describe", totalPts=1, rows=3))
```
Use these commands to construct the graph comparing the distribution of the mothers' and fathers' heights to the children's heights.  Describe how they are
different and explain why this is.       
`r I(textItem(name="describe", totalPts=1, rows=3))`

Other useful commands for adding elements to lattice plots are <code>llines</code>, <code>lpoints</code> and <code>ltext</code>.

`r I(closeProblem())`
