Intro to Statistical Modeling Ch. 17 Reading Questions
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-17-RQ-SD")
```

* Why does an observed correlation between two variables not provide compelling evidence that one causes the other? 
```{r include=FALSE, eval=FALSE}
I(textItem(name="observed", totalPts=2, rows=3))
```
 `r I(textItem(name="observed", totalPts=2, rows=3))`

* What is a hypothetical causal network?  What does the word "hypothetical" signify about these networks? 
```{r include=FALSE, eval=FALSE}
I(textItem(name="hypothetical", totalPts=2, rows=3))
```
 `r I(textItem(name="hypothetical", totalPts=2, rows=3))`

* What is the difference between a correlating pathway and a non-correlating pathway? 
```{r include=FALSE, eval=FALSE}
I(textItem(name="correlating", totalPts=2, rows=3))
```

 `r I(textItem(name="correlating", totalPts=2, rows=3))`

* How is the appropriate choice of covariates in models to study causation influenced by the structure of the modeler's hypothetical causal network?
```{r include=FALSE,eval=FALSE}
I(textItem(name="causation", totalPts=2, rows=3))
```
 `r I(textItem(name="causation", totalPts=2, rows=3))`

* When might two modelers legitimately disagree about which covariates to include in a model? 
```{r include=FALSE, eval=FALSE}
I(textItem(name="disagree", totalPts=2, rows=3))
```
 `r I(textItem(name="disagree", totalPts=2, rows=3))`

`r I(closeProblem())`