Intro to Statistical Modeling Ch. 17 Prob. 2
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-17-2-SD")
```

$$
\newcommand{\causes}{{\Rightarrow}}
\newcommand{\causedBy}{{\Leftarrow}}
\newcommand{\correlatedWith}{{\Leftrightarrow}}$$

Say whether the pathway connecting A and B is correlating or non-correlating.

```{r include=FALSE}
prob1=selectSet(name="1a", totalPts=1, "correlating"=TRUE, "noncorrelating"=FALSE)
```
* $A\causes C\causes B$ `r I(prob1)`

```{r include=FALSE}
prob2=selectSet(name="2a", totalPts=1, "correlating"=TRUE, "noncorrelating"=FALSE)
```
* $A\causedBy C\causedBy B$ `r I(prob2)`

```{r include=FALSE}
prob3=selectSet(name="3a", totalPts=1, "correlating"=TRUE, "noncorrelating"=FALSE)
```
* $A\causedBy C\causes B$ `r I(prob3)`

```{r include=FALSE}
prob4=selectSet(name="4a", totalPts=1, "correlating"=FALSE, "noncorrelating"=TRUE)
```
* $A\causes C\causedBy B$ `r I(prob4)`

```{r include=FALSE}
prob5=selectSet(name="5a", totalPts=1, "correlating"=FALSE, "noncorrelating"=TRUE)
```
* $A\causes C\causedBy D \causes B$ `r I(prob5)`

```{r include=FALSE}
prob6=selectSet(name="6a", totalPts=1, "correlating"=FALSE, "noncorrelating"=TRUE)
```
* $A\causes C\causedBy D \causedBy B$ `r I(prob6)`

```{r include=FALSE}
prob7=selectSet(name="7a", totalPts=1, "correlating"=TRUE, "noncorrelating"=FALSE)
```
* $A\causedBy C\causedBy D \causedBy B$ `r I(prob7)`

```{r include=FALSE}
prob8=selectSet(name="8a", totalPts=1, "correlating"=FALSE, "noncorrelating"=TRUE)
```
* $A\causedBy C\causes D \causedBy E\causedBy B$ `r I(prob8)`

`r I(endProblem())`