Intro to Statistical Modeling Ch. 17 Prob. 10
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-17-10-SD")
```
To answer the following questions, refer to the hypothetical causal network shown in Figure 17.9.

Consider studying the direct link between teacher compensation and student test scores with a model of the form *Student Test Scores* ~ *Teacher Compensation + C*, where C is one or more covariates.  Which of the following choices of C can block the back-door pathways?

```{r include=FALSE}
prob1=selectSet(name="c.class.size", totalPts=1, "blocks"=FALSE, "does not block"=TRUE)
```
* C is class size. `r I(prob1)`

```{r include=FALSE}
prob2=selectSet(name="c.teacher.comp", totalPts=1, "blocks"=TRUE, "does not block"=FALSE)
```
* C is class size and teacher compensation. `r I(prob2)`

```{r include=FALSE}
prob3=selectSet(name="c.family.income", totalPts=1, "blocks"=FALSE, "does not block"=TRUE)
```
* C is family income. `r I(prob3)`

```{r include=FALSE}
prob4=selectSet(name="c.per.capita", totalPts=1, "blocks"=FALSE, "does not block"=TRUE)
```
* C is per capita expenditures. `r I(prob4)`

```{r include=FALSE}
prob5=selectSet(name="c.family.income.2", totalPts=1, "blocks"=FALSE, "does not block"=TRUE)
```
* C is per capita expenditures and family income. `r I(prob5)`

```{r include=FALSE}
prob6=selectSet(name="c.class.size.2", totalPts=1, "blocks"=TRUE, "does not block"=FALSE)
```
* C is per capita expenditures and class size. `r I(prob6)`

```{r include=FALSE}
prob7=selectSet(name="c.education", totalPts=1, "blocks"=FALSE, "does not block"=TRUE)
```
* C is class size and parents' education. `r I(prob7)`

`r I(endProblem())`