Intro to Statistical Modeling Ch. 17 Prob. 1
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-17-1-SD")
```

$$
\newcommand{\causes}{{\Rightarrow}}
\newcommand{\causedBy}{{\Leftarrow}}
\newcommand{\correlatedWith}{{\Leftrightarrow}}$$

For each of the following pathways connecting A and B, choose the appropriate causal structure.

```{r include=FALSE}
prob1=selectSet(name="1", totalPts=1, "A causes B."=TRUE, "B causes A."=FALSE, "A and B share a common cause."=FALSE, "No causal connection between A and B."=FALSE)
```
* $A\causes C\causes B$ `r I(prob1)`

```{r include=FALSE}
prob2=selectSet(name="2", totalPts=1, "A causes B."=FALSE, "B causes A."=TRUE, "A and B share a common cause."=FALSE, "No causal connection between A and B."=FALSE)
```
* $A\causedBy C\causedBy B$ `r I(prob2)`

```{r include=FALSE}
prob3=selectSet(name="3", totalPts=1, "A causes B."=FALSE, "B causes A."=FALSE, "A and B share a common cause."=TRUE, "No causal connection between A and B."=FALSE)
```
* $A\causedBy C\causes B$ `r I(prob3)`

```{r include=FALSE}
prob4=selectSet(name="4", totalPts=1, "A causes B."=FALSE, "B causes A."=FALSE, "A and B share a common cause."=FALSE, "No causal connection between A and B."=TRUE)
```
* $A\causes C\causedBy B$ `r I(prob4)`

```{r include=FALSE}
prob5=selectSet(name="5", totalPts=1, "A causes B."=FALSE, "B causes A."=FALSE, "A and B share a common cause."=FALSE, "No causal connection between A and B."=TRUE)
```
* $A\causes C\causedBy D \causes B$ `r I(prob5)`

```{r include=FALSE}
prob6=selectSet(name="6", totalPts=1, "A causes B."=FALSE, "B causes A."=FALSE, "A and B share a common cause."=FALSE, "No causal connection between A and B."=TRUE)
```
* $A\causes C\causedBy D \causedBy B$ `r I(prob6)`

```{r include=FALSE}
prob7=selectSet(name="7", totalPts=1, "A causes B."=FALSE, "B causes A."=FALSE, "A and B share a common cause."=TRUE, "No causal connection between A and B."=FALSE)
```
* $A\causedBy C\causedBy D \causedBy B$ `r I(prob7)`

```{r include=FALSE}
prob8=selectSet(name="8", totalPts=1, "A causes B."=FALSE, "B causes A."=FALSE, "A and B share a common cause."=FALSE, "No causal connection between A and B."=TRUE)
```
* $A\causedBy C\causes D \causedBy E\causedBy B$ `r I(prob8)`

`r I(endProblem())`