Intro to Statistical Modeling Ch. 17 Prob. 12
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-17-12-SD")
``` 

Here is a somewhat complicated hypothetical causal network:


### Needs image from paths-108b

\begin{tikzpicture}{scale=.6}
\measurableNode{A}{(2,8)}{A}
\measurableNode{B}{(4,6)}{B}
\measurableNode{C}{(2,4)}{C}
\measurableNode{D}{(2,2)}{D}
\measurableNode{E}{(6,4)}{E}
\measurableNode{F}{(0,6)}{F}
\straightLink{A}{F}{}
\straightLink{A}{B}{}
\straightLink{B}{C}{}
\straightLink{B}{E}{}
\straightLink{F}{C}{}
\straightLink{C}{D}{}
\end{tikzpicture}


You are interested in studying the causal effect of F on D.  

You want to block the backdoor pathway from F to D through A.  

* For each of the following covariates, say what will be the effect of including the covariate in your model on the F-through-A-to-D pathway.
```{r include=FALSE}
prob1 = selectSet(name="A", totalPts=1, "Blocks"=TRUE, "Unblocks"=FALSE, "Neither"=FALSE)
```
*  A:  `r I(prob1)`
```{r include=FALSE}
prob2=selectSet(name="B", totalPts=1, "Blocks"=TRUE, "Unblocks"=FALSE, "Neither"=FALSE)
```
*  B:  `r I(prob2)`
```{r include=FALSE}
prob3=selectSet(name="C", totalPts=1, "Blocks"=FALSE, "Unblocks"=FALSE, "Neither"=TRUE)
```
*  C:  `r I(prob3)`

An additional rule about pathway blocking is that including any covariate that is a causal child of another covariate equivalent in terms of blocking to including the parent node. (A child is a node that has a causal arrow leading from the parent to the child.)  Applying this rule, say whether including covariate E would block the F-through-A-to-D pathway:
```{r include=FALSE}
prob4=selectSet(name="E", totalPts=1, "Blocks"=FALSE, "Unblocks"=FALSE, "Neither"=TRUE)
```
*  E:  `r I(prob4)`

You could use C to block the backdoor pathway from F to D through A.
Explain why this would not be a good thing to do if you want to study
the causal connection between F and D.

`r I(textItem(name="explain", totalPts=2, rows=3))`


<aside>
ANSWER:    
While C blocks the backdoor pathway, as a causal mediator between F and D it also blocks the pathway that you want to study.
</aside>

`r I(endProblem())`