Applied Calculus Ch. 2 Sec. 4 Prob. 26
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("AC-2-4-26")
```

Let $P(t)$ represent the price of a share of stock of a corporation at time $t$.  What does each of the following statements tell us about the signs of the first and second derivatives of $P(t)$?

* "The price of the stock is rising faster and faster."
```{r include=FALSE}
prob1=selectSet(name="2.4.26a1", totalPts=1, "positive"=TRUE, "negative"=FALSE, "zero"=FALSE)
```
  * First derivative: `r I(prob1)`
```{r include=FALSE}
prob2=selectSet(name="2.4.26a2", totalPts=1, "positive"=TRUE, "negative"=FALSE, "zero"=FALSE)
```
  * Second derivative: `r I(prob2)`


* "The price of the stock is close to bottoming out."
```{r include=FALSE}
prob3=selectSet(name="2.4.26b1", totalPts=1, "positive"=FALSE, "negative"=TRUE, "zero"=FALSE)
```
  * First derivative: `r I(prob3)`
```{r include=FALSE}
prob4=selectSet(name="2.4.26b2", totalPts=1, "positive"=TRUE, "negative"=FALSE, "zero"=FALSE)
```
  * Second derivative: `r I(prob4)`

`r I(endProblem())`