Applied Calculus Ch. 2 Sec. 4 Prob. 28
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("AC-2-4-28")
```

Each of the graphs --- marked as I, II, III, IV --- in Figure 2.42 (in the book) shows the position of a particle moving along the $x$-axis as a function of time, $0 \leq t \leq 5$.  The vertical scales of the graphs are the same.  During this time interval, which particle has:

```{r include=FALSE}
prob1=selectSet(name="2.4.28a", totalPts=1, "I"=FALSE, "II"=FALSE, "III"=FALSE, "IV"=TRUE)
```
* Constant velocity? `r I(prob1)`
```{r include=FALSE}
prob2=selectSet(name="2.4.28b", totalPts=1, "I"=FALSE, "II"=FALSE, "III"=TRUE, "IV"=FALSE)
```
* The greatest initial velocity? `r I(prob2)`
```{r include=FALSE}
prob3=selectSet(name="2.4.28c", totalPts=1, "I"=FALSE, "II"=TRUE, "III"=FALSE, "IV"=FALSE)
```
* The greatest average velocity? `r I(prob3)`
```{r include=FALSE}
prob4=selectSet(name="2.4.28d", totalPts=1, "I"=TRUE, "II"=FALSE, "III"=FALSE, "IV"=FALSE)
```
* Zero average velocity? `r I(prob4)`
```{r include=FALSE}
prob5=selectSet(name="2.4.28e", totalPts=1, "I"=FALSE, "II"=FALSE, "III"=FALSE, "IV"=TRUE)
```
* Zero acceleration? `r I(prob5)`
```{r include=FALSE}
prob6=selectSet(name="2.4.28f", totalPts=1, "I"=FALSE, "II"=TRUE, "III"=FALSE, "IV"=FALSE)
```
* Positive acceleration throughout? `r I(prob6)`

`r I(endProblem())`