Applied Calculus Ch. 2 Sec. 5 Prob. 12
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("AC-2-5-12")
```

Cost (in $) and revenue functions for a charter bus company are shown in Figure 2.57 (in the book).      
Cost and revenue are function of the size of the bus company, as measured by the number of busses in the fleet. 
```{r include=FALSE}
prob1=selectSet(name="2.5.12a", totalPts=1, "Yes"=TRUE, "No"=FALSE, "Unknown"=FALSE)
```
* Would a company with a fleet of size 50 busses make a profit? `r I(prob1)`
```{r include=FALSE}
prob2=selectSet(name="2.5.12b", totalPts=1, "Yes"=TRUE, "No"=FALSE, "Unknown"=FALSE)
```
* Would a company with a fleet of size 90 busses make a profit? `r I(prob2)`
```{r include=FALSE}
prob3=selectSet(name="2.5.12c", totalPts=1, "Yes"=FALSE, "No"=TRUE, "Unknown"=FALSE)
```
* Would a company with a fleet of size 125 busses make a profit? `r I(prob3)`
```{r include=FALSE}
prob4=selectNumber(choices=c(25,50,75,100), correct=c(75), totalPts=1, name="2.5.12d")
```
* What should the size of the company be to maximize the total profit? (Pick the closest answer.) `r I(prob4)`

`r I(endProblem())`