Intro to Statistical Modeling Ch. 16 Prob. 5
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-16-5-SD")
```
This model traces through some of the steps in fitting a model of a yes/no process.  For specificity, pretend that the data are from observations of a random sample of teenaged drivers. The response variable is whether or not the driver was in an *accident* during one year (birthday to birthday).  The explanatory variables are *sex* and *age* of the driver.
 
The model being fit is *accident* ~ *1* + *age* + *sex*.

Here is a very small, fictitious set of data. 

Case &nbsp; | &nbsp; Age &nbsp; | &nbsp; Sex &nbsp; | &nbsp; Accident?
|:---|:---:|:---:|:---:|
1 | 17 | F | Yes 
2 | 17 | M | No 
3 | 18 | M | Yes
4 | 19 | F | No 

Even if it weren't fictitious, it would be too small for any practical purpose.  But it will serve to illustrate the principles of fitting.

In fitting the model, the computer compares the likelihoods of various   candidate values for the coefficients, choosing those coefficients that maximize the likelihood of the model.

Consider these two different candidate coefficients:

Candidate A Coefficients | | |
|:---:|:---:|:---:|
Intercept &nbsp; | &nbsp; *age* &nbsp; | &nbsp; *sexF*
35 | -2 | -1 



Candidate B Coefficients | | |
|:---:|:---:|:---:|
Intercept &nbsp; | &nbsp; *age* &nbsp; | &nbsp; *sexF*
35 | -2 | 0


The link value is found by multiplying the coefficients by the values of the explanatory variables in the usual way.

* Using the candidate A coefficients, what is the link value for case 1?
```{r include=FALSE}
f=newMC(totalPts=1, name="link.value.1")
```
`r I(f(FALSE))` $35 - 2\times 17 - 0 = 1$    
`r I(f(TRUE))` $35 - 2\times 17 - 1 = 0$    
`r I(f(FALSE))` $35 - 2\times 18 - 1 = -2$    
`r I(f(FALSE))` $35 - 2\times 19 - 1 = -4$       
`r I(f(finish=TRUE))`

* Using the candidate B coefficients, what is the link value for case 3?
```{r include=FALSE}
g=newMC(totalPts=1, name="link.value.3")
```
`r I(g(TRUE))` $35 - 2\times 18 - 0 = -1$    
`r I(g(FALSE))` $35 - 2\times 18 - 1 = -2$    
`r I(g(FALSE))` $35 - 2\times 18 + 1 = 0$    
`r I(g(FALSE))` $35 - 2\times 18 - 2 = -3$    
`r I(g(finish=TRUE))`

The link value is converted to a probability value by using the logistic transform.

```{r include=FALSE}
prob1=selectNumber(choices=c(0.004,0.018,0.027,0.047,0.172,0.261), correct=c(0.018), totalPts=1, name="candidate.A")
```
* The link value under the candidate A coefficients for case 4 is $35 -2\times 19 - 1 = -4$.  What is the corresponding probability value? (Hint: Plug in the link value to the logistic transform!) `r I(prob1)`

```{r include=FALSE}
prob2=selectNumber(choices=c(0.004,0.018,0.027,0.047,0.172,0.261), correct=c(0.047), totalPts=1, name="candidate.B")
```
* The link value under the candidate B coefficients for case 4 is $35 -2\times 19 - 0 = -3$.  What is the corresponding probability value? `r I(prob2)`


The probability value is converted to a likelihood by calculating the probability of the observed outcome according to the probability value.  When the outcome is "Yes," the likelihood is just the same as the probability value.  But when the outcome is "No," the likelihood is 1 minus the probability value.

```{r include=FALSE}
prob3=selectNumber(choices=c(0.000,0.269,0.500,0.731,1.000), correct=c(0.269), totalPts=1, name="case.3.A")
```
* The link value for case 3 using the candidate A coefficients is $-1$ and the corresponding probability value is $0.269$.  What is the likelihood of the observed value of case 3 under the candidate A coefficients? `r I(prob3)`

```{r include=FALSE}
prob4=selectNumber(choices=c(0.000,0.269,0.500,0.731,1.000), correct=c(0.269), totalPts=1, name="case.2.A")
```
* The link value for case 2 using the candidate A coefficients is $1$ and the corresponding probability value is $0.731$.  What is the likelihood of the observed value of case 2 under the candidate A coefficients? `r I(prob4)`

To compute the likelihood of the entire set of observations under the candidate coefficients, multiply together the likelihoods for all the cases.  Do this calculation separately for the candidate A coefficients and the candidate B coefficients.  Show your work.  Say which of the two candidates gives the *bigger* likelihood? 

`r I(textItem(name="bigger.likelihood", totalPts=2, rows=4))`

In an actual fitting calculation, the computer goes through large numbers of candidate coefficients in a systematic way to find the candidate with the largest possible likelihood: the maximum likelihood candidate.  
Explain why it makes sense to choose the candidate with the *maximum*  rather than the minimum likelihood.

`r I(textItem(name="maximum.likelihood", totalPts=2, rows=4))`

`r I(endProblem())`