Intro to Statistical Modeling Ch. 16 Prob. 4
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-16-4-SD")
```
George believes in astrology and wants to check whether a person's sign influences whether they are left- or right-handed.  With great effort, he collects data on 100 people, recording their dominant *hand* and their astrological *sign*.  He builds a logistic model *hand* ~ *sign*.  The deviance from the model *hand* ~ *1* is 102.8 on 99 degrees of freedom.  Including the *sign* term in the model reduces the deviance to 63.8 on 88 degrees of freedom.


The *sign* term only reduced the degrees of freedom by 11 (that is, from 99 to 88) even though there are 12 astrological signs.  Why? 
```{r include=FALSE}
f=newMC(totalPts=1, name="sign.term")
```
`r I(f(FALSE))` There must have been one sign not represented among the 100 people in George's sample.    
`r I(f(TRUE))` *sign* is redundant with the intercept and so one level is lost.    
`r I(f(FALSE))` *hand* uses up one degree of freedom.       
`r I(f(finish=TRUE))`

According to theory, if *sign* were unrelated to *hand*, the 11 degrees of freedom ought to reduce the deviance by how much, on average?
```{r include=FALSE}
g=newMC(totalPts=1, name="deviance.reduction")
```
`r I(g(TRUE))` $11/99 \times 102.8$   
`r I(g(FALSE))` $1/11 \times 102.8$    
`r I(g(FALSE))` to zero    
`r I(g(FALSE))` None of the above.    
`r I(g(finish=TRUE))`

`r I(endProblem())`