Intro to Statistical Modeling Ch. 13 Reading Questions
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-13-RQ-SD")
```
* What is a "null hypothesis?"  Why does it play a special role in hypothesis testing? 
```{r include=FALSE,eval=FALSE}
I(textItem(name="null", totalPts=2, rows=3))
```
 `r I(textItem(name="null", totalPts=2, rows=3))`

* Why is it good to have a hypothesis test with a low "significance level?" 
```{r include=FALSE,eval=FALSE}
I(textItem(name="significance", totalPts=2, rows=3))
```
 `r I(textItem(name="significance", totalPts=2, rows=3))`

* Why is it good to have a hypothesis test with a high "power?"
```{r include=FALSE,eval=FALSE}
I(textItem(name="power", totalPts=2, rows=3))
```
 `r I(textItem(name="power", totalPts=2, rows=3))`

* What is a p-value? 
```{r include=FALSE, eval=FALSE}
I(textItem(name="p-value", totalPts=2, rows=3))
```
 `r I(textItem(name="p-value", totalPts=2, rows=3))`

* Why are there two kinds of potential errors in hypothesis testing, Type I and Type II? 
```{r include=FALSE, eval=FALSE}
I(textItem(name="errors", totalPts=2, rows=3))
```
 `r I(textItem(name="errors", totalPts=2, rows=3))`

`r I(closeProblem())`