Intro to Statistical Modeling Ch. 13 Prob. 14
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-13-14-SD")
```
Consider these two sampling distributions:

```{r pair2,fig=TRUE,pdf=TRUE,echo=FALSE,figwidth=5,figheight=4}
x <- seq(-30,130,length=1000)
d1 <- dnorm(x,mean=35,sd=10)
d2 <- dnorm(x,mean=50,sd=30)
plot(x,d1,xlab='Test Statistic', main='Conditional Sampling Distributions', ylab='Prob. Density', type='l', lwd=8)
text(30,.02,'Null')
lines(x,d2, lwd=4, col='blue')
text(80,.015,'Alternative', col='blue')
``` 



```{r include=FALSE}
test=selectSet(name="powerful1tailedTest", totalPts=1, "About 5%"=FALSE, "About 50%"=TRUE, "About 95%"=FALSE, "Can't tell from the information given."=FALSE)
```
Suppose that you insisted that every hypothesis test have a significance of 0.05.  For the conditional sampling distributions shown above, what would be the power of the most powerful possible one-tailed test? `r I(test)`


```{r include=FALSE}
test2=selectSet(name="powerful2tailedTest", totalPts=1, "About 10% bigger than the one-tailed test."=TRUE, "About 10% smaller than the one-tailed test."=FALSE, "About 50% bigger than the one-tailed test."=FALSE, "About 50% smaller than the one-tailed test."=FALSE, "Can't tell from the information given."=FALSE)
```
What would be the power of the most powerful possible two-tailed test? `r I(test2)`

`r I(endProblem())`
