Intro to Statistical Modeling Ch. 13 Prob. 1
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-13-1-SD")
```
Which of the following are legitimate possible outcomes of a hypothesis test?  Mark as "true" any legitimate ones and "false" for any illegitimate ones.

```{r include=FALSE}
true=selectSet(name="TorF", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* accept the alternative hypothesis `r I(true)`
```{r include=FALSE}
true2=selectSet(name="TorF2", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* accept the null hypothesis `r I(true2)`
```{r include=FALSE}
true3=selectSet(name="TorF3", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* reject the alternative hypothesis `r I(true3)`
```{r include=FALSE}
true4=selectSet(name="TorF4", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* fail to reject the alternative hypothesis `r I(true4)`
```{r include=FALSE}
true5=selectSet(name="TorF5", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* reject the null hypothesis `r I(true5)`
```{r include=FALSE}
true6=selectSet(name="TorF6", totalPts=1, "TRUE"=TRUE, "FALSE"=FALSE)
```
* fail to reject the null hypothesis`r I(true6)`
```{r include=FALSE}
true7=selectSet(name="TorF7", totalPts=1, "TRUE"=FALSE, "FALSE"=TRUE)
```
* indeterminate result `r I(true7)`

Pick one of the illegitimate outcomes and explain why it is illegitimate.    
`r I(textItem(name="illegitimate", totalPts=2, rows=3))`

`r I(endProblem())`