Intro to Statistical Modeling Ch. 13 Prob. 2
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-13-2-SD")
```

Consider the two conditional sampling distributions shown in the figure.

```{r pair1,fig=TRUE,pdf=TRUE,echo=FALSE,figwidth=5,figheight=4}
x <- seq(0,100,length=1000)
d1 <- dnorm(x,mean=35,sd=10)
d2 <- dnorm(x,mean=65,sd=10)
plot(x,d1,xlab='Test Statistic', main='Conditional Sampling Distributions', ylab='Prob. Density', type='l', lwd=8)
text(30,.02,'Null')
lines(x,d2, lwd=4, col='blue')
text(80,.02,'Alternative', col='blue')
``` 

```{r include=FALSE}
test=selectSet(name="99perSignificance", totalPts=1, "About 0.05"=FALSE, "About 0.30"=TRUE, "About 0.95"=FALSE, "Can't tell (even approximately) from the information given."=FALSE)
```
Imagine that you set rejection criteria so that the power was 99%. What would be the significance of the test?  (Choose the best answer.) `r I(test)`

We sometimes speak of the probability of Type I or Type II errors. We want to know what sort of probability these are.  To simplify notation, we'll define the following outcomes:

* **N** The Null Hypothesis is correct.
* **A** The Alternative Hypothesis is correct.
* **Fail** Fail to reject the Null Hypothesis
* **Reject** Reject the Null Hypothesis.

```{r include=FALSE}
test2=selectSet(name="Type1", totalPts=1, "A joint probability: p(Reject and N)"=FALSE, "A joint probability: p(Fail and A)"=FALSE, "A conditional probability: p(Reject given N)"=TRUE, "A conditional probability: p(Reject given A)"=FALSE, "A marginal probability: p(Reject)"=FALSE, "A marginal probability: p(Fail)"=FALSE)
```
What is the probability of a Type I error? `r I(test2)`

```{r include=FALSE}
test3=selectSet(name="Type2", totalPts=1, "A joint probability: p(Reject and A)"=FALSE, "A joint probability: p(Fail and N)"=FALSE, "A conditional probabiltiy: p(Fail given N)"=FALSE, "A conditional probability: p(Fail given A)"=TRUE, "A marginal probability: p(N)"=FALSE, "A marginal probability: p(A)"=FALSE)
```
What is the probability of a Type II error? `r I(test3)`

`r I(endProblem())`