Intro to Statistical Modeling Ch. 4 Prob. 7
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-4-07-SD")
```

Read in the Galton height data

```{r}
g = fetchData("Galton")
```

```{r include=FALSE, eval=FALSE}
I(textItem(name="StdDev", totalPts=2, rows=3))
```

* What is the standard deviation of the height?      
`r I(textItem(name="StdDev", totalPts=2, rows=3))`

```{r include=FALSE, eval=FALSE}
I(textItem(name="GrandMean", totalPts=2, rows=3))
```

* Calculate the grand mean and, from that, the residuals of the
  actual heights from the grand mean.      
`r I(textItem(name="GrandMean", totalPts=2, rows=3))`

<aside>
```{r}
mean(height, data=g)

res0 = g$height - 66.76069
sd(res0)
```
</aside>

```{r include=FALSE}
stddev=selectNumber(choices=c(2.51,2.58,2.92,3.58,3.82), correct=c(3.58), totalPts=1, name="residuals")
```
What is the standard deviation of the residuals from this "grand mean"
model? `r I(stddev)` 

```{r include=FALSE, eval=FALSE}
I(textItem(name="group-wiseMean", totalPts=2, rows=3))
```
* Calculate the group-wise mean for the different sexes and, from
  that, the residuals of the actual heights from this group-wise
  model.     
  `r I(textItem(name="group-wiseMean", totalPts=2, rows=3))`

<aside>
```{r}
mod1 = mean( height ~ sex, data=g)
res1 = g$height - fitted( mod1, data=g)
sd(res1)
```
</aside>

```{r include=FALSE}
stddev2=selectNumber(choices=c(2.51,2.58,2.92,3.58,3.82), correct=c(2.51), totalPts=1, name="residuals2")
```

What is the standard deviation of the residuals from this group-wise
model? `r I(stddev2)`

```{r include=FALSE, eval=FALSE}
I(textItem(name="explain", totalPts=2, rows=4))
```

* Explain why the standard deviation of the residuals of the
  group-wise model less than the standard deviation of the residuals
  of the "grand mean" model.      
  `r I(textItem(name="explain", totalPts=2, rows=4))`
  
`r I(closeProblem())`