Intro to Statistical Modeling Ch.4 Prob. 8
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-4-P8-SD")
```

Create a spreadsheet with the three variables *distance*, *team*, and *position*, in the following way:




*distance* | *team* | *position*
:-----:|:-----:|:-----:
5 | Eagles | center
12 | Eagles | forward
11 | Eagles | end
2 | Doves | center
18 | Doves | end
12 | Penguins | forward
15 | Penguins | end
19 | Eagles | back
5 | Penguins | center
12 | Penguins | back




**A.** After entering the data, you can calculate the mean *distance* in various ways.

```{r include=FALSE}
distance=selectNumber(choices=c(4,9.25,10,11,11.1,11.75,12,14.67,15.5), correct=c(11.1), name="grandmean", totalPts=1)
```

* What is the grand mean distance? `r I(distance)`

```{r include=FALSE}
distance2=selectNumber(choices=c(4,9.25,10,11,11.1,11.75,12,14.67,15.5), correct=c(11.75), name="groupmean", totalPts=1)
```
* What is the group mean distance for the three teams?
  * Eagles `r I(distance2)`
  
```{r include=FALSE}
distance3=selectNumber(choices=c(4,9.25,10,11,11.1,11.75,12,14.67,15.5), correct=c(10), name="groupmean2", totalPts=1)
```
  * Doves `r I(distance3)`

```{r include=FALSE}
distance4=selectNumber(choices=c(4,9.25,10,11,11.1,11.75,12,14.67,15.5), correct=c(11), name="groupmean3", totalPts=1)
```
  * Penguins `r I(distance4)`     
  


* What is the group mean distance for the following positions?
```{r include=FALSE}
distance5=selectNumber(choices=c(4,9.25,10,11,11.1,11.75,12,14.67,15.5), correct=c(15.5), name="back", totalPts=1)
```
  * back `r I(distance5)`
  
```{r include=FALSE}
distance6=selectNumber(choices=c(4,9.25,10,11,11.1,11.75,12,14.67,15.5), correct=c(4), name="center", totalPts=1)
```
  * center `r I(distance6)`
  
```{r include=FALSE}
distance7=selectNumber(choices=c(4,9.25,10,11,11.1,11.75,12,14.67,15.5), correct=c(14.67), name="end", totalPts=1)
```
  * end `r I(distance7)`     


**B.** Now, just for the sake of developing an understanding of group means, you are going to change the *dist* data.  Make up values for *dist* so that the mean *dist* for Eagles is 14, for Penguins is 13, and for Doves is 15.

Cut and paste the output from R showing the means for these groups and then the means taken group-wise according to *position*.  
```{r include=FALSE, eval=FALSE}
I(textItem(name="means", totalPts=2, rows=4))
```
`r I(textItem(name="means", totalPts=2, rows=4))`


**C.** Now arrange things so that the means are as stated in (B) but **every** case has a residual of either $1$ or $-1$.
```{r include=FALSE, eval=FALSE}
I(textItem(name="means2", totalPts=2, rows=4))
```
`r I(textItem(name="means2", totalPts=2, rows=4))`

`r I(endProblem())`
