Intro to Statistical Modeling Ch. 4 Reading Questions
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-4-RQ-SD")
```

* Which is larger: variance of residuals, variance of the model values, or the variance of the actual values?
```{r include=FALSE, eval=FALSE}
I(textItem(name="larger", totalPts=2, rows=3))
```
 `r I(textItem(name="larger", totalPts=2, rows=3))`

* How can a difference in group means clearly shown by your data nonetheless be misleading?
```{r include=FALSE, eval=FALSE}
I(textItem(name="misleading", totalPts=2, rows=3))
```
 `r I(textItem(name="misleading", totalPts=2, rows=3))`

* What does it mean to partition variation?  What's special about the variance --- the square of the standard deviation --- as a way to measure variation?
```{r include=FALSE, eval=FALSE}
I(textItem(name="partition", totalPts=2, rows=3))
```
 `r I(textItem(name="partition", totalPts=2, rows=3))`

`r I(closeProblem())`