Intro to Statistical Modeling Ch. 4 Prob. 7
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-4-07-SD")
```

Read in the Galton height data into an object called `g`.

```{r}
g = fetchData("Galton")
```

* What is the standard deviation of the height? Enter the commands you used in the box, including the numerical result.     
`r I(textItem(name="StdDev", totalPts=2, rows=3))`

<aside>
```{r}
sd( ~height, data=g )
```
</aside>

* Calculate the grand mean and, from that, the residuals from the actual heights from the grand mean.   There will be several hundred residuals, one for each case in `Galton`.  Cut and paste your commands here, but include just the first line or two of the residuals:   
`r I(textItem(name="GrandMean", totalPts=2, rows=3))`

<aside>
```{r echo=1:2}
mean(~ height, data=g)
g = transform(g, resid=height-66.76069)
g$resid[1:20]
```
or you could use `mm()`
```{r results="hide"}
mod0 = mm(height~1, data=g)
resid(mod0)
```

```{r echo=FALSE}
resid(mod0)[1:20]
```
</aside>

```{r include=FALSE}
stddev=selectNumber(choices=c(2.51,2.58,2.92,3.58,3.82), correct=c(3.58), totalPts=1, name="residuals")
```
What is the standard deviation of the residuals from this "grand mean"
model? `r I(stddev)` 

<aside>
If you used the `transform()` method, then you created a variable `resid` in the dataframe `g`.
```{r}
sd(~resid, data=g)
```
Things are a bit easier if you used `mm()`
```{r}
sd(resid(mod0))
```
</aside>
              

```{r include=FALSE, eval=FALSE}
I(textItem(name="group-wiseMean", totalPts=2, rows=3))
```
* Calculate the group-wise mean for the different sexes and, from that, the standard deviation of the residuals of the actual heights from this group-wise model.  


```{r include=FALSE}
stddev2=selectNumber(choices=c(2.51,2.58,2.92,3.58,3.82), correct=c(2.51), totalPts=1, name="residuals2")
```

What is the standard deviation of the residuals from this group-wise
model? `r I(stddev2)`

<aside>
```{r}
mod1 = mm( height ~ sex, data=g)
sd(fitted(mod1))
```
</aside>



```{r include=FALSE, eval=FALSE}
I(textItem(name="explain", totalPts=2, rows=4))
```

* Explain briefly why the standard deviation of the residuals of the group-wise model is less than the standard deviation of the residuals from the "grand mean" model.      
  `r I(textItem(name="explain", totalPts=2, rows=4))`
  
`r I(endProblem())`
