Intro to Statistical Modeling Ch. 15 Prob. 5
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-15-5-SD")
```
A statistics student wrote:

> I'm interested in the publishing business, particularly magazines, and thought I would try a statistical analysis of some of the features of magazines. I looked at several different magazines, and recorded several variables, some of which I could measure from a single copy and some of which I deduced from my knowledge of the publishing business.

* **magazine**  a number to identify the magazine 

* **pages** the number of pages in a typical issue

* **color**  the number of pages with a color picture 

* **age** the age group of the target audience 

* **sex** the sex of the intended audience 

* **sentenceLength** the average number of words in a sentence in the articles in the magazine. 


Most people find it hard to believe, but most mass-market magazines are very deliberately written and composed graphically to be attractive to the target audience.  The distinctive "styles" of magazines is no accident.

I was interested to see if there is a relation between the average sentence length and any of the other variables. I made one linear model and had a look at the ANOVA table, as shown below.


Analysis of Variance Table

Response: sentenceLength    

| | &nbsp; Df &nbsp; | &nbsp; Sum Sq &nbsp; | &nbsp; Mean Sq &nbsp; | &nbsp; F value &nbsp; | &nbsp; Pr(>&#124;F&#124;) |
|:---|:---:|:---:|:---:|:---:|:---:|
| sex &nbsp; | 1 | 0.222 | 0.222 | 0.0717 | 0.80626 |  
| age | 3 | 71.067 | 23.689 | 7.6407 | ???? |  
| color | 1 | 0.299 | 0.299 | 0.0964 | 0.77647 |  
| Residuals &nbsp; | 3 | 9.301 | 3.100 | | |                 

Answer each question based on the information given above.

* What model structure did I use to generate this table?
```{r include=FALSE}
f=newMC(totalPts=1, name="model")
```
`r I(f(FALSE))` <code>sentenceLength ~ age + sex + color</code>    
`r I(f(FALSE))` <code>sentenceLength ~ sex * age + color</code>    
`r I(f(TRUE))` <code>sentenceLength ~ sex + age + color</code>    
`r I(f(FALSE))` <code>color ~ sentenceLength + sex + age</code>    
`r I(f(finish=TRUE))`

```{r include=FALSE}
prob1=selectSet(name="cases", totalPts=1, "8"=FALSE, "9"=TRUE, "10"=FALSE, "No way to tell from the information given."=FALSE)
```
* How many cases are there altogether? `r I(prob1)`

```{r include=FALSE}
prob2=selectSet(name="variable", totalPts=1, "categorical"=TRUE, "quantitative"=FALSE, "Could be either."=FALSE, "Can't know for sure from the data given."=FALSE)
```
* Is the variable <code>age</code> categorical or quantitative? `r I(prob2)`

* The p-value for <code>age</code> is missing. What should this value be?
```{r include=FALSE}
g=newMC(totalPts=1, name="p-value")
```
`r I(g(FALSE))` 0.93553 from <code>pf(7.6407, 3, 3)</code>    
`r I(g(TRUE))` 0.06446 from <code>1-pf(7.6407, 3, 3)</code>    
`r I(g(FALSE))` 0.98633 from <code>pf(23.689, 3, 3)</code>    
`r I(g(FALSE))` 0.01367 from <code>1-pf(23.689, 3, 3)</code>    
`r I(g(FALSE))` 0.99902 from <code>pnorm(23.689, 0, 7.6507)</code>    
`r I(g(FALSE))` 0.00098 from <code>1-pnorm(23.689, 0, 7.6507)</code>    
`r I(g(finish=TRUE))`

```{r include=FALSE}
prob3=selectSet(name="null.hypothesis", totalPts=1, "An average sentence has zero words."=FALSE, "There is no relationship between the number of color pages and the sex of the intended audience."=FALSE, "The number of color pages is not related to the sentence length."=FALSE, "There is no relation between the average number of words per sentence in an article and the age group that the magazine is intended for, after taking sex into account."=TRUE, "None of the above, because there is a different null hypothesis corresponding to each model term in the ANOVA report."=FALSE)
```
* Based on the ANOVA table, what null hypothesis can be rejected in this study at the significance level $p<0.10$? `r I(prob3)`

```{r include=FALSE}
prob4=selectSet(name="sex.age", totalPts=1, "To see if the different sexes have a different distribution of age groups."=FALSE, "To see if there is a difference in average sentence length between magazines for females and males."=FALSE, "To see if magazines for different age groups are targeted to different sexes."=FALSE, "To see if the difference in average sentence length between magazines for females and males changes from one age group to another."=TRUE)
```
* I really wanted to look to see if there is an interaction between <code>sex</code> and <code>age</code>.  What would be the point of including this term in the model? `r I(prob4)`

* I tried to include an interaction between *sex* and *age* into the model.  This didn't work out.  Just using the information in the printed ANOVA report, judge what might have gone wrong.  
```{r include=FALSE}
h=newMC(totalPts=1, name="what.went.wrong")
```
`r I(h(FALSE))` The term was included as the last term in the ANOVA report and
didn't have a significant sum of squares.    
`r I(h(FALSE))` I discovered that <cod>sex</code> and <code>age</code> were
redundant.    
`r I(h(TRUE))` The p-values disappeared from the report.    
`r I(h(FALSE))` None of the above.    
`r I(h(finish=TRUE))`

`r I(endProblem())`