Intro to Statistical Modeling Ch. 15 Prob. 10
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-15-10-SD")
```
P-values concern the "statistical significance" of evidence for a relationship.  This can be a different thing from the real-world importance of the observed relationship.  It's possible for a weak connection to be strongly statistically significant (if there is a lot of data for it) and for a strong relationship to lack statistical significance (if there is not much data).

Consider the data on the times it took runners to complete the Cherry Blossom ten-mile race in March 2005:
```{r}
run = fetchData("ten-mile-race.csv")
names(run)
```
**SHOULD MATCH**
[1] "state" "time"  "net"   "age"   "sex"  

Consider the <code>net</code> variable, which gives the time it took the runners to get from the start line to the finish line.

Answer each of the following questions, giving both a quantitative argument and also an everyday English explanation.  Assessing statistical significance is a technical matter, but to interpret the substance of a relationship, you will have to put it in a real-world context.

```{r include=FALSE, eval=FALSE}
I(textItem(name="time.age", totalPts=2, rows=3))
```
* What is the relationship between net running time and the runner's age?  Is the relationship significant?  Is it substantial?    
`r I(textItem(name="time.age", totalPts=2, rows=3))`

```{r include=FALSE, eval=FALSE}
I(textItem(name="time.sex", totalPts=2, rows=3))
```
* What is the relationship between net running time and the runner's sex?  Is the relationship significant?  Is it substantial?    
`r I(textItem(name="time.sex", totalPts=2, rows=3))`

```{r include=FALSE, eval=FALSE}
I(textItem(name="age.sex", totalPts=2, rows=3))
```
* Is there an interaction between sex and age?  Is the relationship significant?  Is it substantial?    
`r I(textItem(name="age.sex", totalPts=2, rows=3))`

`r I(closeProblem())`