Intro to Statistical Modeling Ch. 15 Prob. 2
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-15-2-SD")
```
Here is an ANOVA table (with the "intercept" term included) from a fictional study of scores assigned to various flavors, textures, densities, and chunkiness of ice cream.  Some of the values in the table have been left out.  Figure out from the rest of the table what they should be.

| | &nbsp; Df &nbsp; | &nbsp; Sum-Sq &nbsp; | &nbsp; Mean-Sq &nbsp; | &nbsp; F-value &nbsp; | &nbsp; p-value &nbsp; |
|:---|:---:|:---:|:---:|:---:|:---:|
| (intercept) | 1 | _A_ | 200 | _B_ | _C_ |
| flavor | 8 | 640 | 80 | _D_ | 0.134 |
| density | _E_ | 100 | 100 | 2 | 0.160 |
| fat-content | 1 | 300 | _F_ | 6 | 0.015 |  
| chunky | 1 | 200 | 200 | 4 | 0.048 |
| Residuals | 100 | 5000 | 50 | | |  

```{r include=FALSE}
prob1=selectNumber(name="A", totalPts=1, choices=c(1,2,100,200,400,600), correct=c(200))
```
* The value of A: `r I(prob1)`
```{r include=FALSE}
prob2=selectNumber(choices=c(1,2,3,4,5,6,7,8,10,20,200), correct=c(4), totalPts=1, name="B")
```
* The value of B: `r I(prob2)`
```{r include=FALSE}
prob3=selectNumber(choices=c(0.00,0.015,0.030,0.048,0.096,0.134,0.160,0.320,0.480), correct=c(0.048), totalPts=1, name="C")
```
* The value of C: (Hint: There's enough information in the table
  to find this.) `r I(prob3)`

<aside>
ANSWER:    
The p-value is set by the F-value and the degrees of freedom in the term and in the residuals.  Since the F-value for the intercept is 4, and there is one degree of freedom, it happens that the p-value for the intercept will match that for "chunky", which has the same F value and also a single degree of freedom.
</aside>

```{r include=FALSE}
prob4=selectNumber(choices=c(0.0,0.8,1.6,3.2,4.8), correct=c(1.6), totalPts=1, name="D")
```
* The value of D: `r I(prob4)`
```{r include=FALSE}
prob5=selectNumber(choices=c(0,1,2,3,4,5,6), correct=c(1), totalPts=1, name="E")
```
* The value of E: `r I(prob5)`
```{r include=FALSE}
prob6=selectNumber(choices=c(100,200,300,400,500), correct=c(300), totalPts=1, name="F")
```
* The value of F: `r I(prob6)`
```{r include=FALSE}
prob7=selectNumber(choices=c(50,100,111,112,200,5000), correct=c(112), totalPts=1, name="number.of.cases")
```
* How many cases are involved altogether? `r I(prob7)`
```{r include=FALSE}
prob8=selectNumber(choices=c(1,3,5,8,9,10,12,100),correct=c(9), totalPts=1, name="different.flavors")
```
* How many different flavors were tested? `r I(prob8)`

`r I(endProblem())`