Intro to Statistical Modeling Ch. 15 Prob. 21
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-15-21-SD")
```

In conducting a hypothesis test, we need to specify two things:
* A Null Hypothesis 
* A Test Statistic 

The numerical output of a hypothesis test is a p-value.

In modeling, a sensible Null Hypothesis is that one or more explanatory variables are unrelated to the response variable.  We can simulate a situation in which this Null applies by shuffling the variables.  For example, here are 
two trials of a simulation of the Null in a model of the kidsfeet data:
```{r}
kids = fetchData("KidsFeet")
lm( width ~ length + shuffle(sex), data=kids)
```

```{r}
lm( width ~ length + shuffle(sex), data=kids)
```

The test statistic summarizes the situation.  There are several possibilities, but here we will use $R^2$ from the model since this gives an indication of the quality of the model. 
```{r}
r.squared(lm( width ~ length + shuffle(sex), data=kids))
```

```{r}
r.squared(lm( width ~ length + shuffle(sex), data=kids))
```

```{r}
r.squared(lm( width ~ length + shuffle(sex), data=kids))
```

By computing many such trials, we construct the sampling distribution under the Null --- that is, the sampling distribution of the test statistic in the world in which the Null holds true.  We can automate this process using <code>do</code>:
```{r}
samps = do(1000) * 
+   r.squared(lm( width ~ length + shuffle(sex), data=kids))
```

Finally, to compute the p-value, we need to compute the test statistic on the model fitted to the  actual data, not on the simulation.  
```{r}
r.squared( lm( width ~ length + sex, data=kids))
```

The p-value is the probability of seeing a value of the test statistic from the Null Hypothesis simulation that is more extreme than our actual value.  The meaning of "more extreme" depends on what the test statistic is.  In this example, since a better fitting model will always have a larger $R^2$  we check the probability of getting a larger $R^2$ squares from our simulation than from the actual data.
```{r}
table( samps >= 0.4595428)
```

Our p-value is about 9%.

Here are various computer modeling statements that implement possible Null Hypotheses. Connect each computer statement to the corresponding Null.

1. <code> lm(width ~ length + shuffle(sex),data=kids) </code> 

2. <code> lm(width ~ shuffle(length) + shuffle(sex), data=kids) </code>

3. <code> lm(width ~ shuffle(length), data=kids) </code>

4. <code> lm(width ~ shuffle(sex), data=kids) </code>

5. <code> lm(width ~ length + sex, data=shuffle(kids)) </code>


```{r include=FALSE}
prob1=selectNumber(choices=c(1,2,3,4,5), correct=c(2), name="Statement1")
```
* Foot width is unrelated to foot length or to sex. `r I(prob1)`

<aside>
ANSWER:    
In (2), both length and sex are being randomized with respect to width.  After randomization, width is therefore unrelated to foot length or sex.  You could also do this to accomplish much the same thing.
```{r eval=FALSE}
lm(shuffle(width) ~ length + sex, data=kids)
```
</aside>

```{r include=FALSE}
prob2=selectNumber(choices=c(1,2,3,4,5), correct=c(1), name="Statement2")
```
* Foot width is unrelated to sex, but it is related   to foot length. `r I(prob2)`

<aside>
ANSWER:    
Only *sex* has been randomized in (1), leaving intact whatever is the relationship between *length* and *width*.
</aside>

```{r include=FALSE}
prob3=selectNumber(choices=c(1,2,3,4,5), correct=c(4), name="Statement3")
```
* Foot width is unrelated to sex, and we won't consider any possible relationship to foot length. `r I(prob3)`

<aside>
ANSWER:    
In (4), the variable *length* doesn't appear, so the model doesn't take *length* into account.  *sex* has been randomized, so it has been made unrelated to the response variable, *width*.
</aside>

```{r include=FALSE}
prob4=selectNumber(choices=c(1,2,3,4,5), correct=c(3), name="Statement4")
```
* Foot width is unrelated to foot length, and we won't consider any possible relationship to sex. `r I(prob4)`

<aside>
ANSWER:    
In (3), *sex* has been left out of the model and *length* has been randomized.
</aside>

```{r include=FALSE}
prob5=selectNumber(choices=c(1,2,3,4,5), correct=c(5), name="Statement5")
```
* This isn't a hypothesis test; the randomization won't change anything from the original data. `r I(prob5)`


<aside>
ANSWER:    
In (5), the data are being shuffled, just like a deck of cards is shuffled.  But each of the cases is being left intact, there is no randomization of variables with respect to one another.  Thus, the statement in (5) --- which is pretty useless --- just fits the model on shuffled data.  Keep in mind that \texttt{shuffle} will deal out all of the cases, as if the entire deck of shuffled cards were being dealt out.  So the shuffled data is the same as the original --- it's the same sample.
</aside>


`r I(endProblem())`