Intro to Statistical Modeling Ch. 15 Prob. 1
=============================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-15-1-SD")
```

Often we are interested in whether two groups are different.  For example,  we might ask if girls have a different mean footlength than do boys.  We can answer this question by constructing a suitable model.
```{r}
kids = fetchData("KidsFeet")
summary( lm( length ~ sex, data=kids ) )
```

Interpret this report, keeping in mind that the foot length is reported in centimeters.  (The reported value *<2e-16* means $p < 2 \times 10^{-16}$.)

```{r include=FALSE}
prob1=selectSet(name="point.estimate", totalPts=1, "Girls' feet are, on average, 25 centimeters long."=FALSE, "Girls' feet are 0.4079 cm shorter than boys'."=FALSE, "Girls' feet are 0.7839 cm shorter than boys'."=TRUE, "Girls' feet are $1.922$ cm shorter than boys'."=FALSE)
```
What is the point estimate of the difference between the lengths of boys and girls feet. `r I(prob1)`

<aside>
ANSWER:    
The difference between the typical foot *length* of the two sexes is indicated by the *sexG* coefficient.  It's negative, meaning that level G (that is, girls) has a smaller typical foot length.
</aside>

```{r include=FALSE}
prob2=selectNumber(choices=c(-0.78,0.28,0.41,0.60,0.80), correct=(0.80), totalPts=1, name="95.marg.error")
```
The confidence interval can be written as a point estimate plus-or-minus a margin of error: $P \pm M$.  What is the 95% margin of error, $M$, on the difference between boy's and girl's foot lengths. `r I(prob2)`

<aside>
ANSWER:    
The standard error on the *sexG* coefficient is 0.41.  Doubling that gives a 95% margin of error.  
</aside>

```{r include=FALSE}
prob3=selectSet(name="null.hypothesis", totalPts=1, "Boys' feet are, on average, longer than girls' feet."=FALSE, "Girls' feet are, on average,  shorter than boys' feet."=FALSE, "All boys' feet are longer than all girls' feet."=FALSE, "No girl's foot is shorter than all boys' feet."=FALSE, "There is no difference, on average, between boys' footlengths and girls' footlengths."=TRUE)
```
What is the Null Hypothesis being tested by the reported p-value $0.0623$? `r I(prob3)`

<aside>
ANSWER:    
The p-value in a regression report relates to the null hypothesis that the corresponding coefficient is zero *in the population*.  So the p-value of $0.0623$, which corresponds to the *sexG* coefficient, is against the null that that coefficient would be 0 in the population.  That means that in the population there is no difference between the foot *length* of girls and boys.
</aside>

```{r include=FALSE}
prob4=selectSet(name="null.hypothesis.intercept", totalPts=1, "Boys' and girls' feet are, on average, the same length."=FALSE, "The length of kids' feet is, on average, zero."=FALSE, "The length of boys' feet is, on average, zero."=TRUE, "The length of girls' feet is, on average, zero."=FALSE, "Girls' and boys' feet don't intercept."=FALSE)
```
What is the Null Hypothesis being tested by the p-value on the intercept? `r I(prob4)`

<aside>
ANSWER:     
The intercept in this model corresponds to the mean foot *length* of the reference group: boys.  So the p-value is that the length of boys' feet is, on average, zero.  That's obviously wrong, which is why the p-value is so very, very small.
</aside>

Here is the report from a related, but slightly different model:
```{r}
summary( lm( length~sex-1, data=kids ))
```

Note that the p-values for both coefficients are practically zero, $p < 2 \times 10^{-16}$.

```{r include=FALSE}
prob5=selectSet(name="null.hypothesis.sexG", totalPts=1, "Girls' feet have a different length, on average, than boys'."=FALSE, "Girls' feet are no different in length, on average, than boys'."=FALSE, "Girls' footlengths are, on average, zero."=TRUE, "Girls' footlengths are, on average, greater than zero."=FALSE)
```
What is the Null Hypothesis tested by the p-value on *sexG*? `r I(prob5)`

<aside>
ANSWER:    
Since there's no intercept in this model, the *sexG* coefficient refers to the mean of the girls' foot *length*.  So the p-value relates to the null hypothesis that the mean girls foot *length* is zero.  Again, that's obviously wrong, which is why the p-value is so small.
</aside>

`r I(endProblem())`