Chapter 2, Problem 1
========================

```{r include=FALSE}
require(WriteScoreR)
newScorerSet("Ch2-prob1-DTK-2013-05-26")
require(mosaic)
```

CASES AND VARIABLES.  `HELPrct`

How many cases? use `nrow()`

Which of these is a variable?

Chapter 2, Problem 5
========================

Introduce `with(data=HELPrct, class(satreat))`

Which of these is a quantitative variable?

Which of these is a categorical variable?




Using the `tally()` operator to construct the appropriate tables of counts, answer the following questions about the `CO2` data.  (Hint: For some problems, you can read the answer directly from the table.  For others, you may need to add up different counts.)

**Example 1**: How many of the cases in `CO2` have level `Mc1` in the variable `Plant`? 

```{r}
tally( ~ Plant, data=CO2 )
```
Reading from the table, the count for level `Mc1` is 7 (as are all the other levels in this case.)





* **1**. How many of the plants in CO2 are either Mc1 or Mn1? `r I(selectNumber(choices=c(8,12,14,16,23,54,92),correct=14))`

For the remaining questions, you will use the `>=` and `<=` comparison operators.

**Example 2**: How many cases have a concentration (`conc`) of 300 or bigger?
```{r}
tally( ~ conc >= 300, data=CO2 )
```
48 cases satisfy the criterion

* **2**: How many cases have a concentration less than 200?

* **3**: How many cases have a concentration greater than 600?
 12  24  36  48  60  

For the remaining questions, you will combine two or more variables using the `&` operator: 

**Example 3**: How many of the cases in `CO2` have level `Quebec` for variable `Type` and level `nonchilled` for variable `Treatment`?

```{r}
tally( ~Type & Treatment, data=CO2 )
```
You can read the answer, 21, off the table.
5.
How many have a concentration between 300 and 450 (inclusive)?
 12  24  36  48  60  
6.
How many have a concentration between 300 and 450 (inclusive) and are nonchilled?
 6  8  10  12  14  16  
7.
How many have an uptake that is less than 1/10 of the concentration (in the units reported)?
 17  33  34  51  68  


`r I(closeProblem())`
#### from [Statistical Modeling: A Fresh Approach](http://www.mosaic-web.org/go/StatisticalModeling/)