Writing ScoreR Problems
========================================================

```{r include=FALSE}
require(WriteScoreR)
newScorerSet("intro-DTK-2013-05-23")
```

<aside>

### With answers displayed!
This example shows the conditional display of answers using the "aside" HTML flag.</aside>

A **ScoreR** problem is a Rmd/HTML file containing zero or more items.  There are three types of items:


### Selection from a set.

This is intended for a set of short answers, e.g. one-word or number.

DOCUMENT THIS IN selectSet.Rmd -- can use numbers in quotes, can use TRUE and FALSE to indicate correctness, can give a hint in the yes/no function.

```{r include=FALSE}
spainrain = selectSet("Rain",reward="My Fair Lady!",
                       Algeria=no(hint="Wrong continent"),
                       "1492"=no(),
                       Spain=yes())
hurricanes= selectSet(name="Hurricanes", often=no(),usually=no(),"hardly ever"=yes())
horses = selectSet(name="Horses",Ascot=TRUE,Pimlico=TRUE,"Yankee Stadium"=FALSE)
```

* The rain in BLANK falls mainly on the plain. `r I(spainrain)`
* In Hartford, Hereford and Hampshire, hurricanes BLANK happen: `r I(hurricanes)`
* Horses race at : `r I(horses)`

<aside>You can also put answers in the markup, which will be displayed only if the Answer field is set to `TRUE`</aside>

### Multiple choice, which can have short or long answers.

Which of these is the start of the "Declaration of Independence"?

```{r include=FALSE}
f = newMC(totalPts=5,name="Declaration") # Ordinarily, make this silent
```
`r I(f(FALSE))` "We the people of the United States of America, in order to form a more perfect union ..."

`r I(f(TRUE))` "When in the course of human events, it becomes necessary ..."

`r I(f(FALSE))` "Four score and seven years ago, our forefathers brought forth upon this continent, a new nation, conceived in liberty and dedicated to the proposition that all men are created equal." 
`r I(f(finish=TRUE))`

### Free text.

What would you like to write a question about?     
`r I(textItem(name="question-topic",rows=3))`

You can re-size the text box on most browsers.  

**Remember to press** the radio button to submit your answer.

## For the future

1. Numerical entry
2. The markup contains provisions for hints and rewards.  These are not yet displayed.
3. In an interactive mode, the result will be shown immediately.

`r I(closeProblem())`

#### Danny Kaplan
#### May 22, 2013