Intro to Statistical Modeling Ch. 3 Prob. 3.19
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P19-SD")
```

Consider a large company where the average wage of workers is $15 per hour, but there is a spread of wages from minimum wage to $35 per hour.  


After a contract negotiation, all workers receive a $2 per hour raise.
What happens to the standard deviation of hourly wages?

```{r include=FALSE}
f = newMC(totalPts=1)
```
 `r I(f(TRUE))` No change.     
 `r I(f(FALSE))` It goes up by $2 per hour.     
 `r I(f(FALSE))` It goes up by $4 per hour.     
 `r I(f(FALSE))` It goes up by 4 dollars-square per hour.     
 `r I(f(FALSE))` It goes up by $4 per hour-square.     
 `r I(f(FALSE))` Can't tell from the information given.     
 
```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```

The annual cost-of-living adjustment is 3%.  After the cost-of-living adjustment, what happens to the standard deviation of hourly wages?

```{r include=FALSE}
g = newMC(totalPts=1)
```
 `r I(g(FALSE))` No change.     
 `r I(g(TRUE))` It goes up by 3%.     
 `r I(g(FALSE))` It goes up by 9%.     
 `r I(g(FALSE))` Can't tell from the information given.     
 
```{r include=FALSE, results="hide"}
I(g(finish=TRUE))
```

`r I(closeProblem())`