Intro to Statistical Modeling Ch. 3 Prob. 19
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-3-P19-SD")
```

Consider a large company where the average wage of workers is $15 per hour, but there is a spread of wages from minimum wage to $35 per hour.  

```{r include=FALSE}
prob1=selectSet(name="std.dev", totalPts=1, "No change."=TRUE, "It goes up by $2 per hour."=FALSE, "It goes up by $4 per hour."=FALSE, "It goes up by 4 dollars-square per hour."=FALSE, "It goes up by $4 per hour-square."=FALSE, "Can't tell from the information given."=FALSE)
```
After a contract negotiation, all workers receive a $2 per hour raise.
What happens to the standard deviation of hourly wages? `r I(prob1)`

```{r include=FALSE}
prob2=selectSet(name="std.dev.2", totalPts=1, "No change."=FALSE, "It goes up by 3%."=TRUE, "It goes up by 9%."=FALSE, "Can't tell from the information given."=FALSE)
```
The annual cost-of-living adjustment is 3%.  After the cost-of-living adjustment, what happens to the standard deviation of hourly wages? `r I(prob2)`

 
`r I(endProblem())`