Intro to Statistical Modeling Ch. 3 Prob. 3.24
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-3-P24-SD")
```
Data on the distribution of economic variables, such as income, is often presented in quintiles: divisions of the group into five equal-sized parts.  

Here is a table from the US Census Bureau (Historical Income Tables from March 21, 2002) giving the distribution of income across US households in year 2000.

Quintile   |   Upper Boundary   |   Mean Value
:-------:|:-------:|:-------:
Lowest | $17,955 | $10,190
Second | $33,006 | $25,334
Third  | $52,272 | $42,361
Fourth | $81,960 | $65,729
Fifth | --- | $141,260

Based on this table, calculate:

* The 20th percentile of family income. 
```{r include=FALSE}
econ=selectNumber(choices=c(10190,17955,33006,25334,52272,42361,81960,141260), correct=c(17955), name="20percent", totalPts=1)
```
  `r I(econ)`

* The 80th percentile of family income.
```{r include=FALSE}
econ2=selectNumber(choices=c(10190,17955,33006,25334,52272,42361,81960,141260), correct=c(81960), name="80percent", totalPts=1)
```
  `r I(econ2)`
  
* The table doesn't specify the median family income but you can
  make a reasonable estimate of it.  Pick the closest one.
```{r include=FALSE}
econ3=selectNumber(choices=c(10000,18000,25500,42500,53000,65700), correct=c(42500), name="medfaminc", totalPts=1)
```
  `r I(econ3)`

* Note that there is no upper boundary reported for the fifth
  quintile, and no lower boundary reported for the first quintile.
  Why?

  `r I(textItem(name="noUpnoLow", rows=4, totalPts=2))`
  
* From this table, what evidence is there that family income has a
  skew rather than ``normal'' distribution?

  `r I(textItem(name="skew", rows=4, totalPts=2))`

`r I(endProblem())`