Intro to Statistical Modeling Ch. 3 Prob. 3.54
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-03-P54-SD")
```

There are two kinds of questions that are often asked relating to
percentiles:


* What is the value that falls at a given percentage?  For instance, in the <code>ten-mile-race.csv</code> running data, how fast are the fastest 10% of runners? In R, you would ask in this way:

```{r}
run = fetchData("ten-mile-race.csv")     
qdata(0.10, run$net)     
```

The answers is in the units of the  variable, in this case seconds.
So 10% of the runners have net times faster than or equal to 4409 seconds.

* What percentage falls at a given value?  For instance, what
  fraction of runners are faster than 4000 seconds?

```{r}
pdata(4000, run$net)     
```

The answer includes those whose *net* time is exactly **equal to** or
**less than** 4000 seconds.

It's important to pay attention to the <code>p</code> and <code>q</code> in the statement.  <code>pdata</code> and <code>qdata</code> ask related but different questions.

Use <code>pdata</code> and <code>qdata</code> to answer the following
questions about the running data.

* **Below (or equal to)  what age are the youngest 35% of
  runners?**     
  * Which statement will do the correct calculation?
```{r include=FALSE}
f = newMC(totalPts=1, name="correct.statement")
```
  `r I(f(FALSE))` <code>pdata(0.35,run$age)</code>     
  `r I(f(TRUE))` <code>qdata(0.35,run$age)</code>     
  `r I(f(FALSE))` <code>pdata(35,run$age)</code>     
  `r I(f(FALSE))` <code>qdata(35,run$age)</code>
`r I(f(finish=TRUE))`

```{r include=FALSE}
run=selectNumber(choices=c(28,29,30,31,32,33,34,35), correct=c(31), totalPts=1, name="answer")
```
  * What will the answer be? `r I(run)`
  
* **What's the *net* time that divides the slowest 20% of
  runners from the rest of the runners?**     
  * Which statement will do the correct calculation?
```{r include=FALSE}
g=newMC(totalPts=1, name="correct.statement2")
```
  `r I(g(FALSE))` <code>pdata(0.20,run$net)</code>     
  `r I(g(FALSE))` <code>qdata(0.20, run$net)</code>     
  `r I(g(FALSE))` <code>pdata(0.80,run$net)</code>     
  `r I(g(TRUE))` <code>qdata(0.80, run$net)</code>    
`r I(g(finish=TRUE))`

```{r include=FALSE}
ans=selectNumber(choices=c(4921,5318,5988,6346,7123,7431), correct=c(6346), totalPts=1, name="nettime")
```
  
  * What will the answer be? `r I(ans)`
  


* **What is the 95% coverage interval on age?**     
  * Which statement will do the correct calculation?
```{r include=FALSE}
h=newMC(totalPts=1, name="correct.statement3")
```
  `r I(h(FALSE))` <code>pdata(c(0.025,0.975),run$age)</code>     
  `r I(h(TRUE))` <code>qdata(c(0.025,0.975),run$age)</code>     
  `r I(h(FALSE))` <code>pdata(c(0.050,0.950),run$age)</code>     
  `r I(h(FALSE))` <code>qdata(c(0.050,0.950),run$age)</code>
`r I(h(finish=TRUE))`

  * What will the answer be?
```{r include=FALSE}
j=newMC(totalPts=1, name="95per")
```
  `r I(j(TRUE))` 22 to 60     
  `r I(j(FALSE))` 20 to 65     
  `r I(j(FALSE))` 25 to 59     
  `r I(j(FALSE))` 20 to 60     
`r I(j(finish=TRUE))`

* **What fraction of runners are 30 or younger?**     
  * Which statement will do the correct calculation?
```{r include=FALSE}
k=newMC(totalPts=1, name="correct.statement4")
```
  `r I(k(TRUE))` <code>pdata(30, run$age)</code>
  `r I(k(FALSE))` <code>qdata(30, run$age)</code>     
  `r I(k(FALSE))` <code>pdata(30.1, run$age)</code>     
  `r I(k(FALSE))` <code>qdata(30.1, run$age)</code>
`r I(k(finish=TRUE))`

```{r include=FALSE}
ans2=selectNumber(choices=c(29.3,30.1,33.7,35.9,38.0,39.3), correct=c(33.7), totalPts=1, name="<30")
```
  * What will the answer be? In percent: `r I(ans2)` 



* **What fraction of runners are 65 or older?**  (Caution: This isn't
  yet in the form of a BELOW question.)     
  * Which statement will do the correct calculation?
```{r include=FALSE}
l=newMC(totalPts=1, name="correct.statement5")
```
  `r I(l(FALSE))` <code>pdata(65, run$age)</code>     
  `r I(l(FALSE))` <code>pdata(64.99, run$age)</code>     
  `r I(l(FALSE))` <code>pdata(65.01, run$age)</code>      
  `r I(l(FALSE))` <code>1-pdata(65, run$age)</code>     
  `r I(l(TRUE))` <code>1-pdata(64.99, run$age)</code>          
  `r I(l(FALSE))` <code>1-pdata(65.01, run$age)</code>     
`r I(l(finish=TRUE))`

<aside>
ANSWER:
Since <code>pdata</code> answers a *below* question, the first step is to ask a relevant question in that form.  You want the runners who are 65 or older, which is related to the fraction who are younger than 65.  So, <code>pdata(64.99, run$age)</code>  %$ which works because the ages are in integer years.  Subtract that answer from 1 to get the final answer.
</aside>

```{r include=FALSE}
ans3=selectNumber(choices=c(0.5,1.1,1.7,2.3,2.9), correct=c(1.1), totalPts=1, name="65plus")
```
  * What will the answer be? In percent: `r I(ans3)`

The time it takes for a runner to get to the start line after the starting gun is fired is the difference between the *time* and *net*.       

<code>
run$to.start = run$time - run$net
</code>

```{r include=FALSE}
ans4=selectNumber(choices=c(164,192,213,294,324,351), correct=c(351), totalPts=1, name="startline")
```
* **How long is it before 75% of runners get to the start line?** In seconds: `r I(ans4)` 


```{r include=FALSE}
ans5=selectNumber(choices=c(10,15,19,22,25,31,34), correct=c(25), totalPts=1, name="fraction")
```
* **What fraction of runners get to the start line before one
  minute?**  (Caution: the times are measured in seconds.) In percent: `r I(ans5)`

* **What is the 95% coverage interval on the ages of female
  runners?**
```{r include=FALSE}
m=newMC(totalPts=1, name="95per.fem.runners")
```
  `r I(m(FALSE))` 19 to 61 years     
  `r I(m(FALSE))` 22 to 61 years     
  `r I(m(FALSE))` 19 to 56 years     
  `r I(m(TRUE))` 22 to 56 years     
`r I(m(finish=TRUE))`

```{r include=FALSE}
ans6=selectNumber(choices=c(3.72,4.00,4.03,4.07,5.21), correct=c(4.00), totalPts=1, name="net.time<4000")
```
* **What fraction of runners have a *net* time BELOW 4000 seconds?**  (That is, don't include those who are at exactly 4000 seconds.) In percent: `r I(ans6)` 

`r I(endProblem())`