Intro to Statistical Modeling Ch. 3 Prob. 3.11
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P11-SD")
```

By hand, calculate the mean, the range, the variance, and the standard
deviation of each of the following sets of numbers:

  ( A ) $1, 0, -1$

  ( B ) $1, 3$

  ( C ) $1, 2, 3$.

* Which of the 3 sets of numbers --- A, B, or C --- is the most spread out according to the range? 
```{r include=FALSE}
f = newMC(totalPts=1)
```
  `r I(f(FALSE))` A     
  `r I(f(FALSE))` B      
  `r I(f(FALSE))` C     
  `r I(f(FALSE))` No way to know     
  `r I(f(TRUE))` All the same       
```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```


* Which of the 3 sets of numbers  --- A, B, or C --- is the most spread out according to the standard deviation?
```{r include=FALSE}
g = newMC(totalPts=1)
```
  `r I(g(FALSE))` A     
  `r I(g(TRUE))` B     
  `r I(g(FALSE))` C     
  `r I(g(FALSE))` No way to know     
  `r I(g(FALSE))` All the same

```{r include=FALSE, results="hide"}
I(g(finish=TRUE))
```

`r I(closeProblem())`



