Intro to Statistical Modeling Ch. 3 Prob. 9
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-3-P9-SD")
```


Here is a boxplot:    
```{r plot1, fig.width=4,fig.height=4,echo=FALSE,dev="svg",out.width="70%"}
x = rbinom(1000,10, .2)
boxplot(x)
```


Reading from the graph, answer the following:

* What is the median?
```{r include=FALSE}
graph=selectSet(name="median", totalPts=1, "0"=FALSE, "1"=FALSE, "2"=TRUE, "3"=FALSE, "6"=FALSE, "Can't estimate from this graph"=FALSE)
```

 `r I(graph)`
                             
<aside> ANSWER:
The boxplot displays the 25th, 50th, and 75th percentiles as the
bottom, middle, and top of the box.  
the 
</aside>

* What is the 75th percentile?
```{r include=FALSE}
graph2=selectSet(name="75percentile", totalPts=1, "0"=FALSE, "1"=FALSE, "2"=FALSE, "3"=TRUE, "6"=FALSE, "Can't estimate from this graph"=FALSE)
```

 `r I(graph2)`

* What is the IQR?
```{r include=FALSE}
graph3=selectSet(name="IQR", totalPts=1, "0"=FALSE, "1"=FALSE, "2"=TRUE, "3"=FALSE, "4"=FALSE, "6"=FALSE, "Can't estimate from this graph"=FALSE)
```

 `r I(graph3)`

<aside>
ANSWER:
The IQR is the distance between the 25th and 75th percentiles.
</aside>

```{r include=FALSE}
prob1=selectSet(name="40per", totalPts=1, "Between 0 and 1"=FALSE, "Between 1 and 2"=TRUE, "Between 2 and 3"=FALSE, "Between 3 and 4"=FALSE, "Between 4 and 6"=FALSE, "Can't estimate from this graph"=FALSE)
```
* What is the 40th percentile? `r I(prob1)`

<aside>
ANSWER:
The 40th percentile **must** be somewhere between the 25th and 50th
percentiles, both of which can be read off the graph.
</aside>

`r I(endProblem())`