Intro to Statistical Modeling Ch. 3 Prob. 3.09
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P9-SD")
```


Here is a boxplot:
```{r, eval=FALSE}
plot1, fig=true,include=false,width=4,height=4,echo=false
x = rbinom(1000,10, .2)
boxplot(x)
```

```{r, eval=FALSE}
includegraphics[width=2.5in]{Figures/AC128-plot1.pdf
```


Reading from the graph, answer the following:

* What is the median?
```{r include=FALSE}
graph=selectSet(name="median", totalPts=1, "0"=FALSE, "1"=FALSE, "2"=TRUE, "3"=FALSE, "6"=FALSE, "Can't estimate from this graph"=FALSE)
```

 `r I(graph)`
                             
<aside> ANSWER:
The boxplot displays the 25th, 50th, and 75th percentiles as the
bottom, middle, and top of the box.  
the 
</aside>

* What is the 75th percentile?
```{r include=FALSE}
graph2=selectSet(name="75percentile", totalPts=1, "0"=FALSE, "1"=FALSE, "2"=FALSE, "3"=TRUE, "6"=FALSE, "Can't estimate from this graph"=FALSE)
```

 `r I(graph2)`

* What is the IQR?
```{r include=FALSE}
graph3=selectSet(name="IQR", totalPts=1, "0"=FALSE, "1"=FALSE, "2"=TRUE, "3"=FALSE, "4"=FALSE, "6"=FALSE, "Can't estimate from this graph"=FALSE)
```

 `r I(graph3)`

<aside>
ANSWER:
The IQR is the distance between the 25th and 75th percentiles.
</aside>

* What is the 40th percentile?
```{r include=FALSE}
f = newMC(totalPts=1)
```

 `r I(f(FALSE))` Between 0 and 1     
 `r I(f(TRUE))` Between 1 and 2      
 `r I(f(FALSE))` Between 2 and 3      
 `r I(f(FALSE))` Between 3 and 4     
 `r I(f(FALSE))` Between 4 and 6      
 `r I(f(FALSE))` Can't estimate from this graph     
 
```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```

<aside>
ANSWER:
The 40th percentile **must** be somewhere between the 25th and 50th
percentiles, both of which can be read off the graph.
</aside>

`r I(closeProblem())`