Intro to Statistical Modeling Ch.3 Prob. 4
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P4-SD")
```

In Galton's data, are the sons typically taller than their fathers? 
Create a variable that is
the difference between the son's height and the father's height.
(Arrange it so that a positive number refers to a son who is taller
than his father.)

```{r include=FALSE}
galtondata=selectNumber(choices=c(-2.47,-0.31,0.06,66.76,69.23), correct=c(0.06), name="meanDifference", totalPts=1)
```
1. What's the mean height difference (in inches)? `r I(galtondata)`

```{r include=FALSE}
galtondata2=selectNumber(choices=c(1.32,2.63,2.74,3.58,3.75), correct=c(2.74), name="StdDev", totalPts=1)
```
2. What's the standard deviation (in inches)? `r I(galtondata2)`

```{r include=FALSE}
f=newMC(totalPts=1)
```
3. What is the 95-percent coverage interval (in inches)?      
  `r I(f(FALSE))` -3.7 to 4.8      
  `r I(f(FALSE))` -4.6 to 4.9     
  `r I(f(TRUE))` -5.2 to 5.6     
  `r I(f(FALSE))` -9.5 to 4.5     
```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```

<aside>
ANSWER:
First, you need to pull out the data for males.     
<code>
\> males = subset( galton, sex=='M')     
\> mean(males$height - males$father)     
[1] 0.06065     
\> sd(males$height - males$father)     
[1] 2.735     
\> quantile(males$height - males$father, c(.025,.975))     
 2.5% 97.5%      
-5.18  5.58      
</code>
</aside>

`r I(closeProblem())`
