Intro to Statistical Modeling Ch. 3 Prob. 3.01
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P1-SD")
```

Here is a small table of percentiles of typical daily calorie consumption 
of college students.


Percentile  | Calories
:-----:|:-----:
0 | 1400
5 | 1800
10 | 2000
25 | 2400
50 | 2600
75 |  2900
90 |  3100
95 |  3300
100 | 3700



What is the 50%-coverage interval?
```{r include=FALSE}
college=selectNumber(name="50percentLow", totalPts=1, choices=c(1800,1900,2000,2200,2400,2500,2600), correct=c(2400))
```
* Lower Boundary `r I(college)`
```{r include=FALSE}
college2=selectNumber(name="50percentUp", totalPts=1, choices=c(2600,2750,2900,3000,3100,3200,3500), correct=c(2900))
```
* Upper Boundary `r I(college2)`


What percentage of cases lie between 2900 and 3300? 
```{r include=FALSE}
college3=selectNumber(name="between", totalPts=1, choices=c(10,20,25,30,40,50,60,70,80,90,95), correct=c(20))
```
`r I(college3)`

What is the percentile
that marks the upper end of the
95%-coverage interval?
```{r include=FALSE}
college4=selectNumber(name="UpperEnd", totalPts=1, choices=c(75,90,92.5,95,97.5,100), correct=c(97.5))
```
`r I(college4)`

Estimate the corresponding calorie value from the table.
```{r include=FALSE}
estimate=selectNumber(name="calvalue", totalPts=1, choices=c(2900,3000,3100,3300,3500,3700), correct=c(3500))
```
`r I(estimate)`

Using the 1.5 IQR rule-of-thumb for identifying an outlier,
what would be the threshold for identifying a low calorie consumption as 
an outlier?
```{r include=FALSE}
estimate2=selectNumber(name="IQR", totalPts=1, choices=c(1450,1500,1650,1750,1800,2000), correct=c(1650))
```

`r I(estimate2)`


`r I(closeProblem())`

