Intro to Statistical Modeling Ch. 3 Prob 3.14
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-3-P14-SD")
```

The boxplots below are all made from exactly the same data.  One of
them is made correctly, according to the ``1.5 IQR'' convention for
drawing the whiskers.  The others are drawn differently.

```{r, echo="false"}
dd = c( jitter(seq(-10,10,by=1)), runif(1000,-3,3) )
```

### Plot 1     
```{r b1,fig.width=3,fig.height=5,echo=FALSE, dev="svg", out.width="20%"}
boxplot(dd,range=2.5,pch=20)
```     
     
### Plot 2     
```{r b2,fig.width=3,fig.height=5,echo=FALSE, dev="svg", out.width="20%"}
boxplot(dd,pch=20)
```

### Plot 3     
```{r b3,fig.width=3,fig.height=5,echo=FALSE,dev="svg", out.width="20%"}
boxplot(dd,range=1,pch=20)
```

### Plot 4     
```{r b4,fig.width=3,fig.height=5,echo=FALSE, dev="svg", out.width="20%"}
boxplot(dd,range=0,pch=20)
```



Which of the plots is correct?
```{r include=FALSE}
plots=selectNumber(choices=c(1,2,3,4), correct=c(2), name="correctplot", totalPts=1)
```

 `r I(plots)`

<aside>
ANSWER:
The height of the box gives the IQR.  If there are outliers, the whisker length should be 1.5
times the IQR.  So look for the plot that has a whisker length
somewhat taller than the box itself.
</aside>
