Intro to Statistical Modeling Ch. 3 Prob. 4
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-3-P4-SD")
```

```{r include=FALSE}
galton=fetchData("Galton")
```

In Galton's data, are the sons typically taller than their fathers? Create a variable that is the difference between the son's height and the father's height. (Arrange it so that a positive number refers to a son who is taller than his father.)

```{r include=FALSE}
galtondata=selectNumber(choices=c(-2.47,-0.31,0.06,66.76,69.23), correct=c(0.06), name="meanDifference", totalPts=1)
```
1. What's the mean height difference (in inches)? `r I(galtondata)`

```{r include=FALSE}
galtondata2=selectNumber(choices=c(1.32,2.63,2.74,3.58,3.75), correct=c(2.74), name="StdDev", totalPts=1)
```
2. What's the standard deviation (in inches)? `r I(galtondata2)`

```{r include=FALSE}
galtondata3=selectSet(name="95per", totalPts=1, "-3.7 to 4.8"=FALSE, "-4.6 to 4.9"= FALSE, "-5.2 to 5.6"=TRUE, "-9.5 to 4.5"=FALSE)
```
3. What is the 95-percent coverage interval (in inches)? `r I(galtondata3)`      

<aside>
ANSWER:
First, you need to pull out the data for males.     
```{r}
males=subset(galton, sex=='M')
mean(males$height - males$father)
```

```{r}
sd(males$height - males$father)
```

```{r}
qdata(c(0.025, 0.975), males$height - males$father, data=galton)
```
</aside>

`r I(endProblem())`
