Intro to Statistical Modeling Ch. 3 Prob. 3.12
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P12-SD")
```

A standard deviation contest.  For (a) and (b) below, you can choose
numbers from the set $0,1,2,3,4,5,6,7,8$, and $9$.  Repeats are
allowed.

* Which list of 4 numbers has the largest standard
  deviation such a list can possibly have?
```{r include=FALSE}
f = newMC(totalPts=1)
```
  
  `r I(f(FALSE))` $0,3,6,9$     
  `r I(f(FALSE))` $0,0,0,9$     
  `r I(f(TRUE))` $0,0,9,9$      
  `r I(f(FALSE))` $0,9,9,9$
  
```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```

* Which list of 4 numbers has the smallest standard
  deviation such a list can possibly have?
```{r include=FALSE}
g = newMC(totalPts=1)
```

  `r I(g(FALSE))` $0,3,6,9$     
  `r I(g(FALSE))` $0,1,2,3$     
  `r I(g(FALSE))` $5,5,6,6$     
  `r I(g(TRUE))` $9,9,9,9$
  
```{r include=FALSE, results="hide"}
I(g(finish=TRUE))
```

`r I(closeProblem())`
