Intro to Statistical Modeling Ch. 3 Prob. 3.10
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P10-SD")
```

##### This is either 10a or 10b, but because I can't tell what the plot looks like, I can't tell which one it is.  I'll finish this later.


The plot shows two different displays of density.  The displays might
be from the same distribution or two different distributions.

```{r eval=FALSE}
<<exp,fig=TRUE,pdf=TRUE,include=false,width=5,height=4,echo=false>>=
one = rnorm(150,mean=5,sd=2)
x = seq(-2,12,length=100)
plot(x,pnorm(x,mean=5,sd=2),ylab="???",xlab="Value",main="",type="l",lwd=2)
rug(one)
```

```{r eval=FALSE}
\centerline{\includegraphics[width=4in]{Figures/B103-2-exp.pdf}}
```

\begin{enumerate}[(a)]
\item What are the two displays?

\begin{MultipleChoice}
\wrong{Density and cumulative}
\correct{Rug and cumulative}
\wrong{Cumulative and box plot}
\wrong{Density and rug plot}
\wrong{Rug and box plot}
\end{MultipleChoice}

\begin{AnswerText}
The rug plot is the small ticks on the horizontal axis.  The other
distribution has a shape that increases steadily --- never decreasing --- starting from 0 on
the left and going to 1 on the right.  That's the shape of a
cumulative distribution.  
\end{AnswerText}

\item 
The two displays show the same distribution. \TorF{true} 


\item Describe briefly any sign of mismatch or what features convince you
that the two displays are equivalent. \\
\TextEntry
\end{enumerate}

