Intro to Statistical Modeling Ch. 3 Prob. 6
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
require(knitr)
startProblem("SM-3-P6-SD")
#opts_chunk(tidy=FALSE)
```

Using Galton's height `Galton`, compute the answers to these
questions about outliers using the 1.5 IQR rule of
thumb.  To help, you execute the following command to create a function `outlier()` that indicates whether each case is an outlier. 

```{r message=FALSE,results="hide"}
fetchData("outlier-function.R") # reads in the function
```

**Example**: How many outliers are there in column of fathers' heights?
```{r}
tally(~outlier(father), data=Galton)
```

As it happens, `outlier()` is an very simple problem that doesn't take the `~` and `data=` arguments.  But you can use it via `with()`, for instance, `with(data=Galton,outlier(father))`.

**1.** Which of these statements will tally the number of cases that are outliers with respect to *height*?  (Remember that the data frame is named `Galton`.)  Try each of the commands, some of which won't give anything like what you want.
```{r include=FALSE}
f=newMC(totalPts=1, name="which.statement")
```
  `r I(f(FALSE))` <code>~with(data=Galton,outlier(height))</code>     
  `r I(f(TRUE))` <code>tally(~outlier(height),data=Galton)</code>     
  `r I(f(FALSE))` <code>~outlier(tally(~height, data=Galton))</code>     
  `r I(f(FALSE))` <code>subset(Galton, outlier(height))</code>     
  `r I(f(FALSE))` <code>~outlier(subset(Galton, height))</code>    
`r I(f(finish=TRUE))`
 
```{r include=FALSE}
outliers=selectNumber(choices=c(0,1,2,3,5,10,15,20), correct=c(1), name="height", totalPts=1)
```
**2.** How many of the cases are outliers in *height* ? `r I(outliers)`

<aside>
ANSWER:         
```{r}
tally( ~outlier(height ), data=Galton )      
```
</aside>

```{r include=FALSE}
outliers2=selectNumber(choices=c(0,11,22,33,44,55,66), correct=c(44), name="mother", totalPts=1)
```
**3.** How many of the cases are outliers in *mother*? `r I(outliers2)`

<aside>
ANSWER:
```{r}
tally( ~outlier(mother), data=Galton )      
```
</aside>

```{r include=FALSE}
outliers3=selectNumber(choices=c(0,4,9,14,19,24,29), correct=c(9), name="father", totalPts=1)
```
**4.** How many of the cases are outliers in *father*? `r I(outliers3)`

<aside>
ANSWER:
```{r}
tally( ~outlier(father), data=Galton )     
```
</aside>

```{r include=FALSE}
outliers4=selectNumber(choices=c(0,5,10,15,20,25,30,35), correct=c(20), name="female", totalPts=1)
```
**5.** Looking just at the cases where *mother* is an outlier (hint: use `subset()`), how
  many of the children involved (variable *sex*) are female? This is harder`r I(outliers4)`
  
<aside>
>ANSWER:
```{r}   
tally(~sex, data=subset(Galton, outlier(mother)))     
```
</aside>

`r I(endProblem())`