Intro to Statistical Modeling Ch. 3 Prob. 3.08
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P8-SD")
```
The figure shows the results from the medal winners in the
women's 10m air-rifle competition in the 2008 Olympics.  (Figure from
the New York Times, Aug. 10, 2008)

```{r eval=FALSE}
\medskip
\centerline{\includegraphics[width=2.5in]{../Figures/shooting.png}}
\medskip
```

The location of each of 10 shots is shown as transluscent light
circles in each target.  The
objective is to hit the bright target dot in the center.  There is random
scatter (variance) as well as steady deviations (bias) from the target.



What is the direction of the apparent bias in Katerina Emmons's
results? (Directions are indicated as compass directions, E=east,
NE=north east, etc.)

```{r include=FALSE}
direction=selectSet(name="compass", totalPts=1, "NE"=FALSE, "NW"=FALSE, "SW"=TRUE, "SE"=FALSE)
```

  `r I(direction)`


To measure the size of the bias, find the center of the shots and
measure how far that is from the target dot.  Take the distance
between the concentric circles as one unit. 

What is the size of the bias in Katerina Emmon's results?
```{r include=FALSE}
size=selectNumber(name="bias", totalPts=1, choices=c(0,1,3,4,6,10), correct=c(1))
```
  `r I(size)`

`r I(closeProblem())`
