Intro to Statistical Modeling Ch. 3 Prob. 2
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-3-P2-SD")
```

Here are some useful operators for taking a quick look at data frames:

<code>names</code> | Lists the names of the components.
:------------------:|:------------------:
<code>ncol</code> | Tells how many components there are.
<code>nrow</code> | Tells how many lines of data there are.
<code>head</code> | Prints the first several lines of the data frame.

Here are some examples of these commands applied to the <code>CO2</code>
data frame:

```{r}
CO2 = fetchData("CO2")
names(CO2)
ncol(CO2)
nrow(CO2)
head(CO2)
```



The data frame <code>iris</code> records measurements on flowers. You can read in with 

```{r, eval=FALSE}
iris = fetchData("iris")
```

creating an object named <code>iris</code>.

Use the above operators to answer the following questions.

* Which of the following is the name of a column in <code>iris</code>?
```{r include=FALSE}
irisquest=selectSet(name="name", totalPts=1, "Flower"=FALSE, "Color"=FALSE, "Species"=TRUE, "Length"=FALSE)
```

  `r I(irisquest)`
  
* How many rows are there in <code>iris</code>?
```{r include=FALSE}
irisquest2=selectNumber(choices=c(1,50,100,150,200), correct=c(150), name="rows", totalPts=1)
```

  `r I(irisquest2)`

* How many columns are there in <code>iris</code>?
```{r include=FALSE}
irisquest3=selectNumber(choices=c(2,3,4,5,6,7,8,10), correct=c(5), name="columns", totalPts=1)
```

  `r I(irisquest3)`

* What is the <code>Sepal.Length</code> in the third row?
```{r include=FALSE}
irisquest4=selectNumber(choices=c(1.2,3.6,4.2,4.7,5.9), correct=c(4.7), name="SepalLength", totalPts=1)
```

  `r I(irisquest4)`

* The data frame <code>mtcars</code> has data on cars from the 1970s.  
You can read it in with 
```{r, eval=FALSE}
cars = fetchData("mtcars")
```

 creating an object named <code>cars</code>.

Use the above operators to answer the following questions.

* Which of the following is the name of a column in <code>cars</code>?
```{r include=FALSE}
carsq=selectSet(name="name.of.column", totalPts=1, "carb"=TRUE, "color"=FALSE, "size"=FALSE, "weight"=FALSE, "wheels"=FALSE)
```

  `r I(carsq)`

* How many rows are there in <code>cars</code>?
```{r include=FALSE}
carsq2=selectNumber(choices=c(30,31,32,33,34,35), correct=c(32), name="rows2", totalPts=1)
```

  `r I(carsq2)`

* How many columns are there in <code>cars</code>?
```{r include=FALSE}
carsq3=selectNumber(choices=c(7,8,9,10,11), correct=c(11), name="columns2", totalPts=1)
```

  `r I(carsq3)`

* What is the <code>wt</code> in the second row?
```{r include=FALSE}
carsq4=selectNumber(choices=c(2.125,2.225,2.620,2.875,3.215), correct=c(2.875), name="wt", totalPts=1)
```

  `r I(carsq4)`
  
`r I(endProblem())`