Intro to Statistical Modeling Ch. 3 Prob. 3
========================================================
```{r include=FALSE}
require(mosaic)
require(ScoreR)
startProblem("SM-3-P3-SD")
```
Here are Galton's data on heights of adult children and their parents.

```{r messages=FALSE,warning=FALSE}
require(mosaic)     
galton = fetchData("Galton")  
```

Which one of these commands will give the 95th percentile of the
children's heights in Galton's data? `Galton`

```{r include=FALSE}
f=newMC(totalPts=1, name="which.command")
```
  `r I(f(FALSE))` <code>quantile(galton$height, 95)</code>     
  `r I(f(TRUE))` <code>quantile(galton$height, 0.95)</code>     
  `r I(f(FALSE))` <code>quantile(galton$father, 95)</code>     
  `r I(f(FALSE))` <code>quantile(galton$father, 0.95)</code>    
`r I(f(finish=TRUE))`

<aside>
ANSWER:
What's key here is to remember that percentiles need to be specified
as a fraction: the 95th percentile is 0.95.


The children's heights are contained in the *height* variable, not
*father* (which has the heights of the fathers).
</aside>

<bigskip>

Which of these command will give the 90-percent coverage interval of the children's heights in Galton's data?
```{r include=FALSE}
g=newMC(totalPts=1, name="which.command.2")
```
  `r I(g(TRUE))` <code>quantile(galton$height, c(0.05, 0.95))</code>     
  `r I(g(FALSE))` <code>quantile(galton$height, c(0.025, 0.975))</code>     
  `r I(g(FALSE))` <code>quantile(galton$height, 0.90)</code>     
  `r I(g(FALSE))` <code>quantile(galton$height, 90)</code>     
`r I(g(finish=TRUE))`

<aside>
ANSWER:
Since you're looking for a 90-percent coverage interval to cover the
center of the data, you want to
leave 5 percent on the left and 5 percent on the right.  This means
that the interval will run from the 5th percentile to the 95th percentile.
</aside>


 
Find the 50-percent coverage interval of the following variables in Galton's height data:
```{r include=FALSE}
prob1=selectSet(name="50per", totalPts=1, "59 to 73 inches"=FALSE, "68 to 71 inches"=TRUE, "63 to 65.5 inches"=FALSE, "68 to 74 inches"=FALSE)
```
* Father's heights `r I(prob1)`

<aside>
ANSWER: A 50-percent coverage interval will leave 25 percent of the data to the left and another 25 percent to the right, so the interval runs from the 25th to the 75th percentile.      
```{r}
qdata(  c(0.25, 0.75), father, data=galton)     
```

Note how the command uses <code>c(0.25, 0.75)</code> to create a set with
BOTH percentiles.  If you wanted, you could do one at a time:     
```{r}
qdata(c(0.25), father, data=galton)
```

```{r}
qdata(c(0.75), father, data=galton)
```

But it's nicer to have both ends of the interval reported in one statement.
</aside>

```{r include=FALSE}
prob2=selectSet(name="mother", totalPts=1, "59 to 73 inches"=FALSE, "68 to 71 inches"=FALSE, "63 to 65.5 inches"=TRUE, "68 to 74 inches"=FALSE)
```
* Mother's heights `r I(prob2)`   

<aside>
ANSWER:
Just like with the fathers' heights, but now ask for the quantiles on
the mothers' height:     
```{r}
qdata(c(0.25, 0.75), mother, data=galton)
```
</aside>




Find the 95-percent coverage interval of
```{r include=FALSE}
prob3=selectSet(name="father", totalPts=1, "65 to 73 inches"=FALSE, "65 to 74 inches"=TRUE, "68 to 73 inches"=FALSE, "59 to 69 inches"=FALSE)
```
* Father's heights `r I(prob3)`
    
<aside>
ANSWER:For a 95-percent coverage interval, look at the 2.5 and 97.5
percentile. 
```{r}
qdata(c(0.025,0.975), father, data=galton)
```
</aside>

```{r include=FALSE}
prob4=selectSet(name="mother2", totalPts=1, "62.5 to 68.5 inches"=FALSE, "65 to 69 inches"=FALSE, "63 to 68.5 inches"=FALSE, "59 to 69 inches"=TRUE)
```
* Mother's heights `r I(prob4)`

    
<aside>
ANSWER:
```{r}
qdata(c(0.025, 0.975), mother, data=galton)
```
</aside>

`r I(endProblem())`