Intro to Statistical Modeling Ch. 3 Prob 3.14
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P14-SD")
```

The boxplots below are all made from exactly the same data.  One of
them is made correctly, according to the ``1.5 IQR'' convention for
drawing the whiskers.  The others are drawn differently.

```{r, echo="false"}
dd = c( jitter(seq(-10,10,by=1)), runif(1000,-3,3) )
```

```{r eval=FALSE}
\centerline{\begin{tabular}{cccc}
{\bf Plot 1} & {\bf Plot 2} & {\bf Plot 3} & {\bf Plot 4}\\
 & & \\
<<b1,fig=TRUE,pdf=TRUE,include=false,width=3,height=5,echo=false>>=
boxplot(dd,range=2.5,pch=20)
@ 
\includegraphics[width=.8in,trim=35 30 25 30]{Figures/B101-b1}
&
<<b2,fig=TRUE,pdf=TRUE,include=false,width=3,height=5,echo=false>>=
boxplot(dd,pch=20)
@ 
\includegraphics[width=.8in,trim=35 30 25 30]{Figures/B101-b2}
&
<<b3,fig=TRUE,pdf=TRUE,include=false,width=3,height=5,echo=false>>=
boxplot(dd,range=1,pch=20)
@ 
\includegraphics[width=.8in,trim=35 30 25 30]{Figures/B101-b3}
&
<<b4,fig=TRUE,pdf=TRUE,include=false,width=3,height=5,echo=false>>=
boxplot(dd,range=0,pch=20)
@ 
\includegraphics[width=.8in,trim=35 30 25 30]{Figures/B101-b4}
```


Which of the plots is correct?
```{r include=FALSE}
plots=selectNumber(choices=c(1,2,3,4), correct=c(2), name="correctplot", totalPts=1)
```

 `r I(plots)`

<aside>
ANSWER:
The height of the box gives the IQR.  If there are outliers, the whisker length should be 1.5
times the IQR.  So look for the plot that has a whisker length
somewhat taller than the box itself.
</aside>
