Intro to Statistical Modeling Ch. 3 Prob. 5 
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P5-SD")
```

Use R to generate the sequence of 101 numbers: $0, 1, 2, 3, \cdots, 100$.

<aside>
ANSWER:
```{r}
s1 = seq(0,100)
```
</aside>

```{r include=FALSE}
sequence=selectNumber(choices=c(25,50,75,100), correct=c(50), name="meanvalue", totalPts=1)
```
(1) What's the mean value? `r I(sequence)`

<aside>
ANSWER:
```{r}
mean(s1)
```
</aside>

```{r include=FALSE}
sequence2=selectNumber(choices=c(25,50,75,100), correct=c(50), name="medianvalue", totalPts=1)
```
(2) What's the median value? `r I(sequence2)`


<aside>
ANSWER:
```{r}
median(s1)
```
</aside>

```{r include=FALSE}
sequence3=selectNumber(choices=c(10.7,29.3,41.2,53.8), correct=c(29.3), name="StdDev", totalPts=1)
```
(3) What's the standard deviation? `r I(sequence3)`

<aside>
ANSWER:
```{r}
sd(s1)
```
</aside>

```{r include=FALSE}
sequence4=selectNumber(choices=c(5050,20251,103450,338350,585200), correct=c(338350), name="SumoftheSquares", totalPts=1)
```
(4) What's the sum of squares? `r I(sequence4)`

<aside>
ANSWER:
```{r}
sum( s1^2 )
```
</aside>

Now generate the sequence of perfect squares $0, 1, 4, 9, \cdots, 10000$,
or, written another way, $0^2, 1^2, 2^2, 3^2, \cdots, 100^2$.  (Hint:
Make a simple sequence 0 to 100 and square it.)

<aside>
ANSWER:
```{r}
s2 = seq(0,100)^2
```
</aside>


```{r include=FALSE}
perfectsquares=selectNumber(choices=c(50,2500,3350,4750,7860), correct=c(3350), name="meanvalue2", totalPts=1)
```
1. What's the mean value? `r I(perfectsquares)` 

```{r include=FALSE}
perfectsquares2=selectNumber(choices=c(50,2500,3350,4750,7860), correct=c(2500), name="medianvalue2", totalPts=1)
```
2. What's the median value? `r I(perfectsquares2)`

```{r include=FALSE}
perfectsquares3=selectNumber(choices=c(29.3,456.2,3028,4505,6108), correct=c(3028), name="StdDev2", totalPts=1)
```
3. What's the standard deviation? `r I(perfectsquares3)`

```{r include=FALSE}
perfectsquares4=selectNumber(choices=c(5050,20251,338350,585200,2050333330), correct=c(2050333330), name="SumoftheSquares2", totalPts=1)
```
4. What's the sum of squares? `r I(perfectsquares4)`

`r I(closeProblem())`