Intro to Statistical Modeling Ch. 3 Prob. 3.15
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P15-SD")
```

The plot purports to show the density of a distribution of data.  If this is
true, the fraction of the data that falls between any two values on
the $x$ axis should be the area under the curve between those two
values.

```{r plot1, fig.width=4, fig.height=4, echo=FALSE, dev="svg", out.width="70%"}
xpts = seq(5,20,length=1000)
lines(xpts,dnorm(xpts,mean=12,sd=2),lwd=2)
```

![plot](B106-plot1.pdf)


Answer the following questions. In doing so, keep in mind that the area of each
little box on the graph paper has been arranged to be $0.01$, so you
can calculate the area by counting boxes.  You don't need to be too
fanatical about dealing with boxes where only a portion in under the
curve; just eyeball things and estimate.

* The total area under a density curve should be 1.
  Assuming that the density curve has height zero outside of the area
  of the plot, is the area under the entire curve consistent with
  this?
```{r include=FALSE}
densitycurve=selectSet(name="consistentArea", totalPts=1, "Yes"=TRUE, "No"=FALSE)
```

 `r I(densitycurve)`

* What fraction of the data falls in the range $12 \leq x \leq
  14$?
```{r include=FALSE}
f = newMC(totalPts=1)
```

 `r I(f(FALSE))` 14%     
 `r I(f(FALSE))` 22%      
 `r I(f(TRUE))` 34%      
 `r I(f(FALSE))` 56%     
 `r I(f(FALSE))` Can't tell from this graph.     

```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```


* What fraction of the data falls in the range $14 \leq x \leq
  16$?
```{r include=FALSE}
g = newMC(totalPts=1)
```

 `r I(g(TRUE))` 14%     
 `r I(g(FALSE))` 22%     
 `r I(g(FALSE))` 34%     
 `r I(g(FALSE))` 56%     
 `r I(g(FALSE))` Can't tell from this graph.

```{r include=FALSE, results="hide"}
I(g(finish=TRUE))
```

* What fraction of the data has $x \geq 16$?

```{r include=FALSE}
h = newMC(totalPts=1)
```

 `r I(h(FALSE))` 1%     
 `r I(h(TRUE))` 2%     
 `r I(h(FALSE))` 5%     
 `r I(h(FALSE))` 10%     
 `r I(h(FALSE))` Can't tell from this graph.     
 
```{r include=FALSE, results="hide"}
I(h(finish=TRUE))
```

* What is the width of the 95% coverage interval.  (Note: The
  coverage interval itself has top and bottom ends.  This problem asks
  for the spacing between the two ends.)
  
```{r include=FALSE}
i = newMC(totalPts=1)
```

 `r I(i(FALSE))` 2     
 `r I(i(FALSE))` 4     
 `r I(i(TRUE))` 8      
 `r I(i(FALSE))` 12     
 `r I(i(FALSE))` Can't tell from the graph.

```{r include=FALSE, results="hide"}
I(i(finish=TRUE))
```

`r I(closeProblem())`
