Intro to Statistical Modeling Ch. 3 Prob. 3.56
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P56-SD")
```
To exercise your ability to extract subsets of data, 
take each of the following subsets of the swimming records in 
`SwimRecords`
 and calculate
the mean and minimum swimming time for the subset.  (Answers have been
rounded to one decimal place.)

* All records between 1920 and 1940 (including 1920 and 1940).

```{r include=FALSE}
records=selectNumber(choices=c(54.6,60.2,64.7,69.6,71.3), correct=c(64.7), totalPts=1, name="mean")
```

  Mean: `r I(records)`

```{r include=FALSE}
records2=selectNumber(choices=c(56.4,60.2,64.7,69.6,71.3), correct=c(56.4), totalPts=1, name="min")
```

  Min: `r I(records2)` 

* Female records in the 1970s and 1980s

```{r include=FALSE}
records3=selectNumber(choices=c(54.1,54.7,56.2,60.2,64.7,69.6,71.3), correct=c(56.2), totalPts=1, name="mean2")
```

  Mean: `r I(records3)`

```{r include=FALSE}
records4=selectNumber(choices=c(54.1,54.7,56.2,60.2,64.7,69.6,71.3), correct=c(54.7), totalPts=1, name="min2")
```

  Min: `r I(records4)`

* All records that are **slower** than 60 seconds.  (Hint: Think
  what "slower" means in terms of the swimming times.)

```{r include=FALSE}
slowrecords=selectNumber(choices=c(56.2,60.2,64.7,69.6,71.3,73.2,75.8), correct=c(69.6), totalPts=1, name="mean3")
```
  
  Mean: `r I(slowrecords)`

```{r include=FALSE}
slowrecords2=selectNumber(choices=c(56.2,60.2,61.5,64.7,69.6,71.3), correct=c(60.2), name="min3", totalPts=1)
```

  Min: `r I(slowrecords2)`
  

<aside>
<code>
\> s = subset( swim, year >=1920 & year <=1940)     
\> mean(s$time)     
[1] 64.675     
\> min(s$time)     
[1] 56.4     
\> s = subset( swim, sex == 'F' & year >=1970 & year < 1990)     
\> mean(s$time)     
[1] 56.22571     
\> min(s$time)     
[1] 54.73     
\> s = subset( swim, time > 60)     
\> mean(s$time)     
[1] 69.61667     
\> min(s$time)     
[1] 60.2     

</code>
</aside>

`r I(closeProblem())`
