Intro to Statistical Modeling Ch.3 Prob. 6
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P6-SD")
```

Using Galton's height `Galton`, compute the answers to these
questions about outliers using the 1.5 IQR rule of
thumb.  To help, you execute the following command to create a function `outlier()` that indicates whether each case is an outlier. 

```{r}
fetchData("outlier-function.R")
```

Example:
```
tally(~outlier(father), data=Galton)
```

1. Which of these statements will compute the number of cases that
  are outliers with respect to *height*?  (Remember that the data
  frame is named `Galton`.)
```{r include=FALSE}
f=newMC(totalPts=1)
```
  `r I(f(FALSE))` <code>outlier(galton$height)</code>     
  `r I(f(TRUE))` <code>table(outlier(galton$height))</code>     
  `r I(f(FALSE))` <code>outlier(table(galton$height))</code>     
  `r I(f(FALSE))` <code>subset(galton, outlier(galton$height))</code>     
  `r I(f(FALSE))` <code>outlier(subset(galton, galton$height))</code>
```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```
 
```{r include=FALSE}
outliers=selectNumber(choices=c(0,1,2,3,5,10,15,20), correct=c(1), name="height", totalPts=1)
```
2. How many of the cases are outliers in *height* ? `r I(outliers)`

<aside>
ANSWER:         
```{r}
tally( ~outlier(height ), data=Galton )      
```
</aside>

```{r include=FALSE}
outliers2=selectNumber(choices=c(0,11,22,33,44,55,66), correct=c(44), name="mother", totalPts=1)
```
3. How many of the cases are outliers in *mother*? `r I(outliers2)`

<aside>
ANSWER:
```{r}
table( outlier( galton$mother ) )      
```
</aside>

```{r include=FALSE}
outliers3=selectNumber(choices=c(0,4,9,14,19,24,29), correct=c(9), name="father", totalPts=1)
```
4. How many of the cases are outliers in *father*? `r I(outliers3)`

<aside>
ANSWER:
```{r}
table( outlier( galton$father ) )     
```
</aside>

```{r include=FALSE}
outliers4=selectNumber(choices=c(0,5,10,15,20,25,30,35), correct=c(20), name="female", totalPts=1)
```
5. Looking just at the cases where *mother* is an outlier, how
  many of the children involved (variable *sex*) are female? `r I(outliers4)`
  
<aside>
>ANSWER:
```{r}
foo = subset(galton, outlier( galton$mother) )      
table(foo$sex)     
```
</aside>

`r I(closeProblem())`
