Intro to Statistical Modeling Ch.3 Prob. 6
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-3-P6-SD")
```
Using Galton's height `Galton`, compute the answers to these
questions about outliers using the 1.5 IQR rule of
thumb and the <code>outlier</code> function.

1. Which of these statements will compute the number of cases that
  are outliers with respect to *height*?  (Assume that the data
  frame is named <code>galton</code>.)
```{r include=FALSE}
f=newMC(totalPts=1)
```
  `r I(f(FALSE))` <code>outlier(galton$height)</code>     
  `r I(f(TRUE))` <code>table(outlier(galton$height))</code>     
  `r I(f(FALSE))` <code>outlier(table(galton$height))</code>     
  `r I(f(FALSE))` <code>subset(galton, outlier(galton$height))</code>     
  `r I(f(FALSE))` <code>outlier(subset(galton, galton$height))</code>
```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```
 
```{r include=FALSE}
outliers=selectNumber(choices=c(0,1,2,3,5,10,15,20), correct=c(1), name="height", totalPts=1)
```
2. How many of the cases are outliers in *height* ? `r I(outliers)`

<aside>
>ANSWER:     
<code>
>table( outlier( galton$height ) )      
FALSE  TRUE       
  897     1       
</code>
</aside>

```{r include=FALSE}
outliers2=selectNumber(choices=c(0,11,22,33,44,55,66), correct=c(44), name="mother", totalPts=1)
```
3. How many of the cases are outliers in *mother*? `r I(outliers2)`

<aside>
>ANSWER:
<code>
>\> table( outlier( galton$mother ) )      
>FALSE  TRUE      
  854    44      
</code>
</aside>

```{r include=FALSE}
outliers3=selectNumber(choices=c(0,4,9,14,19,24,29), correct=c(9), name="father", totalPts=1)
```
4. How many of the cases are outliers in *father*? `r I(outliers3)`

<aside>
>ANSWER:
<code>
>table( outlier( galton$father ) )     
>FALSE  TRUE      
>  889     9      
</code>
</aside>

```{r include=FALSE}
outliers4=selectNumber(choices=c(0,5,10,15,20,25,30,35), correct=c(20), name="female", totalPts=1)
```
5. Looking just at the cases where *mother* is an outlier, how
  many of the children involved (variable *sex*) are female? `r I(outliers4)`
  
<aside>
>ANSWER:
<code>
>\> foo = subset(galton, outlier( galton$mother) )      
>\> table(foo$sex)     
 F  M      
20 24      
</code>
</aside>

`r I(closeProblem())`
