Intro to Statistical Modeling Ch. 2 Prob. 2
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-02-P2-SD")
```

Using the <code>table</code> operator and the comparison operators (such as
<code>></code> or <code>==</code>), answer the following questions about the CO2 data.  You can read in the CO2 data with the statement 

```{r}
CO2 = fetchData("CO2") 
```
You can see the data set itself by giving the command

```{r results="hide"}
CO2
```

In this exercise, you will use R commands to count how many of the
cases satisfy various criteria:

How many of the plants in CO2 are Mc1 for *Plant*?

```{r include=FALSE}
numberplants=selectNumber(choices=c(7,12,14,21,28,34), correct=c(7), name="MC1", totalPts=1)
```

`r I(numberplants)`

<aside>
ANSWER:
```{r}
table(CO2$Plant=='MC1')
```
</aside>

How many of the plants in CO2 are either Mc1 or Mn1?

```{r include=FALSE}
numberplants2=selectNumber(choices=c(8,12,14,16,23,54,92), correct=c(14), name="Mc1orMn1", totalPts=1)
```

`r I(numberplants2)`

<aside>
ANSWER:
```{r}
table( CO2$Plant == 'Mc1' | CO2$Plant == 'Mn1')
```
</aside>

How many are Quebec for *Type* and nonchilled for *Treatment*?

```{r include=FALSE}
numberplants3=selectNumber(choices=c(8,12,14,16,21,23,54,92), correct=c(21), name="Quebec", totalPts=1)
```

`r I(numberplants3)`

<aside>
ANSWER:
```{r}
table( CO2$Type=="Quebec" & CO2$Treatment=="nonchilled")
```   
or, another way

```{r}
with(CO2,table(Type, Treatment))
``` 
</aside>

How many have a concentration (*conc*) of 300 or bigger?

```{r include=FALSE}
numberplants4=selectNumber(choices=c(12,24,36,48,60), correct=c(48), name="concentration", totalPts=1)
```

`r I(numberplants4)`

<aside>
ANSWER:
```{r}
table( CO2$conc >= 300)
```
</aside>

How many have a concentration between 300 and 450 (inclusive)?

```{r include=FALSE}
numberplants5=selectNumber(choices=c(12,24,36,48,60), correct=c(12), name="conc300to450", totalPts=1)
```

`r I(numberplants5)`

<aside>
ANSWER:
```{r}
table( CO2$conc >= 300 & CO2$conc <=450)
```
</aside>

How many have a concentration between 300 and 450 (inclusive) and are nonchilled?

```{r include=FALSE}
numberplants6=selectNumber(choices=c(6,8,10,12,14,16), correct=c(6), name="concNonchilled", totalPts=1)
```

`r I(numberplants6)`

<aside>
ANSWER:
```{r}
table( CO2$Treatment == 'chilled' & 
      CO2$conc >= 300 & CO2$conc <=450)
```   
</aside>


How many have an *uptake* that is less than 1/10 of the concentration
(in the units reported)?

```{r include=FALSE}
numberplants7=selectNumber(choices=c(17,33,34,51,68), correct=c(51), name="uptake", totalPts=1)
```

`r I(numberplants7)`

<aside>
ANSWER:
```{r}
table(CO2$uptake < 0.1*CO2$conc)
```
</aside>

`r I(closeProblem())`
