Intro to Statistical Modeling Ch. 2 Prob. 2.16
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-2-P16-SD")
```

Read in the file `KidsFeet`.  For each of the following, hand
in the R statements to find what is asked for.  Provide both the
command you give and the output of the command.

* The names of the variables.
```{r include=FALSE, eval=FALSE}
I(textItem(name="names", totalPts=2, rows=3))`
```

 `r I(textItem(name="names", totalPts=2, rows=3))`

* The mean of the foot *width* variable.
```{r include=FALSE, eval=FALSE}
I(textItem(name="width", totalPts=2, rows=3))
```

 `r I(textItem(name="width", totalPts=2, rows=3))`

* Which of the cases are girls.
```{r include=FALSE, eval=FALSE}
I(textItem(name="girls", totalPts=2, rows=3))
```

 `r I(textItem(name="girls", totalPts=2, rows=3))`

* The mean foot *width* for the subset of data for the
  girls.
```{r include=FALSE, eval=FALSE}
I(textItem(name="girlfeet", totalPts=2, rows=3))
```

 `r I(textItem(name="girlfeet", totalPts=2, rows=3))`


Of no particular statistical value, but to review the use of logical
operators: 

* The mean foot *width* for the subset of data for people
whose bigger foot is left and dominant hand is also left.
```{r include=FALSE, eval=FALSE}
I(textItem(name="review", totalPts=2, rows=3))
```

 `r I(textItem(name="review", totalPts=2, rows=3))`


And, for some extra practice in using logical operators:

* The mean foot *width* for the subset of data for people
who are either male or whose bigger foot matches the dominant hand. 
```{r include=FALSE, eval=FALSE}
I(textItem(name="extrapractice", totalPts=2, rows=3))
```

 `r I(textItem(name="extrapractice", totalPts=2, rows=3))`

* The mean foot *width* for the subset of data for people
whose bigger foot does NOT match the dominant hand.
```{r include=FALSE, eval=FALSE}
I(textItem(name="extrapractice2", totalPts=2, rows=3))
```

 `r I(textItem(name="extrapractice2", totalPts=2, rows=3))`

`r I(closeProblem())`