Intro to Statistical Modeling Ch. 2 Prob. 2.22
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-02-P2-22-SD")
```

Since the computer has to represent numbers that are both very large
and very small, scientific notation is often used.  The number
<code>7.23e4</code> means $7.23\times 10^4 = 72300$.  The number
<code>1.37e-2</code> means $1.37\times 10^{-2} = 0.0137$.

For each of the following numbers written in computer scientific
notation, say what is the corresponding number.

* <code>3e1</code> 
```{r include=FALSE}
scinote= selectNumber(choices=c(.0001,0.001,0.003,0.01,0.03,0.1,0.3,1,3,10,30,100,300,1000,3000,10000), correct=c(30), name="a", totalPts=1)
```

`r I(scinote)`

* <code>1e3</code>

```{r include=FALSE}
scinote2= selectNumber(choices=c(.0001,0.001,0.003,0.01,0.03,0.1,0.3,1,3,10,30,100,300,1000,3000,10000), correct=c(100), name="b", totalPts=1)
```
`r I(scinote2)`

* <code>0.1e3</code>

```{r include=FALSE}
scinote3= selectNumber(choices=c(.0001,0.001,0.003,0.01,0.03,0.1,0.3,1,3,10,30,100,300,1000,3000,10000), correct=c(10), name="c", totalPts=1)
```
`r I(scinote3)`

* <code>0.3e-2</code>
```{r include=FALSE}
scinote4= selectNumber(choices=c(.0001,0.001,0.003,0.01,0.03,0.1,0.3,1,3,10,30,100,300,1000,3000,10000), correct=c(0.003), name="d", totalPts=1)
```
`r I(scinote4)`

* <code>10e3</code>
```{r include=FALSE}
scinote5= selectNumber(choices=c(.0001,0.001,0.003,0.01,0.03,0.1,0.3,1,3,10,30,100,300,1000,3000,10000), correct=c(10000), name="f", totalPts=1)
```
`r I(scinote5)`

* <code>10e-3</code>
```{r include=FALSE}
scinote6= selectNumber(choices=c(.0001,0.001,0.003,0.01,0.03,0.1,0.3,1,3,10,30,100,300,1000,3000,10000), correct=c(0.01), name="g", totalPts=1)
```
`r I(scinote6)`

* <code>0.0003e3</code>
```{r include=FALSE}
scinote7= selectNumber(choices=c(.0001,0.001,0.003,0.01,0.03,0.1,0.3,1,3,10,30,100,300,1000,3000,10000), correct=c(0.3), name="h", totalPts=1)
```
`r I(scinote7)`

`r I(closeProblem())`


