Intro to Statistical Modeling Ch. 2 Reading Questions
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-02-ReadingQuestions-SD")
```

* What are the two major different kinds of variables?
```{r include=FALSE, eval=FALSE}
I(textItem(rows=3, totalPts=2, name="variables"))
```

  `r I(textItem(rows=3, totalPts=2, name="variables"))`

* How are variables and cases arranged in a data frame?
```{r include=FALSE, eval=FALSE}
I(textItem(rows=3, totalPts=2, name="arrangement"))
```

  `r I(textItem(rows=3, totalPts=2, name="arrangement"))`

* How is the relationship between these things: population,
  sampling frame, sample, census?
```{r include=FALSE, eval=FALSE}
I(textItem(rows=3, totalPts=2, name="relationship"))
```

  `r I(textItem(rows=3, totalPts=2, name="relationship"))`

* What's the difference between a longitudinal and cross-sectional
  sample?
```{r include=FALSE, eval=FALSE}
I(textItem(rows=3, totalPts=2, name="difference"))
```

  `r I(textItem(rows=3, totalPts=2, name="difference"))`

* Describe some types of sampling that lead to the sample
  potentially being unrepresentative of the population?
```{r include=FALSE, eval=FALSE}
I(textItem(rows=3, totalPts=2, name="unrepresentative"))
```

  `r I(textItem(rows=3, totalPts=2, name="unrepresentative"))`

`r I(closeProblem())`