Intro to Statistical Modeling Ch.2 Prob. 2.04
========================================================
```{r include=FALSE}
require(mosaic)
require(WriteScoreR)
newScorerSet("SM-02-P2-24-SD")
```

Here is a small data frame about automobiles.


```{r}
emphasize.cols=2,4,6
```

Make and model  |  Vehicle type | Trans. type | \# of cyl. |  City MPG |  Hwy MPG
:-----: | :-----: | :-----: | :-----: | :-----: | :-----: 
Kia Optima  |  compact  | Man.  | 4 | 21  | 31
Kia Optima  | compact | Auto. | 6 | 20  | 28
Saab 9-7X AWD | SUV | Auto. | 6 | 14  | 20
Saab 9-7X AWD | SUV | Auto. | 8 | 12  | 16
Ford Focus  | compact | Man.  | 4 | 24  | 35
Ford Focus  | compact | Auto. | 4 | 24  | 33
Ford F150 2WD | pickup  | Auto. | 8 | 13  | 17     



What are the cases in the data frame?

```{r include=FALSE}
f = newMC(totalPts=1)
```

 `r I(f(FALSE))` Individual car companies     
 `r I(f(FALSE))` Individual makes and models of cars     
 `r I(f(TRUE))` Individual configurations of cars     
 `r I(f(FALSE))` Different sizes of cars     

```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```

<aside>
Answer: 
Each case is a different make and model in a particular
configuration.  For instance, there are two cases that are Kia
Optimas.  One of these cases has a manual transmission, the other an
automatic transmission.  For the Saab, the two cases have different
numbers of cylinders, even though both are automatic transmissions.
</aside>

For each case, what variables are given?  Are they categorical 
or quantitative?

 * Kia Optima:
 
```{r include=FALSE}
kiaoptima=selectSet(name="catorquant", totalPts=1, "Not a variable"=TRUE, "Categorical"=FALSE, "Quantitative"=FALSE)
```

 `r I(kiaoptima)`

<aside>
Answer:
The Kia Optima is not a variable, it's a level of the *Make and
  model* variable.
</aside>

 * City MPG:
```{r include=FALSE}
citympg=selectSet(name="catorquant2", totalPts=1, "Not a variable"=FALSE, "Categorical"=FALSE, "Quantitative"=TRUE)
```

 `r I(citympg)`

 * Vehicle type:
```{r include=FALSE}
vehicletype=selectSet(name="catorquant3", totalPts=1, "Not a variable"=FALSE, "Categorical"=TRUE, "Quantitative"=FALSE)
```
 
 `r I(vehicletype)`

 * SUV:
 
```{r include=FALSE}
SUV=selectSet(name="catorquant4", totalPts=1, "Not a variable"=TRUE, "Categorical"=FALSE, "Quantitative"=FALSE)
```

 `r I(SUV)`

<aside>
Answer:
SUV is a level of the *Vehicle type* variable.
</aside>

 * Trans. type:
 
```{r include=FALSE}
transtype=selectSet(name="catorquant5", totalPts=1, "Not a variable"=FALSE, "Categorical"=TRUE, "Quantitative"=FALSE)
```
 `r I(transtype)`

 * \# of cyl.:
 
```{r include=FALSE}
cyl=selectSet(name="catorquant6", totalPts=1, "Not a variable"=FALSE, "Categorical"=FALSE, "Quantitative"=TRUE)
```
 `r I(cyl)`

Why are some cars listed twice?  Is this a mistake in the table?

```{r include=FALSE}
f = newMC(totalPts=1)
```
 `r I(f(FALSE))` Yes, it's a mistake.   
 `r I(f(TRUE))` A car brand might be listed more than once, but the cases have different attributes on other variables.     
 `r I(f(FALSE))` Some cars are more in demand than others.     

```{r include=FALSE, results="hide"}
I(f(finish=TRUE))
```

<aside> Answer:
As explained above, the cases with the same make and model are
different in other variables.
</aside>

`r I(closeProblem())`


